### 2022-06-12 docs/report/titlepage.tex
Create titlepage.tex

\begin{titlepage}
\begin{flushleft}
\textbf{\LARGE{Researcher Survey of Replication in Geography}}
\vspace{60pt}
\setlength{\columnsep}{20pt}

\noindent \textbf{Peter Kedron}, Corresponding Author\\
  School of Geographical Sciences and Urban Planning, Arizona State University\\
  pkedron@asu.edu\\
  ORCID iD: 0000-0002-1093-3416\\
  \hfill\break
   \textbf{Joseph Holler}\\
  Department of Geography, Middlebury College\\
  josephh@middlebury.edu\\
  ORCID iD: 0000-0002-2381-2699\\
  \hfill\break
  \textbf{Sarah Bardin}\\
  School of Geographical Sciences and Urban Planning, Arizona State University\\
  sfbardin@asu.edu\\
  ORCID iD: 0000-0001-8657-1725 \\
  \hfill\break

\vspace{20pt}

\renewcommand*\abstract{\flushleft\large\textbf{Abstract}\hfill}
\begin{abstract}
\begin{flushleft}
    \noindent While the number of reproduction and replication studies undertaken in the social and behavioural sciences continues to rise, such studies have not yet become commonplace in geography. 
    The small number of studies that have attempted to reproduce geographic research suggest that many studies cannot be fully reproduced, or are simply missing components needed to attempt a reproduction. 
    Despite this suggestive evidence, we have not yet systematically assessed the use of reproducible research practices across the discipline's diverse research traditions, or identified what factors have barred geographers from conducting more reproduction studies.
    This pre-analysis plan outlines the procedures and methods we will use to assess the current use of reproducible research practices in geography and identify barriers to conducting reproductions. 
    This document was prepared after the development of the sampling frame and survey instrument, but before the beginning of data collection.
    \end{flushleft}
\end{abstract}

\vspace{40pt}

Submission date: May 05, 2022
\end{flushleft}
\end{titlepage}

### 2022-06-12 docs/manuscript/manuscript.tex
Create Annals draft template

\documentclass[]{interact}
\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables
%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required

\usepackage{natbib}% Citation support using natbib.sty
\bibpunct[, ]{(}{)}{;}{a}{}{,}% Citation support using natbib.sty
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty

\theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{notation}{Notation}

\begin{document}

\articletype{DRAFT MANUSCRIPT}

\title{Replication in Geography: Insights from a Survey of Geographers}

\author{
\name{Peter Kedron\textsuperscript{a,b}\thanks{CONTACT Peter Kedron. Email: Peter.Kedron@asu.edu}, Joseph Holler\textsuperscript{c}, and Sarah Bardin\textsuperscript{a,b}}
\affil{\textsuperscript{a}School of Geographical Sciences and Urban Planning, Arizona State University, Tempe, Arizona, USA; \textsuperscript{b}Spatial Analysis Research Center (SPARC), Arizona State University, Tempe, Arizona, USA; \textsuperscript{c}Department of Geography, Middlebury College, Middlebury, Vermont, USA}
}

\maketitle

\begin{abstract}
This template is for authors who are preparing a manuscript for a Taylor \& Francis journal using the \LaTeX\ document preparation system and the \texttt{interact} class file, which is available via selected journals' home pages on the Taylor \& Francis website.
\end{abstract}

\begin{keywords}
Replication, Epistemology, Spatial Heterogeneity
\end{keywords}

\end{document}

### 2023-02-16 docs/manuscript/manuscript.tex
Updates from Overleaf

@@
 
-\usepackage{natbib}% Citation support using natbib.sty
-\bibpunct[, ]{(}{)}{;}{a}{}{,}% Citation support using natbib.sty
+\usepackage{natbib}
+\bibliographystyle{chicago}
+\setcitestyle{authoryear,open={(},close={)}}
 \renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty
+
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=blue,
+    filecolor=magenta,
+    urlcolor=blue,
+    citecolor=blue,
+}
+
+\usepackage{titlesec}
+\titleformat*{\section}{\Large\bfseries}
+\titleformat*{\subsection}{\large\bfseries}
+
+\usepackage{endnotes}
+\let\footnote=\endnote
+\usepackage{etoolbox}
+\patchcmd{\enoteformat}{1.8em}{0pt}{}{}
 
@@
 \newtheorem{notation}{Notation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\title{Replication in Geography: Insights from a Survey of Geographers}
+\title{Replication Survey}
 
@@
 \begin{abstract}
-This template is for authors who are preparing a manuscript for a Taylor \& Francis journal using the \LaTeX\ document preparation system and the \texttt{interact} class file, which is available via selected journals' home pages on the Taylor \& Francis website.
+Write Abstract
+
 \end{abstract}
@@
 \begin{keywords}
-Replication, Epistemology, Spatial Heterogeneity
+Reproducible Research, Epistemology, Geographic Research Methods
 \end{keywords}
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\section*{Introduction}
+Since the 1600s, replication has been a defining characteristic of the scientific method and an essential tool of researchers working to remove errors from our understanding of phenomena. 
+\citet{nosek2020} broadly define a replication as any study that has at least one outcome that would be considered to be diagnostic evidence of a claim from prior research.
+More frequently, replication is defined along two axes that help to distinguish the type of diagnostic evidence a study will provide and the function or purpose it is intended to serve. 
+First, it is common to distinguish whether a replication study used the same data as the original study, or if new data were collected and analyzed. 
+Second, it is helpful to identify whether a replication is focused on the question of whether the specific results of the original study can be reobserved, or whether the conclusions drawn from the original study are robust to changes in procedure or context.
+
+When a researcher asks whether the same data and procedures can be used to generate the same results as an original study the central purpose of their study is verification.
+If the researcher uses the original data, but introduces procedural differences they think may effect the original result they pursue a reanalysis designed to determine whether the original reasoning was somehow erroneous.
+Both of these approaches to replication assess the internal validity of research and are more commonly referred to as reproductions.
+If the researcher tries to follow the procedures of an original study, but collects new data, the purpose shifts to evaluating the external validity of the original result by retesting it under new conditions.
+This approach is commonly referred to as replication.
+
+While a replication or reproduction can never provide conclusive evidence for or against a finding, either type of study can be informative. 
+If a well-executed, high-quality replication or reproduction recreates the result of an original study, we are apt to increase our confidence in the original findings. 
+If a finding cannot be recreated, it reduces our confidence in the original result and suggests that our current understanding of the system being studied or our methods of testing that system are insufficient.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Results}
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Survey Response Demographics}
+A total of \textit{n}=282 of the authors we contacted completed the online survey with information sufficient for analysis. 
+The contact rate for the survey was 17.7 percent, the response rate was 11.3 percent, yielding a cooperation rate of 64.0 percent. 
+The refusal rate was 6.4 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
+The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
+Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
+The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
+Respondents were similarly balanced across disciplinary subfields, but did contain a greater number of physical geographers  - human geography (26.8\%), physical geography (39.9\%), nature and society (14.8\%), geographic methods and GIScience (17.3\%).
+Different methodological approaches were well represented by respondents in the sample with qualitative researchers making up the smallest sub-group  - quantitative (47.3\%), qualitative (16.3\%), and mixed-methods (36.0\%).
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Researcher Definitions of Replication and its Epistemic Functions}
+\begin{itemize}
+    \item Coded analysis of Q6
+\end{itemize}
+
+A majority of respondents believe replications can serve epistemic functions.
+\begin{itemize}
+    \item Q7 control of chance 64.5\%
+    \item Q7 identify product of flawed design 59.7\%
+    \item Q7 construct validity 75.2\%
+    \item External validity population 62.9\%
+    \item External validity location 67.8\%
+    \item Human, Nature Society, and Qualitative researchers had lower agreement on each point.
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Replication - Chances and motivations}
+Q12-14 Researcher perspectives on frequency of replication
+\begin{itemize}
+    \item Q12 - Geographic researchers do not believe many studies in their field have been replicated.
+Respondents estimated that on average a quarter of recent studies in their sub-field have be replicated.
+However, the distribution was strongly right skewed with a median resposne of 20\% and a heavy tail of responses (46.9\%) estimating below 10\% of recent studies have been replicated.
+    \item Q13 - Respondents estimated that half of the recent studies in their sub-field could be replicated (55.0\%, $\sigma = 24.3\%$).
+While centered on 55\% responses were fairly evenly dispersed from 0-100 indicating no clear common belied about this value.
+    \item Q14 - Collectively, geographic researchers are also unclear on what percentage of studies should be replicated.
+Like 'could be replicated', respondents on average say half of studies should be replicated (55.9\%, $sigma=27.7\%$), but with a large variance and fairly flat histogram that indicates overall disagreement on the value of replicating a lot of studies.
+\end{itemize}
+
+Q8-11 Factors that affect the chances of replicating a claim.
+Researchers collectively indicated that only a few study characteristics of phenomenon characteristics would alter an independent researcher's chances of replicating a prior claim. 
+Researcher identified more study characteristics than phenomena characterstics, which may indicate they they are thinking of this through the lens of artifact availability from the prior study and not the nature of the phenomena.
+A small but notable percentage of researchers indicated that they simply did not know whether a factor would affect chances of replication.
+
+Only a subset of study characteristics were consistently identified by geographic researchers as altering the chances of replicating the claims of a prior study.
+\begin{itemize}
+    \item Agreement that quantitative studies are more likely to be replicable (80.6\%)
+    \item Poor documentation decreases chances of replication (74.9\%)
+    \item use of restricted data decreases chances (68.1\%)
+    \item Positionality seemed to give a lean to decrease (53.4\%)
+    \item Researcher views on most study characteristics were fairly evenly split across increase, decrease, no-effect.
+Indicating they were not seen as consistently important across the the discipline.
+    \item Minimal variation in responses across method groups or sub-fields. 
+\end{itemize}
+
+Phenomena
+\begin{itemize}
+    \item Spatial dependence lean to decrease chance of replication (41.0\%), but notable percentage of respondents (21.6\%) indicated not having a clear idea of whether this would matter.
+    \item Belief that strong relationship between a phenomenon and local conditions reduced chances of replication (59.7\%)
+    \item Fairly even spread across increase, decrease, no effect on exhibits variation across space.
+    \item When a phenomenon cannot be directly measured decreases chance of replication (61.5\%).
+    \item Really even distribution on nearly a phenomenon characteristics. Also a decently high percentage of i don't know resposnes for each characteristic. In most cases in the 10-20 percent range. 
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Conclusion}
+A standing question is how should geographic research approaches be designed to efficiently generate reliable knowledge.
+
+\theendnotes
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Acknowledgement(s)}
+We thank Tyler Hoffman for providing technical assistance in the development and execution of a set of trial queries using the Scopus API.
+
+\section*{Funding}
+This material is based on work supported by the National Science Foundation under Grant No. \textbf{BCS-2049837}.
+
+\section*{Notes on contributor(s)}
+\textbf{Kedron:} Conceptualization, Methodology, Writing - Original Draft, Writing - Review and Editing, Supervision, Project Administration, Funding Acquisition.
+\textbf{Holler:} Conceptualization, Methodology, Data Curation, Writing - Review and Editing, Funding Acquisition.
+\textbf{Bardin:} Conceptualization, Methodology, Writing - Original Draft, Writing - Review and Editing, Data Curation, Software.
+
+\newpage
+\bibliography{references}
+
+\newpage
+\noindent PETER KEDRON is an Associate Professor in the School of Geographical Science and Urban Planning and core faculty member in the Spatial Analysis Research Center (SPARC) at Arizona State University, Tempe, AZ, 85283, US.
+Email: Peter.Kedron@asu.edu.
+His research interests include spatial analysis, geographic information science, economic geography, and the accumulation of knowledge about geographic phenomena.
+\\
+
+\noindent JOSEPH HOLLER is an Assistant Professor of Geography at Middlebury College, Middlebury, VT, 05753, US. Email: \\
+
+\noindent SARAH BARDIN is a PhD candidate ...
+
 \end{document}

### 2023-05-22 docs/manuscript/manuscript.tex

@@
 \newtheorem{notation}{Notation}
+
+\usepackage{tabularx}
+\usepackage{booktabs,caption}
+\usepackage{threeparttable}
+
+\usepackage{lscape}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+For example, in a survey of 807 ecologists and evolutionary biologists, 64 percent admitted to failing to report non-significant results and 51 percent admitted to presenting unexpected findings as if they had been hypothesized from the start of the research \citep{fraser2018questionable}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection*{Survey Response Demographics}
-A total of \textit{n}=282 of the authors we contacted completed the online survey with information sufficient for analysis. 
+A total of \textit{n}=283 of the authors we contacted completed the online survey with information sufficient for analysis. 
 The contact rate for the survey was 17.7 percent, the response rate was 11.3 percent, yielding a cooperation rate of 64.0 percent. 
@@
 \subsection*{Researcher Definitions of Replication and its Epistemic Functions}
+\begin{itemize}
+    \item Respondents report thinking about replicability (73.9\%) talking with colleagues about replicability (65.0\%) and considering replicability when undertaking peer-review (59.0\%). 
+    \item Far fewer respondents report attempting replications (31.8\%). 
+\end{itemize}
+
 \begin{itemize}
@@
 \subsection*{Replication - Chances and motivations}
-Q12-14 Researcher perspectives on frequency of replication
-\begin{itemize}
-    \item Q12 - Geographic researchers do not believe many studies in their field have been replicated.
-Respondents estimated that on average a quarter of recent studies in their sub-field have be replicated.
-However, the distribution was strongly right skewed with a median resposne of 20\% and a heavy tail of responses (46.9\%) estimating below 10\% of recent studies have been replicated.
-    \item Q13 - Respondents estimated that half of the recent studies in their sub-field could be replicated (55.0\%, $\sigma = 24.3\%$).
-While centered on 55\% responses were fairly evenly dispersed from 0-100 indicating no clear common belied about this value.
-    \item Q14 - Collectively, geographic researchers are also unclear on what percentage of studies should be replicated.
-Like 'could be replicated', respondents on average say half of studies should be replicated (55.9\%, $sigma=27.7\%$), but with a large variance and fairly flat histogram that indicates overall disagreement on the value of replicating a lot of studies.
-\end{itemize}
+Overall geographic researchers believe that the majority of research in the discipline has not been independently replicated and appear to be uncertain about what proportion of literature could or should be replicated (Figure \ref{fig:Q12-HCS}).
+On average, respondents estimated that 25 percent of recent studies in their sub-field have be replicated. 
+However, this average likely overstates the percentage of studies researchers believe have been replicated because the response distribution is strongly right skewed.
+Our median response to this question is 20 percent and a heavy tail of containing 46.9 percent of responses estimated that less than 10 percent of recent studies have been replicated.
+On average, respondents estimated that approximately half of studies 'could be replicated' (55.0\%) or 'should be replicated' (55.9\%). 
+However, these averages are the product of the relatively flat distributions of estimates across the range of possible values. 
+The response to both questions was also highly variable (\textit{$sd_{could}=24.3\%$}, \textit{$sd_{should}=27.7\%$}) indicating no common knowledge or belief about the possibility or value of replicating recent work.
+
+\begin{center}
+\textbf{Insert Figure \ref{fig:Q12-HCS} About Here}
+\end{center}
 
@@
 Researchers collectively indicated that only a few study characteristics of phenomenon characteristics would alter an independent researcher's chances of replicating a prior claim. 
-Researcher identified more study characteristics than phenomena characterstics, which may indicate they they are thinking of this through the lens of artifact availability from the prior study and not the nature of the phenomena.
+Researcher identified more study characteristics than phenomena characteristics, which may indicate they they are thinking of this through the lens of artifact availability from the prior study and not the nature of the phenomena.
 A small but notable percentage of researchers indicated that they simply did not know whether a factor would affect chances of replication.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Factors that Affect the Decision to Attempt Replications}
+Introductory para summarizing section and introducing Figure 2
+
+\begin{center}
+\textbf{Insert Figure \ref{fig:Q15-DecisionFactors} About Here}
+\end{center}
+
+Geographic researchers identified current academic incentives as the factor most frequently impacting the decision to attempt or not attempt a replication study. 
+A majority of respondents identified the pressure to publish original research (77\%) and the lack of funding for replication studies (73\%) as frequently or always impacting the replication decision.
+Respondents also believed that the perception of replications as low value work (64\%) that was often difficult to publish (63\%) impacted researcher decision making.  
+Contrary to some narratives in the replication literature, the desire to identify fabricated data or results was not seen as a determining factor in the decision to attempt a replication. 
+However, this finding should be interpreted with caution as a third of our respondents indicated that they did not know whether potential fabrication influenced researcher decision making.
+
+Artifact Availability
+\begin{itemize}
+    \item See comment hanging off RE. That is the mains story on this one. 
+\end{itemize}
+
+Studt Characteristics
+\begin{itemize}
+    \item The characteristics of a study being replicated or the researcher attempting the replication were seen as less important by our respondents. 
+    \item Respondents did not see ethical concerns as a inhibitor or replication studies.
+\end{itemize}
+
+\begin{center}
+    \textbf{Insert Here Table \ref{tab:motivations}} 
+\end{center}
+
+Q16 - Include a presentation of the factors researchers identified that we did not include in the list of barriers.
+\begin{itemize}
+    \item Clerical issues related to field site access, costs, institutional approvals, 
+    \item Lack of conceptual or methodological frameworks (how to measure similarity) to place RPLs in
+    \item RPL is unnecessary in geog - (i) unique lens on world from each study is their main value, (ii) not valued across respondents from several disciplines and approaches.
+    \item Instability of the system being studied across space and time - Replication is not possible in geography because of spatial heterogeneity or the study of one-off events, temporal variation.
+\end{itemize}
+
+Q15 - A greater number of HG and QL responded that they did not know across all questions.
+Majority of QN researchers identified 'diff recreating proc' as impacting replication decision, minority for other groups.
+MM say 'low val of replication' as less impact on decision.
+HM and NS linked decision more to data access and recreation, while methods additionally linked to accessibility of methods info.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Replication Attempts}
+\begin{itemize}
+    \item sub-set demographics
+    \item Q18 - same location response to characterize the attempts
+    \item Q19 - Motivations
+    \item Q20-21 - Replication outcome to component accessibility comparison. Perhaps also a comparison of success across locations by field of study (depending on the numbers).
+    \item From Q21f percent that published their findings. The into Q22 why didn't respondents pursue publication.
+\end{itemize}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
@@
 
+\newpage
+\begin{landscape}
+\begin{table}[h]
+    \centering
+    \begin{threeparttable}
+    \caption{Factors Affecting Researcher Decisions to Undertake Replication Studies }
+    \begin{tabular}{l c c c c c c c c c c c c}
+         \hline
+                    & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & & & & \\
+         Barrier    & PH & MT & NS & HU            & & QN & MX & QL              & & Overall & N & Missing\\
+         \hline
+         \textit{Research Environment}      & & & & & & & & & & \\
+         Pressure to original publish       & 72.6\% & 71.4\% & 64.3\% & 53.9\% & & 76.2\% & 63.7\% & 43.5\% & & 66.4\% & 245 & 38 \\
+         Lack of funding for replication    & 64.6\% & 57.1\% & 69.0\% & 47.4\% & & 64.9\% & 59.8\% & 43.5\% & & 59.4\% & 231 & 51 \\
+         Low perceived value                & 61.9\% & 59.5\% & 55.1\% & 42.1\% & & 64.9\% & 50.9\% & 36.9\% & & 55.2\% & 242 & 41 \\
+         Difficulty publishing              & 50.5\% & 48.9\% & 57.1\% & 50.0\% & & 58.2\% & 47.1\% & 41.3\% & & 51.2\% & 231 & 51 \\
+         Fraud                              & 17.6\% & 18.4\% & 23.8\% & 18.4\% & & 20.9\% & 21.6\% & 6.5\%  & & 18.7\% & 189 & 94 \\
+                                            & & & & & & & & & & & & \\
+         \textit{Artifact Availability}     & & & & & & & & & & & & \\
+         Data inaccessibility               & 47.8\% & 57.1\% & 61.9\% & 43.9\% & & 56.7\% & 54.9\% & 41.3\% & & 53.7\% & 250 & 33 \\
+         Lack of methods information        & 40.7\% & 59.2\% & 50.0\% & 40.8\% & & 50.0\% & 46.1\% & 30.4\% & & 44.6\% & 250 & 33 \\
+         Inability to recreate procedure    & 38.1\% & 46.9\% & 40.4\% & 39.4\% & & 47.8\% & 36.3\% & 38.3\% & & 40.6\% & 246 & 37 \\
+                                            & & & & & & & & & & & & \\
+         \textit{Study/Researcher Characteristics}     & & & & & & & & & & & & \\
+         Geographic variation               & 35.3\% & 32.7\% & 33.3\% & 27.7\% & & 31.4\% & 35.3\% & 36.4\% & & 32.5\% & 214 & 69 \\
+         Inexperience with replication      & 27.4\% & 49.0\% & 50.0\% & 32.8\% & & 38.1\% & 37.3\% & 28.2\% & & 36.4\% & 229 & 54 \\
+         Low probability of success         & 29.2\% & 31.6\% & 31.0\% & 29.0\% & & 30.6\% & 31.4\% & 28.3\% & & 30.4\% & 236 & 47 \\
+         Ethical concerns                   & 10.5\% & 12.3\% & 21.4\% & 14.4\% & & 11.2\% & 18.6\% & 10.9\% & & 14.0\% & 218 & 68 \\
+                                            & & & & & & & & & & & & \\
+        \hline
+    \end{tabular}
+    \begin{tablenotes}
+        \footnotesize
+        \item Cells report the percentage of respondents reporting that a factor frequently, or always affect researchers' decision to attempt a replication of geographic research.
+Acronyms indicate: \textit{PH} Physical Geography, \textit{MT} GIScience and Methods, \textit{NS} Nature and Society, \textit{HU} Human Geography; \textit{QN} Quantitative, \textit{MX} Mixed Methods, \textit{QL} Qualitative.
+    \end{tablenotes}
+    \label{tab:motivations}
+    \end{threeparttable}
+\end{table}
+\end{landscape}
+
+%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[scale=0.5]{results/figures/Fig-Q12-HCS.png}
+    \caption{Estimates of the percentage of geographic studies that (a) have been replicated, (b) could be replicated, or (c) should be replicated}
+    \label{fig:Q12-HCS}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[scale=0.80]{results/figures/Fig-Q15-Decisions.png}
+    \caption{Factors Affecting Researcher Decisions to Undertake Replication Studies. Factors grouped by: Academic Incentives (AA), Artifact Accessibility (AA), Study Characteristics (SC).}
+    \label{fig:Q15-DecisionFactors}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%
 \newpage

### 2023-05-24 docs/manuscript/manuscript.tex
draft Fig2 results, insert Fig3

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Results}
+\section*{Data and Methods}
+Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Researcher Perceptions of Replication in Geography Repository (OSF WEBSITE).
+The repository connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
+All of the results presented in this paper can be independently reproduced using the materials in that repository.
+Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_RPl_Survey_PAP} - \url{https://osf.io/a4nwg}). 
+The survey was conducted under the approval and supervision of the Arizona State Institutional Review Board - \textit{STUDY00014232}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Survey Response Demographics}
+\subsection*{Sampling Frame}
+Our target population of interest is researchers who have recently published in the field of geography. 
+We followed a 4-step procedure to create a sampling frame for our survey that captures this diverse population of researchers.
+
+First, beginning at the publication level, we identified journals indexed as either geography or physical geography by the \href{https://access.clarivate.com/}{Web of Science's Journal Citation Reports} that also had a 5-year impact factor greater than 1.5.
+From those journals, we created a database of all articles published between 2017 and 2021.
+
+Second, we used Arizona State University's institutional subscription to the \href{https://www.scopus.com/home.uri}{Scopus Database} to extract journal information (e.g., subject area, ranking), article information (e.g., abstract, citation counts), and author information (e.g., corresponding status, email) for each publication.
+Because our intention was to capture individuals actively publishing new geographic research, we retained publications indexed by Scopus as \textit{document type = ``Article''} and removed all other publication types (e.g., editorials, book reviews) from our article database.
+We also removed articles with missing authorship information.
+
+Third, we created a list of researchers and their published articles, focusing on corresponding authors for two reasons.
+(1) Corresponding authorship is one indicator of the level of involvement an individual had in a given work. 
+While imperfect, it was the best available indicator in the Scopus database as across journals there is no commonly adopted policy for declarations of author work (e.g., CRediT Statements).
+(2) Scopus maintains email contact information for all corresponding authors, which gave us a means of contacting researchers in our sampling frame.
+Scopus also maintains a unique identifier for each author (author-id) across time, which allowed us to identify authors across publications.
+
+Fourth, we constructed a sampling frame of unique researchers and their most recent email contact information. 
+We determined uniqueness by grouping researchers by their author-id, and we determined the most recent contact information by selecting records associated with the most recent year of publication. 
+For 383 researchers who had two or more distinct emails in the latest year of publication, we removed non-institutional personal email addresses and then selected one of the remaining institutional email address.
+
+Applying these criteria yielded a sampling frame of 29,828 researchers. 
+On average, these authors published 2.7 articles in geography journals meeting our criteria between 2017 and 2021. 
+Roughly one-third (33.0\%) were most recently a corresponding author for an article published in a general geography journal. 
+A similar proportion (32.0\%) were most recently a corresponding author for an article published in an earth sciences journal, and smaller proportions had published in the social sciences and cultural geography (20.0\% and 16.0\%, respectively).
+
+\subsection*{Survey Instrument}
+The survey first established eligibility based on age and geographic research activity in the past five years and asked researchers to report their primary subfield and methodology.
+We asked each participant to assess their familiarity with the term ``replicability'' and to provide their own definition. 
+We then provided a definition based on the \citet{nosek2020replication}  to establish a common understanding of replicability for the remainder of the survey.
+Remaining questions assessed the epistomological purpose of a replication (5 questions), factors that impact the chances of successfully replicating a study (18 questions) or the decision to attempt a replication (13 questions), and what portion of the geographic literature has/could/should be replicated (3 questions).
+For researchers who reported attempting reproductions, we asked researcher to elaborate on their motivations and outcomes (9 questions).
+
+We developed the survey questions following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility and replicability literature.
+We pilot tested the survey instrument with \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
+After pilot testing, we removed these individuals from our sampling frame to ensure they would not be included in our final sample.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Data Collection}
+We used a digital form of the Tailored Design Method \citep{dillman2014internet} to survey geographic researchers between May 17 and June 10, 2022.
+A simple random sample of 2,000 researchers was drawn without replacement from our sampling frame, and those researchers were invited via email to participate in the online survey. 
+Researchers received their initial invitation on May 17, 2022. 
+Two reminder emails were sent to researchers that had not yet completed the survey on May 26 and May 31, 2022.
+
+The online survey was administered through \href{https://www.qualtrics.com/}{Qualtrics}. 
+Participation in the survey was entirely voluntary. 
+Each researcher that opted to participate in the survey was provided with IRB approved consent documentation and linked to the internet survey instrument. 
+Participants were also given the option to provide an email address for eligibility for one of three  prizes of 90 US\$, selected randomly after the data collection period.
+Participating researchers had the option to exit and re-enter the survey and were also able to review and change their answers using a back button as they progressed through the survey.
+At the end of the data collection period, responses were checked for completeness and coded using the reporting standards of the American Association For Public Opinion Research \citep{aaporstandards}.
+Responses were downloaded from Qualtrics, anonymized, and stored in a public de-identified database in the research compendium (self-identifying reference removed).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Results}
 A total of \textit{n}=283 of the authors we contacted completed the online survey with information sufficient for analysis. 
@@
 
+\begin{center}
+\textbf{Insert Figure \ref{fig:Q8-10-Chances} About Here}
+\end{center}
+
 %%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Factors that Affect the Decision to Attempt Replications}
-Introductory para summarizing section and introducing Figure 2
+Figure \ref{fig:Q15-DecisionFactors} presents how frequently geographic researchers believe differences in academic incentives (AI), the availability of research artifacts (AA), and study characteristics (SC) affect the decision to attempt to replicate existing geographic research.
+We highlight how often researchers identified a given factor as always or frequently influencing the decision to attempt a replication study and use a 50 percent threshold to indicate factors identified as important by a majority of respondents.
+Item response rate are included at the right of the figure.
 
@@
 
-Artifact Availability
-\begin{itemize}
-    \item See comment hanging off RE. That is the mains story on this one. 
-\end{itemize}
+Survey respondents also identified the availability of research artifacts as another set of factors impacting the decision to attempt replications of geographic research.
+Difficulty accessing and recreating data was the most commonly identified deterrent of replication with 61 percent of respondents naming this factor as frequently or always affecting the replication decision.
+Similarly, a slight majority of respondents (51\%) identified the accessibility of procedural and methodological information as a influencing factor. 
+The challenge of recreating the methods of a prior study elicited a similar response (47\%).
 
-Studt Characteristics
-\begin{itemize}
-    \item The characteristics of a study being replicated or the researcher attempting the replication were seen as less important by our respondents. 
-    \item Respondents did not see ethical concerns as a inhibitor or replication studies.
-\end{itemize}
+No characteristics of the original study, or the potential replication attempt, were identified by a majority of researchers as frequently or always impacting the replication decision. 
+However, a near majority of respondents did identify potential geographic variation in the phenomena being investigated (43\%) and inexperience conducting replication studies (45\%) as influencing researcher decisions to attempt or not attempt replications.
+Respondents did not see a low chance of successfully replicating a study as a deterrent to attempting a replication, but it is unclear whether this result is driven by a belief in the value of null replication results or the belief that replications in fact have high chances of success.
+Finally, researchers did not identify ethical concerns as a factor affecting the decision to attempt a replication study.
 
-\begin{center}
-    \textbf{Insert Here Table \ref{tab:motivations}} 
-\end{center}
+Respondents also identified a number of factors that were omitted from our survey instrument. 
+These factors include practical issues such as the difficulty identifying and accessing new field sites where data would be collected during a replication attempt, the costs of conducting a replication, and the time needed to obtain institutional approvals.
+Selected respondents also identified uncertainty about how to compare the  of results of a replication and an prior study as a factor impacting the decision to attempt a replication. 
+Finally, a small number of respondents believe that geographic researchers do not undertake replication studies because they either believe replication is not possible or not necessary in geography. 
+These researchers argued that the main value of geographic studies is that each study provide a unique lens on the portion of the world under investigation, which makes replication a unnecessary endeavour.
 
-Q16 - Include a presentation of the factors researchers identified that we did not include in the list of barriers.
-\begin{itemize}
-    \item Clerical issues related to field site access, costs, institutional approvals, 
-    \item Lack of conceptual or methodological frameworks (how to measure similarity) to place RPLs in
-    \item RPL is unnecessary in geog - (i) unique lens on world from each study is their main value, (ii) not valued across respondents from several disciplines and approaches.
-    \item Instability of the system being studied across space and time - Replication is not possible in geography because of spatial heterogeneity or the study of one-off events, temporal variation.
-\end{itemize}
-
-Q15 - A greater number of HG and QL responded that they did not know across all questions.
-Majority of QN researchers identified 'diff recreating proc' as impacting replication decision, minority for other groups.
-MM say 'low val of replication' as less impact on decision.
-HM and NS linked decision more to data access and recreation, while methods additionally linked to accessibility of methods info.
+Respondents from different disciplinary sub-fields and methodological approaches varied little in their identification of the factors affecting researchers' decisions to attempt a replication studies.
+Human geographers and researchers using quantitative methods less frequently identified academic incentives as important to the replication decision when compared to other sub-groups, but were otherwise broadly similar in their views on artifact availability and study characteristics.
+A greater percentage of quantitative researchers and those working in the areas of GIScience and Methods identified the accessibility of data and methodological information as more commonly impacting the decision to replicate, but not at a level that was substantially higher than other sub-groups.
+In fact, a greater percentage of researchers studying nature and society identified data accessibility as important than did methods researchers.  
+Overall, the differences we observed across sub-groups was small and should be interpreted with caution given the sub-group sample sizes.
+We also found that human geographers and qualitative researchers were disproportionately likely to provide 'I do not know' responses across questions,  
+which further decreases the amount of information available about their views and beliefs.
 
@@
     \centering
+    \includegraphics[scale=0.8]{results/figures/Fig-Q8-10-Chances.png}
+    \caption{Factors affecting the chances of replicating a study.
+Respondents identified (a) how likely study characteristics were to alter the chances of successfully replicating a study and (b) how likely the characteristics of the phenomenon under investigation were to alter the chances of successfully replicating a study in a new location.
+Acronyms indicate: artifact accessibility (AA), researcher characteristics (RC), study approach (SA), and phenomenon characteristics (PC); and the percentage of 'don't know' (DK) and missing (M) responses.
+Unlikely to affect replication chances is omitted, but can be calculated from available data.}
+    \label{fig:Q8-10-Chances}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+\begin{figure}[hbt!]
+    \centering
     \includegraphics[scale=0.80]{results/figures/Fig-Q15-Decisions.png}

### 2023-07-26 docs/manuscript/manuscript.tex
Updates from Overleaf

@@
 A total of \textit{n}=283 of the authors we contacted completed the online survey with information sufficient for analysis. 
-The contact rate for the survey was 17.7 percent, the response rate was 11.3 percent, yielding a cooperation rate of 64.0 percent. 
-The refusal rate was 6.4 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
+The contact rate for the survey was 18.8 percent, the response rate was 14.1 percent, yielding a cooperation rate of 74.4 percent. 
+The refusal rate was 4.8 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
 The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
@@
 \subsection*{Replication - Chances and motivations}
-Overall geographic researchers believe that the majority of research in the discipline has not been independently replicated and appear to be uncertain about what proportion of literature could or should be replicated (Figure \ref{fig:Q12-HCS}).
+Overall respondents believe that the majority of research in the discipline has not been independently replicated and appear to be uncertain about what proportion of the literature could or should be replicated (Figure \ref{fig:Q12-HCS}).
 On average, respondents estimated that 25 percent of recent studies in their sub-field have be replicated. 
-However, this average likely overstates the percentage of studies researchers believe have been replicated because the response distribution is strongly right skewed.
-Our median response to this question is 20 percent and a heavy tail of containing 46.9 percent of responses estimated that less than 10 percent of recent studies have been replicated.
+However, the distribution of these responses is strongly right skewed.
+In fact, 46.9 percent of respondents estimated that less than 10 percent of recent studies have been replicated.
+It is unclear if respondents believe recent geographic research could or should be replicated.
 On average, respondents estimated that approximately half of studies 'could be replicated' (55.0\%) or 'should be replicated' (55.9\%).
-However, these averages are the product of the relatively flat distributions of estimates across the range of possible values. 
-The response to both questions was also highly variable (\textit{$sd_{could}=24.3\%$}, \textit{$sd_{should}=27.7\%$}) indicating no common knowledge or belief about the possibility or value of replicating recent work.
+However, the distribution of responses to both questions are relatively flat across the range of possible values and highly variable (\textit{$sd_{could}=24.3\%$}, \textit{$sd_{should}=27.7\%$}), which suggests
+respondents were uncertain whether it was possible or valuable to replicate recent research.
 
@@
 
-Q8-11 Factors that affect the chances of replicating a claim.
-Researchers collectively indicated that only a few study characteristics of phenomenon characteristics would alter an independent researcher's chances of replicating a prior claim. 
+Respondents identified a range of factors that might impact the chances of an independent researcher replicating the claims of a prior study (Figure \ref{fig:Q8-10-Chances}a).
+A majority of respondents identified the transparency and availability of the components of a study as affecting the odds of replication. 
+Poor documentation of the original study (75\%) and the use of restricted access data (68\%) were seen by the greatest number of respondents as decreasing the odds of replication. 
+Some respondents identified the inclusion of multiple sites in a study as increasing the chances of an independent replication of the findings of that study, but not in great enough numbers to constitute a majority.
+
+The characteristics of the research team that conducted the original study were generally not identified by respondents as likely to change the changes of replicating that study. 
+Respondents were nearly evenly split as to whether a large research team working on a study increased of decreased the chances of replicating that study. 
+On the whole, more respondents believed that reliance on the unique expertise of the research team conducting a study, or the position adopted by that team would decrease, rather than increase, the chances of replicating the claims of a study.
+However, only 54 percent of respondents thought the position a research team chose to adopt when conducting study would decrease the chances of replicating that study. 
+Similarly, 49 percent of respondents identified reliance on the unique expertise of the original researcher team as decreasing the odds of replicating a study.
+
+\vspace{5mm}
+
 Researcher identified more study characteristics than phenomena characteristics, which may indicate they they are thinking of this through the lens of artifact availability from the prior study and not the nature of the phenomena.
@@
     \item Agreement that quantitative studies are more likely to be replicable (80.6\%)
-    \item Poor documentation decreases chances of replication (74.9\%)
-    \item use of restricted data decreases chances (68.1\%)
-    \item Positionality seemed to give a lean to decrease (53.4\%)
-    \item Researcher views on most study characteristics were fairly evenly split across increase, decrease, no-effect.
-Indicating they were not seen as consistently important across the the discipline.
     \item Minimal variation in responses across method groups or sub-fields. 
@@
 \subsection*{Factors that Affect the Decision to Attempt Replications}
-Figure \ref{fig:Q15-DecisionFactors} presents how frequently geographic researchers believe differences in academic incentives (AI), the availability of research artifacts (AA), and study characteristics (SC) affect the decision to attempt to replicate existing geographic research.
-We highlight how often researchers identified a given factor as always or frequently influencing the decision to attempt a replication study and use a 50 percent threshold to indicate factors identified as important by a majority of respondents.
-Item response rate are included at the right of the figure.
+Several factors appear to affect whether researchers decide to attempt to replicate recent geographic research.
+Figure \ref{fig:Q15-DecisionFactors} presents how frequently respondents believe differences in academic incentives (AI), the availability of research artifacts (AA), and study characteristics (SC) affect researchers' decisions to attempt to replicate existing geographic research.
+Response characteristics for each factor are recorded at the right of the figure.
 
@@
 
-Geographic researchers identified current academic incentives as the factor most frequently impacting the decision to attempt or not attempt a replication study. 
-A majority of respondents identified the pressure to publish original research (77\%) and the lack of funding for replication studies (73\%) as frequently or always impacting the replication decision.
-Respondents also believed that the perception of replications as low value work (64\%) that was often difficult to publish (63\%) impacted researcher decision making.  
+Geographic researchers identified current academic incentives as the factor most frequently impacting the decision to attempt a replication study. 
+A majority of respondents identified the pressure to publish original research (77\%) and the lack of funding for replication studies (73\%) as frequently or always impacting the decision to attempt a replication.
+Respondents also believed that the perception of replications as low value work (64\%) that was often difficult to publish (63\%) also impacted decision making.  
 Contrary to some narratives in the replication literature, the desire to identify fabricated data or results was not seen as a determining factor in the decision to attempt a replication. 
-However, this finding should be interpreted with caution as a third of our respondents indicated that they did not know whether potential fabrication influenced researcher decision making.
+However, this finding should be interpreted with caution as a third of respondents indicated that they did not know whether potential fabrication influenced researcher decision making.
 
-Survey respondents also identified the availability of research artifacts as another set of factors impacting the decision to attempt replications of geographic research.
-Difficulty accessing and recreating data was the most commonly identified deterrent of replication with 61 percent of respondents naming this factor as frequently or always affecting the replication decision.
-Similarly, a slight majority of respondents (51\%) identified the accessibility of procedural and methodological information as a influencing factor. 
+Respondents also identified the availability of research artifacts as important to the decision to attempt a replication study.
+Respondents believe that difficulty accessing and recreating data (61\%) frequently or always affects the replication decision.
+Similarly, a slight majority of respondents (51\%) identified the accessibility of procedural and methodological information as a influential factor. 
 The challenge of recreating the methods of a prior study elicited a similar response (47\%).
@@
 No characteristics of the original study, or the potential replication attempt, were identified by a majority of researchers as frequently or always impacting the replication decision. 
-However, a near majority of respondents did identify potential geographic variation in the phenomena being investigated (43\%) and inexperience conducting replication studies (45\%) as influencing researcher decisions to attempt or not attempt replications.
-Respondents did not see a low chance of successfully replicating a study as a deterrent to attempting a replication, but it is unclear whether this result is driven by a belief in the value of null replication results or the belief that replications in fact have high chances of success.
-Finally, researchers did not identify ethical concerns as a factor affecting the decision to attempt a replication study.
+However, a near majority of respondents did identify potential geographic variation in the phenomena being investigated (43\%) and inexperience conducting replication studies (45\%) as influencing decisions to attempt replications.
+Respondents did not see a low chance of successfully replicating a study as a deterrent to attempting a replication, but it is unclear whether this result is driven by a belief in the value of null replication results, or the belief that replications in fact have high chances of success.
+Finally, respondents did not identify ethical concerns as a factor affecting the decision to attempt a replication study.
 
-Respondents also identified a number of factors that were omitted from our survey instrument. 
+Respondents identified a number of factors that were omitted from our survey instrument as important when deciding whether to attempt a replication of a geographic study. 
 These factors include practical issues such as the difficulty identifying and accessing new field sites where data would be collected during a replication attempt, the costs of conducting a replication, and the time needed to obtain institutional approvals.
-Selected respondents also identified uncertainty about how to compare the  of results of a replication and an prior study as a factor impacting the decision to attempt a replication. 
-Finally, a small number of respondents believe that geographic researchers do not undertake replication studies because they either believe replication is not possible or not necessary in geography. 
-These researchers argued that the main value of geographic studies is that each study provide a unique lens on the portion of the world under investigation, which makes replication a unnecessary endeavour.
+Respondents also identified uncertainty about how to compare the results of a replication attempt to the original as important to the replication decision.. 
+Finally, a small number of respondents believe that geographic researchers do not undertake replication studies because those researchers either believe replication is not possible or not necessary in geography.
+These respondents argued that the main value of geographic studies is that each study provide a unique lens on the portion of the world under investigation, which makes replication a unnecessary endeavour.
 
-Respondents from different disciplinary sub-fields and methodological approaches varied little in their identification of the factors affecting researchers' decisions to attempt a replication studies.
+Respondents from different disciplinary sub-fields and methodological approaches varied little in their identification of the factors affecting researchers' decisions to attempt replication studies. 
 Human geographers and researchers using quantitative methods less frequently identified academic incentives as important to the replication decision when compared to other sub-groups, but were otherwise broadly similar in their views on artifact availability and study characteristics.
-A greater percentage of quantitative researchers and those working in the areas of GIScience and Methods identified the accessibility of data and methodological information as more commonly impacting the decision to replicate, but not at a level that was substantially higher than other sub-groups.
+A greater percentage of quantitative researchers and those working in the areas of GIScience and Methods identified the accessibility of data and methodological information as more often impacting the decision to replicate, but not at a level that was substantially higher than other sub-groups.
 In fact, a greater percentage of researchers studying nature and society identified data accessibility as important than did methods researchers.
+
 Overall, the differences we observed across sub-groups was small and should be interpreted with caution given the sub-group sample sizes.
@@
 Respondents identified (a) how likely study characteristics were to alter the chances of successfully replicating a study and (b) how likely the characteristics of the phenomenon under investigation were to alter the chances of successfully replicating a study in a new location.
-Acronyms indicate: artifact accessibility (AA), researcher characteristics (RC), study approach (SA), and phenomenon characteristics (PC); and the percentage of 'don't know' (DK) and missing (M) responses.
+Acronyms indicate: artifact accessibility (AA), researcher characteristics (RC), study approach (SA), and phenomenon characteristics (PC); and the percentage of `don't know' (DK) and missing (M) responses.
 Unlikely to affect replication chances is omitted, but can be calculated from available data.}

### 2023-07-26 docs/manuscript/manuscript.tex
Update figs, correct in-text percent, results additions

@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Replication - Chances and motivations}
+\subsection*{Factors Affecting the Chances of Replicating a Prior Study}
 Overall respondents believe that the majority of research in the discipline has not been independently replicated and appear to be uncertain about what proportion of the literature could or should be replicated (Figure \ref{fig:Q12-HCS}).
@@
 A majority of respondents identified the transparency and availability of the components of a study as affecting the odds of replication. 
-Poor documentation of the original study (75\%) and the use of restricted access data (68\%) were seen by the greatest number of respondents as decreasing the odds of replication. 
+Poor documentation of the original study (74.9\%) and the use of restricted access data (66.1\%) were seen by the greatest number of respondents as decreasing the odds of being able to replicate a prior result.
 Some respondents identified the inclusion of multiple sites in a study as increasing the chances of an independent replication of the findings of that study, but not in great enough numbers to constitute a majority.
@@
 The characteristics of the research team that conducted the original study were generally not identified by respondents as likely to change the changes of replicating that study. 
-Respondents were nearly evenly split as to whether a large research team working on a study increased of decreased the chances of replicating that study. 
+The majority of respondents (51.2\%) indicated that a large research team working on the prior study would have no effect on the chances of an independent researcher replicating that work. 
+The remaining respondents were nearly evenly split as to whether a large team would increase of decrease the chances of replicating that study. 
 On the whole, more respondents believed that reliance on the unique expertise of the research team conducting a study, or the position adopted by that team would decrease, rather than increase, the chances of replicating the claims of a study.
-However, only 54 percent of respondents thought the position a research team chose to adopt when conducting study would decrease the chances of replicating that study. 
-Similarly, 49 percent of respondents identified reliance on the unique expertise of the original researcher team as decreasing the odds of replicating a study.
+However, only 53.4 percent of respondents thought the position a research team chose to adopt when conducting study would decrease the chances of replicating that study. 
+Similarly, 48.8 percent of respondents identified reliance on the unique expertise of the original researcher team as decreasing the odds of replicating a study. 
+In both cases, 24 percent of respondents reported that they did not believe either factor would impact the odds of replicating a prior result.
+
+Respondents were similarly divided about the extend to which the approach adopted in the prior study would affect the chances of replicating that study. 
+Respondents were nearly evenly split as to whether the number of hypotheses tested by a study, and whether that study used qualitative or mixed methods would increase or decrease an independent researcher's chances of finding results that supported the claims of the prior study.
+About a quarter of respondents said that use of a mixed methods approach or the testing of multiple hypotheses had no effect on the chances of replication.
+In contrast, a large majority (80.6\%) of respondents identified the use of quantitative methods in a prior study as increasing the chances of replicating that study. 
+This result matches the association observed in respondent definitions of replication, which ties replication to positivist science and quantitative approaches to knowledge creation.
+
+\begin{itemize}
+    \item Minimal variation in responses across method groups or sub-fields. 
+\end{itemize}
 
@@
 
-Researcher identified more study characteristics than phenomena characteristics, which may indicate they they are thinking of this through the lens of artifact availability from the prior study and not the nature of the phenomena.
-A small but notable percentage of researchers indicated that they simply did not know whether a factor would affect chances of replication.
-
-Only a subset of study characteristics were consistently identified by geographic researchers as altering the chances of replicating the claims of a prior study.
-\begin{itemize}
-    \item Agreement that quantitative studies are more likely to be replicable (80.6\%)
-    \item Minimal variation in responses across method groups or sub-fields. 
-\end{itemize}
+\begin{center}
+\textbf{Insert Figure \ref{fig:Q8-10-Chances} About Here}
+\end{center}
 
@@
 \end{itemize}
-
-\begin{center}
-\textbf{Insert Figure \ref{fig:Q8-10-Chances} About Here}
-\end{center}
 
@@
 Geographic researchers identified current academic incentives as the factor most frequently impacting the decision to attempt a replication study. 
-A majority of respondents identified the pressure to publish original research (77\%) and the lack of funding for replication studies (73\%) as frequently or always impacting the decision to attempt a replication.
-Respondents also believed that the perception of replications as low value work (64\%) that was often difficult to publish (63\%) also impacted decision making.  
+A majority of respondents identified the pressure to publish original research (66\%) and the lack of funding for replication studies (59\%) as frequently or always impacting the decision to attempt a replication.
+Respondents also believed that the perception of replications as low value work (55\%) that was often difficult to publish (51\%) also impacted decision making.  
 Contrary to some narratives in the replication literature, the desire to identify fabricated data or results was not seen as a determining factor in the decision to attempt a replication. 
@@
 Respondents also identified the availability of research artifacts as important to the decision to attempt a replication study.
-Respondents believe that difficulty accessing and recreating data (61\%) frequently or always affects the replication decision.
-Similarly, a slight majority of respondents (51\%) identified the accessibility of procedural and methodological information as a influential factor. 
-The challenge of recreating the methods of a prior study elicited a similar response (47\%).
+Respondents believe that difficulty accessing and recreating data (54\%) frequently or always affects the replication decision.
+Similarly, respondents (45\%) identified the accessibility of procedural and methodological information as a influential factor. 
+The challenge of recreating the methods of a prior study elicited a similar response (41\%).
 
 No characteristics of the original study, or the potential replication attempt, were identified by a majority of researchers as frequently or always impacting the replication decision. 
-However, a near majority of respondents did identify potential geographic variation in the phenomena being investigated (43\%) and inexperience conducting replication studies (45\%) as influencing decisions to attempt replications.
-Respondents did not see a low chance of successfully replicating a study as a deterrent to attempting a replication, but it is unclear whether this result is driven by a belief in the value of null replication results, or the belief that replications in fact have high chances of success.
+However, some respondents did identify inexperience conducting replication studies (37\%) and potential geographic variation in the phenomena being investigated (33\%) as always or frequently influencing decisions to attempt replications.
+Moreover, many respondents also saw these factors as occasionally affecting the decision to attempt a replication.
+Few respondents see a low chance of successfully replicating a study as a deterrent to attempting a replication, but it is unclear whether this result is driven by a belief in the value of null replication results, or the belief that replications in fact have high chances of success.
 Finally, respondents did not identify ethical concerns as a factor affecting the decision to attempt a replication study. 
+However, several of these results should also be interpreted with caution. 
+More that 15 percent of respondents replied that they did not know whether geographic variation, inexperience with replication, or ethical concerns would affect a researcher's decision to attempt a replication.
 
@@
 These factors include practical issues such as the difficulty identifying and accessing new field sites where data would be collected during a replication attempt, the costs of conducting a replication, and the time needed to obtain institutional approvals.
-Respondents also identified uncertainty about how to compare the results of a replication attempt to the original as important to the replication decision.. 
-Finally, a small number of respondents believe that geographic researchers do not undertake replication studies because those researchers either believe replication is not possible or not necessary in geography.
+Respondents also identified uncertainty about how to compare the results of a replication attempt to the original as important when deciding to undertake a replication attempt. 
+Finally, a small number of respondents believe that geographic researchers do not undertake replication studies because they either believe that replication is not possible or not necessary in geography.
 These respondents argued that the main value of geographic studies is that each study provide a unique lens on the portion of the world under investigation, which makes replication a unnecessary endeavour.
@@
 In fact, a greater percentage of researchers studying nature and society identified data accessibility as important than did methods researchers.
+
+\begin{center}
+\textbf{Insert Table \ref{tab:motivations} About Here}
+\end{center}
 
@@
          \textit{Study/Researcher Characteristics}     & & & & & & & & & & & & \\
+         Inexperience with replication      & 27.4\% & 49.0\% & 50.0\% & 32.8\% & & 38.1\% & 37.3\% & 28.2\% & & 36.4\% & 229 & 54 \\
          Geographic variation               & 35.3\% & 32.7\% & 33.3\% & 27.7\% & & 31.4\% & 35.3\% & 36.4\% & & 32.5\% & 214 & 69 \\
-         Inexperience with replication      & 27.4\% & 49.0\% & 50.0\% & 32.8\% & & 38.1\% & 37.3\% & 28.2\% & & 36.4\% & 229 & 54 \\
          Low probability of success         & 29.2\% & 31.6\% & 31.0\% & 29.0\% & & 30.6\% & 31.4\% & 28.3\% & & 30.4\% & 236 & 47 \\

### 2023-08-01 docs/manuscript/manuscript.tex
Completed Fig 2 write up

@@
 
-\begin{itemize}
-    \item Minimal variation in responses across method groups or sub-fields. 
-\end{itemize}
-
-\vspace{5mm}
-
 \begin{center}
@@
 
-Phenomena
-\begin{itemize}
-    \item Spatial dependence lean to decrease chance of replication (41.0\%), but notable percentage of respondents (21.6\%) indicated not having a clear idea of whether this would matter.
-    \item Belief that strong relationship between a phenomenon and local conditions reduced chances of replication (59.7\%)
-    \item Fairly even spread across increase, decrease, no effect on exhibits variation across space.
-    \item When a phenomenon cannot be directly measured decreases chance of replication (61.5\%).
-    \item Really even distribution on nearly a phenomenon characteristics. Also a decently high percentage of i don't know resposnes for each characteristic. In most cases in the 10-20 percent range. 
-\end{itemize}
+There was less agreement among respondents about whether different characteristics of a phenomenon would impact the chances of replicating the claims made by a prior study of that phenomenon (Figure \ref{fig:Q8-10-Chances}b).
+For all six of the characteristics we examined, at least 12 percent of respondents replied that those factors would have no effect on the chances of replicating a prior study.
+Numerous respondents also replied that they the simply did not know whether a characteristic would impact the chances of replicating a study. 
+For example, 20 percent of respondents said they did not know whether a phenomenon being spatially dependent with itself would affect the chances of replicating a prior study, and an additional 15 percent of respondents said spatial dependence would have no effect on replication.
+Even with this uncertainty, 41 percent of respondents said the presence of spatial dependence was likely to decrease the chances of replicating a prior study.
+
+A majority of respondents did identify the inability to directly measure a phenomenon (61.5\%) and a strong relationship between a phenomenon and local conditions (59.7\%) as reducing the chances of replicating a prior study.
+Respondents were roughly evenly divided on whether other factors would increase or decrease the chances of replicating a study.
+Respondents also favored 'somewhat likely' responses over stronger 'very likely' responses across all characteristics, which further suggests that absence of a clear consensus understanding of how these factors relate to and impact replication.
 
@@
 \subsection*{Factors that Affect the Decision to Attempt Replications}
-Several factors appear to affect whether researchers decide to attempt to replicate recent geographic research.
-Figure \ref{fig:Q15-DecisionFactors} presents how frequently respondents believe differences in academic incentives (AI), the availability of research artifacts (AA), and study characteristics (SC) affect researchers' decisions to attempt to replicate existing geographic research.
-Response characteristics for each factor are recorded at the right of the figure.
-
-\begin{center}
-\textbf{Insert Figure \ref{fig:Q15-DecisionFactors} About Here}
-\end{center}
-
+Several factors appear to affect whether researchers decide to attempt to replicate recent geographic research (Figure \ref{fig:Q15-DecisionFactors}).
 Geographic researchers identified current academic incentives as the factor most frequently impacting the decision to attempt a replication study. 
@@
 However, this finding should be interpreted with caution as a third of respondents indicated that they did not know whether potential fabrication influenced researcher decision making.
+
+\begin{center}
+\textbf{Insert Figure \ref{fig:Q15-DecisionFactors} About Here}
+\end{center}
 
@@
 Respondents identified (a) how likely study characteristics were to alter the chances of successfully replicating a study and (b) how likely the characteristics of the phenomenon under investigation were to alter the chances of successfully replicating a study in a new location.
-Acronyms indicate: artifact accessibility (AA), researcher characteristics (RC), study approach (SA), and phenomenon characteristics (PC); and the percentage of `don't know' (DK) and missing (M) responses.
-Unlikely to affect replication chances is omitted, but can be calculated from available data.}
+Acronyms indicate: artifact accessibility (AA), researcher characteristics (RC), study approach (SA), and phenomenon characteristics (PC); and the percentage of no effect (NE), `don't know' (DK), and missing (M) responses.}
     \label{fig:Q8-10-Chances}
@@
     \includegraphics[scale=0.80]{results/figures/Fig-Q15-Decisions.png}
-    \caption{Factors Affecting Researcher Decisions to Undertake Replication Studies. Factors grouped by: Academic Incentives (AA), Artifact Accessibility (AA), Study Characteristics (SC).}
+    \caption{Factors Affecting Researcher Decisions to Undertake Replication Studies.
+Factors grouped by: Academic Incentives (AA), Artifact Accessibility (AA), Study Characteristics (SC); and the percentage `don't know' (DK) and missing (M) responses.}
     \label{fig:Q15-DecisionFactors}

### 2023-08-14 docs/presentation/data/constants.R
viz: import work from OR-RPr

@@ -1,0 +1,107 @@
+library(shiny)
+library(plotly)
+
+# Group definitions ####
+subfields <- list("Human", "Methods", "Nature/society", "Physical")
+types <- list("Quantitative", "Qualitative", "Mixed Methods")
+geo_groups <- list(
+  "Everyone",
+  "Subfield" = subfields,
+  "Type" = types
+)
+
+# Columns to cast as factors ####
+four_levels <- c("Not at all", "Very little", "Somewhat", "To a great extent")
+four_level_cols <- c("Q5_familiarity")
+
+# Q7 Levels of agreement ####
+agree_levels <- c("Strongly disagree", "Disagree", "Don't know", "Agree", "Strongly agree")
+
+# Q7 questions text ####
+q7_text <- c(
+  Q7_value_1 = "Claim is the product of chance",
+  Q7_value_2 = "Result is the product of a flawed research design",
+  Q7_value_3 = "Observations and analyses reflect the concepts they are intended to represent",
+  Q7_value_4 = "Claim will hold in other populations (e.g., different age groups)",
+  Q7_value_5 = "Claim will hold in other locations"
+)
+
+# Q17 questions text ####
+q17_text <- c(
+  Q17_rep_behavior_1 = "Thought about the replicability of your research",
+  Q17_rep_behavior_2 = "Spoke with colleagues about replicability",
+  Q17_rep_behavior_3 = "Questioned the replicability of published research",
+  Q17_rep_behavior_4 = "Considered replicability while peer reviewing a research proposal or publication",
+  Q17_rep_behavior_5 = "Attempted to replicate prior research claims"
+)
+
+# Q15 questions text ####
+q15_text <- c(
+  Q15_1 = "Pressure to publish original research",
+  Q15_2 = "Low value of replication studies",
+  Q15_3 = "Low chances of replicating a result",
+  Q15_4 = "Lack of experience conducting replications",
+  Q15_5 = "Difficulty publishing peer-reviewed replications",
+  Q15_6 = "Difficulty accessing/creating relevant data",
+  Q15_7 = "Insufficient information about original methods",
+  Q15_8 = "Difficulty recreating similar procedures",
+  Q15_9 = "Lack of funding for replication studies",
+  Q15_10 = "Fabrication of data or results by original authors",
+  Q15_11 = "Ethical concerns",
[…]

### 2023-08-14 docs/presentation/global.R

@@ -1,0 +1,40 @@
+# Packages ####
+library(shiny)
+library(plotly)
+library(stringr)
+library(tidyverse)
+library(wordcloud2)
+library(shinycssloaders)
+
+# theme to match HTML
+thematic::thematic_shiny(font = "auto")
+
+# colors for likert
+pal <- c("#DF4949", "#E27A3F", "#BEBEBE", "#45B29D", "#334D5C")
+
+# plot height as CSS
+plot_height <- "60vh"
+plot_full_height <- "80vh"
+
+# text width for axis labels
+width <- 20
+
+# spinner
+spin <- function(plt) {
+  shinycssloaders::withSpinner(
+    plt,
+    type = 4,
+    color = "#1D5B79",
+    size = 2,
+    hide.ui = FALSE
+  )
+}
+
+source("data/constants.R")
+
+# load data ####
+analysis <- readRDS("data/analysis.rds")
+
+clouds_q6 <- readRDS("data/clouds_q6.rds")
+clouds_q19 <- readRDS("data/clouds_q19.rds")
+q7 <- readRDS("data/q7.rds")

### 2023-08-14 docs/presentation/server.R

@@ -1,0 +1,277 @@
+# server function ####
+function(input, output, session) {
+  # Data ####
+  d <- reactive({
+    analysis %>%
+      # No idea why ifelse and if_else don't work
+      dplyr::filter(
+        if (input$group %in% subfields) {
+          .data$Q3_recoded == input$group
+        } else if (input$group %in% types) {
+          .data$Q4_quantqual == input$group
+        } else {
+          TRUE
+        }
+      )
+  }) %>%
+    bindCache(input$group) %>%
+    bindEvent(input$group)
+
+  # Q5 plots ####
+  output$q5 <- renderPlotly({
+    fig1 <- d() %>%
+      count(Q5_familiarity) %>%
+      plot_ly(
+        x = ~Q5_familiarity,
+        y = ~n,
+        type = "bar",
+        # https://community.plotly.com/t/33731
+        hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
+      )
+
+    fig2 <- plot_ly(
+      type = "bar"
+    )
+
+    fig3 <- plot_ly(
+      type = "bar"
+    )
+
+    plotly::subplot(fig1, fig2, fig3, nrows = 1, shareY = TRUE) %>%
+      plt_layout(showlegend = FALSE) %>%
+      plt_config(
+        filename = paste0(
+          "repli_awareness_",
+          input$group %>%
+            tolower() %>%
+            gsub("[^a-z0-9]", "_", .)
+        )
+      )
+  }) %>%
+    bindCache(input$group)
+
+
+  # Q7 likert ####
+  output$q7 <- renderPlotly({
+    plt <- q7[[input$group]] %>%
+      # ggplot
+      ggplot() +
+      geom_segment(aes(
+        x = fct_rev(name),
+        y = start,
+        xend = name, yend = start + perc,
+        colour = value,
+        text = paste0(
+          "<b>", value, "</b><br>",
+          n, " people<br>",
+          round(perc * 100, 2), " %"
+        )
+      ), linewidth = 12) +
+      geom_hline(yintercept = 0, color = c("#646464")) +
+      coord_flip() +
+      scale_color_manual("Response", values = pal, guide = "legend") +
+      labs(title = "", y = "Percent", x = "") +
+      scale_x_discrete(
+        labels = str_wrap(rev(q7_text), width = 40)
+      ) +
+      scale_y_continuous(labels = scales::percent) +
+      theme_minimal() +
+      theme(
[…]

### 2023-08-14 docs/presentation/ui.R

@@ -1,0 +1,263 @@
+# UI tags ####
+tagList(
+  # head
+  tags$head(
+    tags$link(rel = "stylesheet", type = "text/css", href = "style.css"),
+    tags$link(rel = "shortcut icon", href = "favicon.png"),
+  ),
+  navbarPage(
+    title = "Replicability in Geographic Research",
+
+    # customization
+    id = "activeTab",
+    theme = bslib::bs_theme(
+      fg = "#212529", primary = "#1D5B79", secondary = "#C5DFF8",
+      success = "#8EAC50", info = "#468B97", warning = "#F1C93B",
+      base_font = bslib::font_google("Fira Sans"),
+      code_font = bslib::font_google("Fira Code"),
+      bootswatch = "flatly", bg = "#FFFFFF"
+    ),
+    windowTitle = "Replicability in Geographic Research",
+    # Access with `Shiny.shinyapp.$inputValues`
+    header = # conditionalPanel(
+    # condition = "input.activeTab !== 'Word Cloud'",
+      selectInput(
+        "group", h5("Choose a group:"),
+        geo_groups,
+      ),
+    # ),
+
+    # About ####
+    tabPanel(
+      "About",
+      icon = icon("info"),
+      fluidRow(
+        column(
+          12,
+          # col-sm-12
+          class = "col-lg-10 col-xl-8 col-xxl-6",
+          style = "margin-left: 3vw;",
+          markdown(
+            "
+            # TODO: edit this
+            ### Welcome
+            This is an interactive data visualization for
+            *Reproducible Research Practices and Barriers to Reproducible Research in Geography:Insights from a Survey*
+            by Peter Kedron, Joseph Holler, and Sarah Bardin.
+
+            The purpose of the survey was to systematically develop a baseline of information
+            about the state of replicability in geography
+            and to identify any important differences between subfields and methodological approaches.
+
+            This data was collected with an online Qualtrics survey from May 17 to June 10, 2022
+            from a random sample of researchers publishing in geographic academic journals as the corresponding author.
+
+            The survey inquires researchers about their:
+
+            1) understanding and awareness of replicability;
+            2) awareness and implementation of reproducible research practices;
+            3) opinions and perceptions about the role of replicability in geography and their subfield; and
+            4) experience attempting reproductions of prior studies.
+
+            Within each of these themes, responses can be viewed in aggregate (**Everyone**).
+
+            Alternatively, subsets of geographers can be selected
+            according to one of four *subfields* they are most closely associated with:
+
[…]

### 2023-08-15 docs/presentation/data/constants.R
viz: Q8, Q10

@@ -26,6 +26,46 @@ q7_text <- c(
   Q7_value_5 = "Claim will hold in other locations"
 )
 
+# Q8 questions text ####
+q8_text <- c(
+  Q8_study_factors_1 = "Multiple hypotheses were tested",
+  Q8_study_factors_2 = "Quantitative methods were used",
+  Q8_study_factors_3 = "Qualitative methods were used",
+  Q8_study_factors_4 = "Mixed methods were used",
+  Q8_study_factors_5 = "Poor documentation of study methods",
+  Q8_study_factors_6 = "Restricted access data were used",
+  Q8_study_factors_7 = "Data were gathered from multiple study sites",
+  Q8_study_factors_8 = "A large research team conducted the study",
+  Q8_study_factors_9 = "Relied on expertise unique to the researcher",
+  Q8_study_factors_10 = "Relied on the unique position of the researcher"
+)
+
+# Q10 questions text ####
+q10_text <- c(
+  Q10_study_factors_1 = "Is spatially dependent upon itself",
+  Q10_study_factors_2 = "Is strongly related with local conditions",
+  Q10_study_factors_3 = "Exhibits variation across locations",
+  Q10_study_factors_4 = "Cannot be directly measured",
+  Q10_study_factors_5 = "Cannot be directly manipulated",
+  Q10_study_factors_6 = "Has multiple competing theoretical explanations"
+)
+
+# Q15 questions text ####
+q15_text <- c(
+  Q15_decision_factors_1 = "Pressure to publish original research",
+  Q15_decision_factors_2 = "Low value of replication studies",
+  Q15_decision_factors_3 = "Low chances of replicating a result",
+  Q15_decision_factors_4 = "Lack of experience conducting replications",
+  Q15_decision_factors_5 = "Difficulty publishing peer-reviewed replications",
+  Q15_decision_factors_6 = "Difficulty accessing/creating relevant data",
+  Q15_decision_factors_7 = "Insufficient information about original methods",
+  Q15_decision_factors_8 = "Difficulty recreating similar procedures",
+  Q15_decision_factors_9 = "Lack of funding for replication studies",
+  Q15_decision_factors_10 = "Fabrication of data or results by original authors",
+  Q15_decision_factors_11 = "Ethical concerns",
+  Q15_decision_factors_12 = "Known spatial variation in phenomena being studied"
+)
+
 # Q17 questions text ####
 q17_text <- c(
[…]

### 2023-08-15 docs/presentation/global.R

@@ -12,6 +12,10 @@ thematic::thematic_shiny(font = "auto")
 # colors for likert
 pal <- c("#DF4949", "#E27A3F", "#BEBEBE", "#45B29D", "#334D5C")
 
+# continuous colors
+pal4 <- c("#EF5645", "#D9D9D9", "#F2F2F2", "#7F7F7F")
+pal7 <- c("#CD2311", "#EF5645", "#EE947D", "#D9D9D9", "#F2F2F2", "#7F7F7F", "#7F7F7F")
+
 # plot height as CSS
 plot_height <- "60vh"
 plot_full_height <- "80vh"

### 2023-08-15 docs/presentation/server.R

@@ -17,6 +17,7 @@ function(input, output, session) {
     bindCache(input$group) %>%
     bindEvent(input$group)
 
+
   # Q5 plots ####
   output$q5 <- renderPlotly({
     fig1 <- d() %>%
@@ -155,121 +156,66 @@ function(input, output, session) {
 
   # Q17 practices ####
   output$q17 <- renderPlotly({
-    plt <- d() %>%
-      pivot_longer(starts_with("Q17_"), values_to = "Response") %>%
-      group_by(name) %>%
-      mutate(
-        Response = fct_na_value_to_level(fct_rev(Response), "No response")
-      ) %>%
-      dplyr::count(Response) %>%
-      mutate(perc = n / sum(n)) %>%
-      ggplot(aes(
-        x = fct_rev(name),
-        y = n,
-        fill = Response,
-        text = paste0(
-          "<b>", Response, "</b><br>",
-          n, " people<br>",
-          round(perc * 100, 2), " %"
-        )
-      )) +
-      geom_col(
-        position = position_fill(reverse = TRUE),
-        width = 0.8
-      ) +
-      coord_flip() +
-      scale_fill_manual(
-        values = c("#EF5645", "#D9D9D9", "#F2F2F2", "#7F7F7F")
-      ) +
-      scale_x_discrete(
-        expand = c(0, 0),
-        labels = str_wrap(rev(q17_text), width = 40)
-      ) +
-      scale_y_continuous(labels = scales::percent) +
-      theme(
-        axis.title.x = element_blank(),
-        axis.title.y = element_blank(),
-        axis.line.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        panel.border = element_blank(),
-        panel.background = element_blank(),
-        text = element_text(family = "Fira Sans"),
-        legend.position = "bottom",
-        legend.title = element_blank()
-      )
-    # plotly
-    ggplotly(plt, tooltip = "text") %>%
-      plt_layout(
-        legend = list(font = fira)
-      ) %>%
-      plt_config(
-        filename = paste0(
+    d() %>%
+      plt_bar(
+        "Q17_", q17_text, pal4,
+        paste0(
           "repli_practices_",
           input$group %>%
             tolower() %>%
             gsub("[^a-z0-9]", "_", .)
         )
       )
-  })
+  }) %>%
+    bindCache(input$group)
+
 
   # Q15 barriers ####
[…]

### 2023-08-15 docs/presentation/ui.R

@@ -179,11 +179,46 @@ tagList(
       ),
     ),
 
-    # Practices ####
+    # Factors ####
     tabPanel(
-      "Practices",
+      "Factors",
       icon = icon("lightbulb"),
-      p("practices"),
+      tabsetPanel(
+        id = "factors_panel",
+        tabPanel(
+          "The study",
+          fluidRow(
+            column(
+              12,
+              # col-sm-12
+              class = "col-xxl-8",
+              h4(
+                "How do each of the following characteristics of a",
+                strong("study"), "published in your sub-field",
+                "affect the chances of replicating that study?"
+                ),
+              plotlyOutput("q8", height = plot_full_height) %>% spin(),
+            ),
+          ),
+        ),
+        tabPanel(
+          "The phenomenon",
+          fluidRow(
+            column(
+              12,
+              # col-sm-12
+              class = "col-xxl-8",
+              h4(
+                "How do each of the following characteristics of the",
+                 strong("phenomenon"), "being examined",
+                 "affect the chances of replicating a study",
+                "in your sub-field in a different location from the prior study?"
+                 ),
+              plotlyOutput("q10", height = plot_height) %>% spin(),
+            ),
+          ),
+        ),
+      ),
     ),
 
     # Opinions ####

### 2023-08-15 docs/presentation/server.R
viz: fix Q17

@@ -157,6 +157,9 @@ function(input, output, session) {
   # Q17 practices ####
   output$q17 <- renderPlotly({
     d() %>%
+      mutate(
+        across(starts_with("Q17"), fct_rev)
+      ) %>%
       plt_bar(
         "Q17_", q17_text, pal4,
         paste0(

### 2023-08-15 docs/presentation/preprocess.Rmd

---
title: "Preprocessing"
output: 
  html_document:
    theme: flatly
    df_print: paged
date: "2023-07-12"
---

Making sense of the survey data.

```{r import, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  fig.retina = 4,
  fig.showtext = TRUE,
  message = FALSE,
  warning = FALSE
)

# all your themes are belong to us
# library(ggthemes)
library(tidyverse)
library(magrittr)
library(showtext)
font_add_google("Fira Sans", "Fira Sans")
```

```{r data}
analysis <- readRDS("../../data/derived/public/analysis_hegs_rpl.rds")
source("data/constants.R")
```

## Groups

Dropping NAs for brevity

```{r drop na}
analysis %<>%
  drop_na(Q3_recoded, Q4_quantqual) %>%
  filter(Q3_recoded != "Other")
```

Question 3: primary subfield of research

```{r q3 groups}
analysis %>%
  group_by(Q3_recoded) %>%
  summarise(n = n())
```

Question 4: type of research

```{r q4 groups}
analysis %>%
  group_by(Q4_quantqual) %>%
  summarise(n = n())
```

## Word cloud

Q6
Q10

```{r DRY wordcloud}
column_to_cloud <- function(
    col, nrows = 30,
    data = analysis,
    my_palette = c(
      "#cdb4db",
      "#6d597a",
      "#b56576",
      "#e56b6f",
      "#eaac8b"
    )) {
  require(tidytext)
  word_counts <- data %>%
    drop_na(all_of(col)) %>%
    unnest_tokens("word", col) %>%
    # https://bookdown.org/psonkin18/berkshire/tokenize.html#text-normalization---stemming-and-lemmatization
    # doesn't work - why is `reproduct` different from `reproduc`?
    # mutate(word = SnowballC::wordStem(word, language = "english")) %>%
    anti_join(stop_words, by = "word") %>%
    count(word) %>%
    arrange(desc(n)) %>%
    slice(1:nrows)

  require(wordcloud2)
  wordcloud2(
    word_counts,
    color = rep_len(
      my_palette,
      nrow(word_counts)
    )
  ) %>%
    return()
}
```

```{r word clouds}
clouds <- map(cloud_cols, column_to_cloud) %>%
  set_names(cloud_cols)
# saveRDS(clouds, file = "data/clouds.rds")
```

```{r q6 cloud}
clouds_q6_q3 <- map(
  subfields, ~ analysis %>%
    filter(Q3_recoded == .x) %>%
    column_to_cloud("Q6_definition", data = .)
) %>%
  set_names(subfields)

clouds_q6_q4 <- map(
  types, ~ analysis %>%
    filter(Q4_quantqual == .x) %>%
    column_to_cloud("Q6_definition", data = .)
) %>%
  set_names(types)

clouds_q6 <- append(clouds_q6_q3, clouds_q6_q4)
clouds_q6$Everyone <- clouds$Q6_definition
saveRDS(clouds_q6, file = "data/clouds_q6.rds")
```

```{r q19 cloud}
clouds_q19_q3 <- map(
  subfields, ~ analysis %>%
    filter(Q3_recoded == .x) %>%
    column_to_cloud("Q19_reason_for_rep", data = .)
) %>%
  set_names(subfields)

clouds_q19_q4 <- map(
  types, ~ analysis %>%
    filter(Q4_quantqual == .x) %>%
    column_to_cloud("Q19_reason_for_rep", data = .)
) %>%
  set_names(types)

clouds_q19 <- append(clouds_q19_q3, clouds_q19_q4)
clouds_q19$Everyone <- clouds$Q19_reason_for_rep
saveRDS(clouds_q19, file = "data/clouds_q19.rds")
```

## Bar charts
Order Q5
```{r}
analysis %<>%
  mutate(across(all_of(four_level_cols), ~ factor(., levels = four_levels)))
```

TODO: Rename Q6 labels
```{r eval=FALSE, include=FALSE}
analysis %<>%
  mutate(label = case_match(
    label,
    "Omit" ~ NA,
    "Standard" ~ "Assess Prior Work",
    "Experiment" ~ "Repeatable Experiments",
    "Data Collection" ~ "Data Collection",
    "Transparency/Extension" ~ "Transparency/Extension"
  ))
```

## Q7 Likert
```{r}
q7_to_likert <- function(data = analysis) {
  data %>%
    # make data for likert
    pivot_longer(cols = starts_with("Q7_value_")) %>%
    group_by(name, value) %>%
    summarise(n = n()) %>%
    mutate(value = factor(value, levels = agree_levels)) %>%
    replace_na(list(value = "Don't know")) %>%
    group_by(name) %>%
    mutate(perc = n / sum(n)) %>%
    mutate(
      yeah = ifelse(any(value == "Agree"), perc[value == "Agree"], 0),
      idk = ifelse(any(value == "Don't know"), perc[value == "Don't know"] / 2, 0),
      nah = ifelse(any(value == "Disagree"), perc[value == "Disagree"], 0),
      start = case_match(
        value,
        "Strongly agree" ~ yeah + idk,
        "Agree" ~ idk,
        "Don't know" ~ -idk,
        "Disagree" ~ -idk - perc,
        "Strongly disagree" ~ -idk - nah - perc,
      )
    ) %>%
    ungroup() %>%
    dplyr::select(-c(yeah, nah, idk))
}
```

```{r Q8}
q7_q3 <- map(
  subfields, ~ analysis %>%
    filter(Q3_recoded == .x) %>%
    q7_to_likert()
) %>%
  set_names(subfields)

q7_q4 <- map(
  types, ~ analysis %>%
    filter(Q4_quantqual == .x) %>%
    q7_to_likert()
) %>%
  set_names(types)

q7 <- append(q7_q3, q7_q4)
q7$Everyone <- q7_to_likert()
saveRDS(q7, file = "data/q7.rds")
```

## Save
```{r}
analysis %>%
  saveRDS("data/analysis.rds")
```

### 2023-08-15 procedure/code/02-clean.R
joining coding results

@@ -148,4 +148,6 @@ analysis_hegs_rpl %>%
   select(c("ResponseId","Q6_definition")) %>% 
   write.csv(here("data","derived","public","q6_coding.csv"))
 
+## load completed coding and join new fields to analysis_hegs_rpl
+
 saveRDS(int_hegs_rpl, here("data","derived","public","analysis_hegs_rpl.rds"))

### 2023-08-15 procedure/code/02-clean.R
analysis: join coded Q6

@@ -76,7 +76,7 @@ int_hegs_rpl <- int_hegs_rpl %>%
   mutate(Q25_recoded = as.factor(ifelse(toupper(Q25_title_9_TEXT) %in% res_scientist, 5, 
                                  ifelse(toupper(Q25_title_9_TEXT) == "Lecturer/teacher at a university of applied sciences.", 2, Q25_title))))
 
-levels(int_hegs_rpr$Q25_recoded) <- c("Full professor/lecturer",
+levels(int_hegs_rpl$Q25_recoded) <- c("Full professor/lecturer",
                                       "Associate professor/lecturer",
                                       "Assistant professor/lecturer",
                                       "Laboratory director/head",
@@ -149,5 +149,14 @@ analysis_hegs_rpl %>%
   write.csv(here("data","derived","public","q6_coding.csv"))
 
 ## load completed coding and join new fields to analysis_hegs_rpl
+q6_coding <- read.csv(here("data", "derived", "public", "q6_coding_final.csv"))
 
-saveRDS(int_hegs_rpl, here("data","derived","public","analysis_hegs_rpl.rds"))
+q6_coding <- q6_coding %>%
+  select(!c(RowID, Q6_definition)) %>%
+  rename_with(~ paste0("coded_Q6_", .), .cols = !ResponseId)
+
+int_hegs_rpl <- int_hegs_rpl %>%
+  full_join(q6_coding, by = "ResponseId")
+
+
+saveRDS(int_hegs_rpl, here("data", "derived", "public", "analysis_hegs_rpl.rds"))

### 2023-08-15 docs/presentation/data/constants.R
viz: q6 coded plots

@@ -14,6 +14,35 @@ geo_groups <- list(
 four_levels <- c("Not at all", "Very little", "Somewhat", "To a great extent")
 four_level_cols <- c("Q5_familiarity")
 
+# Q6 motivations ####
+q6_motive <- c(
+  "Open & Repeatable" = "coded_Q6_open.repeatable",
+  "External Validation" = "coded_Q6_validate.external",
+  "Geographic Variation" = "coded_Q6_unique.space.time"
+)
+
+# Q6 terms ###
+q6_terms_pos <- c(
+  "New data" = "coded_Q6_data.new",
+  "Same methods" = "coded_Q6_methods.same",
+  "New context" = "coded_Q6_context.new",
+  "Similar result" = "coded_Q6_result.similar"
+)
+
+q6_terms_neg <- c(
+  "Same data" = "coded_Q6_data.same",
+  "Varied methods" = "coded_Q6_methods.varied",
+  "Same context" = "coded_Q6_context.same",
+  "Same result" = "coded_Q6_result.same"
+)
+
+q6_plot_order <- c(
+  "New data", "Same data",
+  "Same methods", "Varied methods",
+  "New context", "Same context",
+  "Similar result", "Same result"
+)
+
 # Q7 Levels of agreement ####
 agree_levels <- c("Strongly disagree", "Disagree", "Don't know", "Agree", "Strongly agree")
 

### 2023-08-15 docs/presentation/server.R

@@ -30,13 +30,57 @@ function(input, output, session) {
         hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
       )
 
-    fig2 <- plot_ly(
-      type = "bar"
-    )
+    neg <- d() %>%
+      select(all_of(q6_terms_neg)) %>%
+      pivot_longer(cols = everything()) %>%
+      filter(value != 0) %>%
+      group_by(name) %>%
+      summarise(n = n()) %>%
+      mutate(name = str_wrap(name, width = width))
 
-    fig3 <- plot_ly(
-      type = "bar"
-    )
+    fig2 <- d() %>%
+      select(all_of(q6_terms_pos)) %>%
+      pivot_longer(cols = everything()) %>%
+      filter(value != 0) %>%
+      group_by(name) %>%
+      summarise(n = n()) %>%
+      mutate(name = str_wrap(name, width = width)) %>%
+      plot_ly(
+        x = ~name,
+        y = ~n,
+        type = "bar",
+        name = "Replicability",
+        hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
+      ) %>%
+      add_trace(
+        x = ~ neg$name,
+        y = ~ neg$n,
+        base = ~ -neg$n,
+        meta = ~ neg$n,
+        type = "bar",
+        name = "Reproducibility",
+        hovertemplate = "<b>%{x}</b>\n%{meta} people<extra></extra>"
+      ) %>%
+      layout(xaxis = list(
+        categoryorder = "array",
+        categoryarray = q6_plot_order
+      ))
+
+
+    fig3 <- d() %>%
+      select(all_of(q6_motive)) %>%
+      pivot_longer(cols = everything()) %>%
+      filter(value != 0) %>%
+      group_by(name) %>%
+      summarise(n = n()) %>%
+      mutate(name = str_wrap(name, width = width)) %>%
+      plot_ly(
+        x = ~name,
+        y = ~n,
+        type = "bar",
+        # name = "Familiar",
+        hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
+      )
 
     plotly::subplot(fig1, fig2, fig3, nrows = 1, shareY = TRUE) %>%
       plt_layout(showlegend = FALSE) %>%
@@ -124,7 +168,8 @@ function(input, output, session) {
         type = "scatter",
         mode = "lines",
         fill = "tozeroy",
-        name = "Could be"
+        name = "Could be",
[…]

### 2023-08-15 docs/presentation/global.R
viz: refactoring

@@ -22,6 +22,7 @@ plot_full_height <- "80vh"
 
 # text width for axis labels
 width <- 20
+width_long <- 32
 
 # spinner
 spin <- function(plt) {

### 2023-08-15 docs/presentation/server.R

@@ -117,7 +117,7 @@ function(input, output, session) {
       scale_color_manual("Response", values = pal, guide = "legend") +
       labs(title = "", y = "Percent", x = "") +
       scale_x_discrete(
-        labels = str_wrap(rev(q7_text), width = 40)
+        labels = str_wrap(rev(q7_text), width = width_long)
       ) +
       scale_y_continuous(labels = scales::percent) +
       theme_minimal() +
@@ -207,7 +207,7 @@ function(input, output, session) {
         across(starts_with("Q17"), fct_rev)
       ) %>%
       plt_bar(
-        "Q17_", q17_text, pal4,
+        "Q17_", q17_text, pal4, width_long,
         paste0(
           "repli_practices_",
           input$group %>%
@@ -223,7 +223,7 @@ function(input, output, session) {
   output$q15 <- renderPlotly({
     d() %>%
       plt_bar(
-        "Q15", q15_text, pal7,
+        "Q15", q15_text, pal7, width_long,
         paste0(
           "repli_barriers_",
           input$group %>%
@@ -239,7 +239,7 @@ function(input, output, session) {
   output$q8 <- renderPlotly({
     d() %>%
       plt_bar(
-        "Q8", q8_text, pal7,
+        "Q8", q8_text, pal7, width_long,
         paste0(
           "repli_study_factors_",
           input$group %>%
@@ -254,7 +254,7 @@ function(input, output, session) {
   output$q10 <- renderPlotly({
     d() %>%
       plt_bar(
-        "Q10", q10_text, pal7,
+        "Q10", q10_text, pal7, width_long,
         paste0(
           "repli_phenomenon_",
           input$group %>%

### 2023-08-15 docs/presentation/ui.R
viz: move cols

@@ -196,7 +196,7 @@ tagList(
                 "How do each of the following characteristics of a",
                 strong("study"), "published in your sub-field",
                 "affect the chances of replicating that study?"
-                ),
+              ),
               plotlyOutput("q8", height = plot_full_height) %>% spin(),
             ),
           ),
@@ -210,10 +210,10 @@ tagList(
               class = "col-xxl-8",
               h4(
                 "How do each of the following characteristics of the",
-                 strong("phenomenon"), "being examined",
-                 "affect the chances of replicating a study",
+                strong("phenomenon"), "being examined",
+                "affect the chances of replicating a study",
                 "in your sub-field in a different location from the prior study?"
-                 ),
+              ),
               plotlyOutput("q10", height = plot_height) %>% spin(),
             ),
           ),
@@ -227,6 +227,21 @@ tagList(
       icon = icon("comments"),
       tabsetPanel(
         id = "op_panel",
+        tabPanel(
+          "Published results",
+          fluidRow(
+            column(
+              12,
+              # col-sm-12
+              class = "col-xxl-8",
+              h4(
+                "Please estimate the percentage of recent studies",
+                "published in your sub-field that ... replicated.",
+              ),
+              plotlyOutput("q12", height = plot_height) %>% spin(),
+            ),
+          ),
+        ),
         tabPanel(
           "Views",
           fluidRow(
@@ -243,21 +258,6 @@ tagList(
                 "assess whether a prior study's ...",
               ),
               plotlyOutput("q7", height = plot_height) %>% spin(),
-            ),
-          ),
-        ),
-        tabPanel(
-          "Published results",
-          fluidRow(
-            column(
-              12,
-              # col-sm-12
-              class = "col-xxl-8",
-              h4(
-                "Please estimate the percentage of recent studies",
-                "published in your sub-field that ... replicated.",
-              ),
-              plotlyOutput("q12", height = plot_height) %>% spin(),
             ),
           ),
         ),

### 2023-08-15 docs/presentation/ui.R
viz: extract about page

@@ -38,81 +38,7 @@ tagList(
           class = "col-lg-10 col-xl-8 col-xxl-6",
           style = "margin-left: 3vw;",
           markdown(
-            "
-            # TODO: edit this
-            ### Welcome
-            This is an interactive data visualization for
-            *Reproducible Research Practices and Barriers to Reproducible Research in Geography:Insights from a Survey*
-            by Peter Kedron, Joseph Holler, and Sarah Bardin.
-
-            The purpose of the survey was to systematically develop a baseline of information
-            about the state of replicability in geography
-            and to identify any important differences between subfields and methodological approaches.
-
-            This data was collected with an online Qualtrics survey from May 17 to June 10, 2022
-            from a random sample of researchers publishing in geographic academic journals as the corresponding author.
-
-            The survey inquires researchers about their:
-
-            1) understanding and awareness of replicability;
-            2) awareness and implementation of reproducible research practices;
-            3) opinions and perceptions about the role of replicability in geography and their subfield; and
-            4) experience attempting reproductions of prior studies.
-
-            Within each of these themes, responses can be viewed in aggregate (**Everyone**).
-
-            Alternatively, subsets of geographers can be selected
-            according to one of four *subfields* they are most closely associated with:
-
-            - **Human** geography;
-            - Spatial analysis and **methods**;
-            - **Nature/Society**; or
-            - **Physical** geography.
-
-            Or, one of three *methods* they most frequently use:
-            - **Quantitative**;
-            - **Qualitative**; or
-            - **Mixed Methods**.
-
-            ### Links
-            Please read our preprint for this study for more details, including discussions of results:
-
-            Kedron, P., Holler, J., & Bardin, S. (2023, June 3).
-            *Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey*.
-            <https://doi.org/10.31219/osf.io/nyrq9>.
-
-            This data visualization is primarily the work of Yifei Luo
-            with supervision of Joseph Holler, and can be cited as:
-
-            Holler, J., Luo, Y., Kedron, P., & Bardin, S. (2023, August 9). *replicability Survey Data Visualization*.
-            <https://doi.org/10.17605/osf.io/b47xu>.
-
-            A sample BibTeX entry is as follows:
-
-            ```
-            @article{holler_2023_replicability,
[…]

### 2023-08-15 docs/presentation/global.R
viz: read from about-page.md

@@ -9,11 +9,14 @@ library(shinycssloaders)
 # theme to match HTML
 thematic::thematic_shiny(font = "auto")
 
+# About page
+about <- readr::read_file("about-page.md")
+
 # colors for likert
 pal <- c("#DF4949", "#E27A3F", "#BEBEBE", "#45B29D", "#334D5C")
 
 # continuous colors
-pal4 <- c("#EF5645", "#D9D9D9", "#F2F2F2", "#7F7F7F")
+pal4 <- c("#EF5645", "#F2F2F2", "#7F7F7F", "#7F7F7F")
 pal7 <- c("#CD2311", "#EF5645", "#EE947D", "#D9D9D9", "#F2F2F2", "#7F7F7F", "#7F7F7F")
 
 # plot height as CSS

### 2023-08-15 docs/presentation/ui.R

@@ -37,9 +37,7 @@ tagList(
           # col-sm-12
           class = "col-lg-10 col-xl-8 col-xxl-6",
           style = "margin-left: 3vw;",
-          markdown(
-            ""
-          ),
+          markdown(about),
         ),
       ),
     ),

### 2023-08-15 docs/presentation/server.R
viz: aesthetics

@@ -50,16 +50,17 @@ function(input, output, session) {
         y = ~n,
         type = "bar",
         name = "Replicability",
+        # https://plotly.com/r/bar-charts/#:~:text=I(%22black%22)
+        color = I("#2ca02c"),
         hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
       ) %>%
       add_trace(
         x = ~ neg$name,
         y = ~ neg$n,
-        base = ~ -neg$n,
-        meta = ~ neg$n,
         type = "bar",
         name = "Reproducibility",
-        hovertemplate = "<b>%{x}</b>\n%{meta} people<extra></extra>"
+        color = I("#ff7f0e"),
+        hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
       ) %>%
       layout(xaxis = list(
         categoryorder = "array",

### 2023-08-15 docs/presentation/ui.R

@@ -49,7 +49,7 @@ tagList(
       tabsetPanel(
         id = "awareness-panel",
         tabPanel(
-          "Question 5",
+          "Concept",
           fluidRow(
             column(
               4,
@@ -76,7 +76,7 @@ tagList(
           plotlyOutput("q5", height = plot_height) %>% spin(),
         ),
         tabPanel(
-          "Question 6",
+          "Definition",
           h4(
             "What is your ", strong("understanding"),
             "of the term “replicability”",
@@ -88,7 +88,7 @@ tagList(
           ),
         ),
         tabPanel(
-          "Question 19",
+          "Motivation",
           h4(
             "Thinking about the replication(s)",
             "you attempted in the last 2 years,",

### 2023-08-17 docs/manuscript/manuscript.tex
Updates from Overleaf

@@
 \author{
-\name{Peter Kedron\textsuperscript{a,b}\thanks{CONTACT Peter Kedron. Email: Peter.Kedron@asu.edu}, Joseph Holler\textsuperscript{c}, and Sarah Bardin\textsuperscript{a,b}}
-\affil{\textsuperscript{a}School of Geographical Sciences and Urban Planning, Arizona State University, Tempe, Arizona, USA; \textsuperscript{b}Spatial Analysis Research Center (SPARC), Arizona State University, Tempe, Arizona, USA; \textsuperscript{c}Department of Geography, Middlebury College, Middlebury, Vermont, USA}
+\name{Peter Kedron\textsuperscript{a,b}\thanks{CONTACT Peter Kedron. Email: peterkedron@ucsb.edu}, Joseph Holler\textsuperscript{d}, and Sarah Bardin\textsuperscript{a,c}}
+\affil{\textsuperscript{a} Department of Geography, University of California Santa Barbara, Santa Barbara, California, USA; \textsuperscript{b}School of Geographical Sciences and Urban Planning, Arizona State University, Tempe, Arizona, USA; \textsuperscript{c}Spatial Analysis Research Center (SPARC), Arizona State University, Tempe, Arizona, USA; \textsuperscript{d}Department of Geography, Middlebury College, Middlebury, Vermont, USA}
 }
@@
 For example, in a survey of 807 ecologists and evolutionary biologists, 64 percent admitted to failing to report non-significant results and 51 percent admitted to presenting unexpected findings as if they had been hypothesized from the start of the research \citep{fraser2018questionable}.
+
+To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of replicability, beliefs about what factors affects the chances or replicating a study, motivations to attempt replication studies, and experiences conducting replications.
+To support generalization, we designed a sampling frame to capture researchers from across disciplinary subfields and methodological approaches, and draw survey participants from that frame using a probability sampling scheme.
+In the remainder of this paper, we first present the design of our survey, sampling strategy, and analytical approach. 
+We then present the results of our survey before discussing the implications and limitations of our work.
 

### 2023-08-17 docs/presentation/preprocess.Rmd
viz: likert for Q8, Q10

@@
 source("data/constants.R")
+
+gen <- list()
 ```
@@
 
-clouds_q6 <- append(clouds_q6_q3, clouds_q6_q4)
-clouds_q6$Everyone <- clouds$Q6_definition
-saveRDS(clouds_q6, file = "data/clouds_q6.rds")
+gen$q6 <- append(clouds_q6_q3, clouds_q6_q4)
+gen$q6$Everyone <- clouds$Q6_definition
 ```
@@
 
-clouds_q19 <- append(clouds_q19_q3, clouds_q19_q4)
-clouds_q19$Everyone <- clouds$Q19_reason_for_rep
-saveRDS(clouds_q19, file = "data/clouds_q19.rds")
+gen$q19 <- append(clouds_q19_q3, clouds_q19_q4)
+gen$q19$Everyone <- clouds$Q19_reason_for_rep
 ```
@@
   mutate(across(all_of(four_level_cols), ~ factor(., levels = four_levels)))
-```
-
-TODO: Rename Q6 labels
-```{r eval=FALSE, include=FALSE}
-analysis %<>%
-  mutate(label = case_match(
-    label,
-    "Omit" ~ NA,
-    "Standard" ~ "Assess Prior Work",
-    "Experiment" ~ "Repeatable Experiments",
-    "Data Collection" ~ "Data Collection",
-    "Transparency/Extension" ~ "Transparency/Extension"
-  ))
 ```
@@
     mutate(value = factor(value, levels = agree_levels)) %>%
-    replace_na(list(value = "Don't know")) %>%
     group_by(name) %>%
@@
     ungroup() %>%
+    drop_na(value) %>%
     dplyr::select(-c(yeah, nah, idk))
@@
 
-```{r Q8}
+```{r Q7}
 q7_q3 <- map(
@@
 
-q7 <- append(q7_q3, q7_q4)
-q7$Everyone <- q7_to_likert()
-saveRDS(q7, file = "data/q7.rds")
+gen$q7 <- append(q7_q3, q7_q4)
+gen$q7$Everyone <- q7_to_likert()
+```
+
+## Q8, Q10 to likert
+
+```{r}
+to_likert <- function(data = analysis, col_prefix) {
+  data %>%
+    # make data for likert
+    pivot_longer(cols = starts_with(col_prefix)) %>%
+    group_by(name, value) %>%
+    summarise(n = n()) %>%
+    mutate(value = factor(value, levels = likely_levels)) %>%
+    group_by(name) %>%
+    mutate(perc = n / sum(n)) %>%
+    mutate(
+      yeah = ifelse(any(
+        value == "Somewhat likely to increase"),
+        perc[value == "Somewhat likely to increase"], 0),
+      idk = ifelse(
+        any(value == "Not likely to affect"),
+                   perc[value == "Not likely to affect"] / 2, 0),
+      nah = ifelse(any(
+        value == "Somewhat likely to decrease"), 
+        perc[value == "Somewhat likely to decrease"], 0),
+      start = case_match(
+        value,
+        "Very likely to increase" ~ yeah + idk,
+        "Somewhat likely to increase" ~ idk,
+        "Not likely to affect" ~ -idk,
+        "Somewhat likely to decrease" ~ -idk - perc,
+        "Very likely to decrease" ~ -idk - nah - perc,
+      )
+    ) %>%
+    ungroup() %>%
+    drop_na(value) %>%
+    dplyr::select(-c(yeah, nah, idk))
+}
+```
+
+```{r Q8}
+q8_q3 <- map(
+  subfields, ~ analysis %>%
+    filter(Q3_recoded == .x) %>%
+    to_likert("Q8_study")
+) %>%
+  set_names(subfields)
+
+q8_q4 <- map(
+  types, ~ analysis %>%
+    filter(Q4_quantqual == .x) %>%
+    to_likert("Q8_study")
+) %>%
+  set_names(types)
+
+gen$q8 <- append(q8_q3, q8_q4)
+gen$q8$Everyone <- to_likert(col_prefix = "Q8_study")
+```
+
+```{r Q10}
+q10_q3 <- map(
+  subfields, ~ analysis %>%
+    filter(Q3_recoded == .x) %>%
+    to_likert("Q10_phen")
+) %>%
+  set_names(subfields)
+
+q10_q4 <- map(
+  types, ~ analysis %>%
+    filter(Q4_quantqual == .x) %>%
+    to_likert("Q10_phen")
+) %>%
+  set_names(types)
+
+gen$q10 <- append(q10_q3, q10_q4)
+gen$q10$Everyone <- to_likert(col_prefix = "Q10_phen")
 ```
@@
   saveRDS("data/analysis.rds")
+
+gen %>%
+  saveRDS("data/generated.rds")
 ```

### 2023-08-17 docs/presentation/data/constants.R

@@ -55,6 +55,13 @@ q7_text <- c(
   Q7_value_5 = "Claim will hold in other locations"
 )
 
+# Q8 & Q10 levels ####
+likely_levels <- c(
+  "Very likely to decrease", "Somewhat likely to decrease",
+  "Not likely to affect",
+  "Somewhat likely to increase", "Very likely to increase"
+)
+
 # Q8 questions text ####
 q8_text <- c(
   Q8_study_factors_1 = "Multiple hypotheses were tested",
@@ -160,7 +167,7 @@ plt_config <- function(plt, filename, ...) {
 }
 
 
-# Function for bar plots
+# Function for bar plots ####
 plt_bar <- function(data, prefix, names, pal, label_width, filename) {
   plt <- data %>%
     pivot_longer(starts_with(prefix), values_to = "Response") %>%
@@ -212,4 +219,41 @@ plt_bar <- function(data, prefix, names, pal, label_width, filename) {
     plt_config(
       filename = filename
     )
+}
+
+# Function for likert plots ####
+plt_likert <- function(data, names, pal, label_width, filename) {
+  plt <- data %>%
+    # ggplot
+    ggplot() +
+    geom_segment(aes(
+      x = fct_rev(name),
+      y = start,
+      xend = name, yend = start + perc,
+      colour = value,
+      text = paste0(
+        "<b>", value, "</b><br>",
+        n, " people<br>",
+        round(perc * 100, 2), " %"
+      )
+    ), linewidth = 12) +
+    geom_hline(yintercept = 0, color = c("#646464")) +
+    coord_flip() +
+    scale_color_manual("Response", values = pal, guide = "legend") +
+    labs(title = "", y = "Percent", x = "") +
+    scale_x_discrete(
+      labels = str_wrap(rev(names), width = label_width)
+    ) +
+    scale_y_continuous(labels = scales::percent) +
+    theme_minimal() +
+    theme(
+      panel.grid.major.y = element_blank(),
+      panel.grid.minor.y = element_blank()
+    )
+  # plotly
+  ggplotly(plt, tooltip = "text") %>%
+    plt_layout(
+      legend = list(font = fira)
+    ) %>%
+    plt_config(filename = filename)
 }

### 2023-08-17 docs/presentation/global.R

@@ -42,7 +42,4 @@ source("data/constants.R")
 
 # load data ####
 analysis <- readRDS("data/analysis.rds")
-
-clouds_q6 <- readRDS("data/clouds_q6.rds")
-clouds_q19 <- readRDS("data/clouds_q19.rds")
-q7 <- readRDS("data/q7.rds")
+gen <- readRDS("data/generated.rds")

### 2023-08-17 docs/presentation/server.R

@@ -99,40 +99,10 @@ function(input, output, session) {
 
   # Q7 likert ####
   output$q7 <- renderPlotly({
-    plt <- q7[[input$group]] %>%
-      # ggplot
-      ggplot() +
-      geom_segment(aes(
-        x = fct_rev(name),
-        y = start,
-        xend = name, yend = start + perc,
-        colour = value,
-        text = paste0(
-          "<b>", value, "</b><br>",
-          n, " people<br>",
-          round(perc * 100, 2), " %"
-        )
-      ), linewidth = 12) +
-      geom_hline(yintercept = 0, color = c("#646464")) +
-      coord_flip() +
-      scale_color_manual("Response", values = pal, guide = "legend") +
-      labs(title = "", y = "Percent", x = "") +
-      scale_x_discrete(
-        labels = str_wrap(rev(q7_text), width = width_long)
-      ) +
-      scale_y_continuous(labels = scales::percent) +
-      theme_minimal() +
-      theme(
-        panel.grid.major.y = element_blank(),
-        panel.grid.minor.y = element_blank()
-      )
-    # plotly
-    ggplotly(plt, tooltip = "text") %>%
-      plt_layout(
-        legend = list(font = fira)
-      ) %>%
-      plt_config(
-        filename = paste0(
+    gen$q7[[input$group]] %>%
+      plt_likert(
+        q7_text, pal, width_long,
+        paste0(
           "repli_views_",
           input$group %>%
             tolower() %>%
@@ -238,9 +208,9 @@ function(input, output, session) {
 
   # Q8 characteristics of study ####
   output$q8 <- renderPlotly({
-    d() %>%
-      plt_bar(
-        "Q8", q8_text, pal7, width_long,
+    gen$q8[[input$group]] %>%
+      plt_likert(
+        q8_text, pal, width_long,
         paste0(
           "repli_study_factors_",
           input$group %>%
@@ -253,9 +223,9 @@ function(input, output, session) {
 
   # Q10 phenomenon ####
   output$q10 <- renderPlotly({
-    d() %>%
-      plt_bar(
-        "Q10", q10_text, pal7, width_long,
+    gen$q10[[input$group]] %>%
+      plt_likert(
+        q10_text, pal, width_long,
         paste0(
           "repli_phenomenon_",
           input$group %>%
@@ -268,6 +238,6 @@ function(input, output, session) {
 
[…]

### 2023-08-17 docs/presentation/ui.R

@@ -115,7 +115,7 @@ tagList(
             column(
               12,
               # col-sm-12
-              class = "col-xxl-8",
+              class = "col-xxl-10",
               h4(
                 "How do each of the following characteristics of a",
                 strong("study"), "published in your sub-field",
@@ -131,7 +131,7 @@ tagList(
             column(
               12,
               # col-sm-12
-              class = "col-xxl-8",
+              class = "col-xxl-10",
               h4(
                 "How do each of the following characteristics of the",
                 strong("phenomenon"), "being examined",

### 2023-08-18 docs/manuscript/manuscript.tex

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Analytical Approach}
+
+We conducted two statistical analyses of the survey responses.
+First, we analyzed researcher perspectives on replicability by coding and calculating summary variables and statistics for three themes: how geographic researchers define replicability, factors researchers believe affect the chances of replicating a study, and factors researchers affect the decision to attempt to replicate a study.
+Second, we analyzed researchers' experiences attempting to replicate prior studies.
+
+\subsubsection*{Analyzing Researcher Perspectives on Reproducibility}
+
+\noindent For our first set of analyses, we examined the full set of survey responses.
+
+\textit{Defining Reproducibility:} 
+We coded participants' qualitative definitions of ``reproducibility'' following two procedures.
+First, we measured the similarity of each provided definition to the definition adopted by the \textcite{NASEM2019}. 
+The NASEM defines reproducible research as having four characteristics --- same data, same procedure, same results, and same conditions.
+To make this comparison, each of the authors independently coded each respondent definition for the presence/absence of each of the four characteristics included in the NASEM definition.
+Disagreements in the assignment of codes were resolved through discussion between the three authors.
+We created an aggregate measure of definition similarity for the final coded response for each participant by counting the presence of each NASEM definition characteristic, resulting in a measure with the domain [0, 4].
+
+Second, we coded each definition to one of four motivations for ensuring the reproducibility of a study: (i) to facilitate the assessment of prior work, (ii) to assess experimental research, (iii) to improve transparency and facilitate further extension of work, and (iv) to improve the transparency and consistency of data collection.
+We derived this coding from common themes in the responses and our own reading of the reproducibility literature.
+As above, each definition was independently coded by each author before code assignments across authors were compared with disagreements resolved through discussion.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection*{Researcher Definitions of Replication and its Epistemic Functions}
+Geographic researchers are thinking about replicability and link the act of replicating a study to a number of different epistemological functions (Figure A). 
+A majority of respondents reported thinking about replicability (74\%), talking with colleagues about replicability (65\%), and considering replicability when undertaking peer-review (59\%) during the past two years.
+Respondents believe that replication studies can be used to assess the construct validity of a prior study (75\%) and whether the claims of that study will hold in new locations (67\%) or new populations (63\%).
+While respondents clearly linked replication to these epistemological objectives, they were also more likely to agree than strongly agree that replications could meet these goals.
+When compared to those working in other subfields, respondents that identified specializing in human geography or the study of nature and society were less likely to agree that replications could be used to achieve these goals.
+For example, while 87 percent of respondents specializing in GIScience and methods believe replications could be used to assess whether a claim was the product of chance, just 57 percent of human and nature-society researchers agreed with this statement.
+
+\begin{center}
+\textbf{Insert Figure A About Here}
+\end{center}
+
+However, when respondents provided their own definitions of replicability many of these same concepts were not explicitly included.
+47 percent of respondents included the need to assess or improve how well a prior study as part of their definition of replicability.
+19 percent of respondents included the motivation to externally validate the claims of the original study by repeating the methods with new data in a new context.
+
+Rather than focusing on these larger concepts, most respondent definitions presented criteria that identify a replication.
+
+Analysis of coded Q6. Coding explicit mentions of the three dimensions of the NASEM replicability definition
 \begin{itemize}
-    \item Respondents report thinking about replicability (73.9\%) talking with colleagues about replicability (65.0\%) and considering replicability when undertaking peer-review (59.0\%). 
-    \item Far fewer respondents report attempting replications (31.8\%). 
+    \item New Data - 12\%
+    \item Same Method - 56\%
+    \item Results same or similar - 65\%
+    \item Only 7\% of respondents mention all three
 \end{itemize}
 
+Subfield variation
 \begin{itemize}
-    \item Coded analysis of Q6
-\end{itemize}
-
-A majority of respondents believe replications can serve epistemic functions.
-\begin{itemize}
-    \item Q7 control of chance 64.5\%
-    \item Q7 identify product of flawed design 59.7\%
-    \item Q7 construct validity 75.2\%
-    \item External validity population 62.9\%
-    \item External validity location 67.8\%
-    \item Human, Nature Society, and Qualitative researchers had lower agreement on each point.
+    \item New Data - 12\%
+    \item Same Method - 56\%
+    \item Results same or similar - 65\%
+    \item Only 7\% of respondents mention all three
 \end{itemize}
@@
 \subsection*{Replication Attempts}
+Far fewer respondents report attempting replications (31.8\%).
+
 \begin{itemize}

### 2023-09-01 docs/manuscript/manuscript.tex

--- 2023-08-17 docs/manuscript/manuscript.tex
@@
 \section*{Introduction}
-Since the 1600s, replication has been a defining characteristic of the scientific method and an essential tool of researchers working to remove errors from our understanding of phenomena. 
-\citet{nosek2020} broadly define a replication as any study that has at least one outcome that would be considered to be diagnostic evidence of a claim from prior research.
-More frequently, replication is defined along two axes that help to distinguish the type of diagnostic evidence a study will provide and the function or purpose it is intended to serve. 
-First, it is common to distinguish whether a replication study used the same data as the original study, or if new data were collected and analyzed. 
-Second, it is helpful to identify whether a replication is focused on the question of whether the specific results of the original study can be reobserved, or whether the conclusions drawn from the original study are robust to changes in procedure or context.
+Since the 1600s, replication has been a defining characteristic of the scientific method and an essential tool of researchers working to understanding and explain phenomena. 
+Broadly defined, a replication study is any study that has at least one outcome that would be considered diagnostic evidence of a claim from prior research \citep{nosek2020}.
+More frequently, replication studies are differentiated along axes that distinguish the epistemological function they are intended to serve. 
+Replications can be used to assess (1) conclusion, (2) internal, (3) construct, and (4) external validity, or (5) may act as confirmatory tests of an underlying hypothesis \citep[see][]{schmidt2009, gomez2010replications, radder2003, radder2012}.
+While the result of a replication study does not provide conclusive evidence for or against a finding, a well-executed, high-quality replication that recreates the results of an prior study typically increases confidence in that finding \citep{earp2015, nichols2021}.
+When prior results cannot be recreated through replication the claims of the prior study, the data and methods used, and the current understanding of the phenomena may be brought into question \citep{christensen2019, NASEM2019}.
 
-When a researcher asks whether the same data and procedures can be used to generate the same results as an original study the central purpose of their study is verification.
-If the researcher uses the original data, but introduces procedural differences they think may effect the original result they pursue a reanalysis designed to determine whether the original reasoning was somehow erroneous.
-Both of these approaches to replication assess the internal validity of research and are more commonly referred to as reproductions.
-If the researcher tries to follow the procedures of an original study, but collects new data, the purpose shifts to evaluating the external validity of the original result by retesting it under new conditions.
-This approach is commonly referred to as replication.
+While the number of reproduction and replication studies undertaken in the social and behavioral sciences continues to rise, such studies have not yet become commonplace in geography.
+The majority of recent research in the geographic literature on the subject has focused on reproduction over replication, and has emphasized the computational reproducibility of geographic research ahead of other dimensions.
+For example, an ongoing reproducibility initiative supported by the Association of Geographic Information Laboratories in Europe annually attempts to reproduce the computational results of submissions to their annual meeting and reports on the accessibility of related data, code, and computational environment \citep{nust2018, ostermann2021}.
+A series of reproduction studies led by Kedron and Holler \citep{Kedron2023Beyond, Kedron_Holler_Bardin_Hilgendorf_2022} advance this stream of work by introducing selected variations into the reproduction process to test the sensitivity of results to conceptual and methodological perturbations.
+However, those studies also largely focuses on testing the conclusion and internal validity of past studies through computational reproduction.
 
-While a replication or reproduction can never provide conclusive evidence for or against a finding, either type of study can be informative. 
-If a well-executed, high-quality replication or reproduction recreates the result of an original study, we are apt to increase our confidence in the original findings. 
-If a finding cannot be recreated, it reduces our confidence in the original result and suggests that our current understanding of the system being studied or our methods of testing that system are insufficient.
-
-For example, in a survey of 807 ecologists and evolutionary biologists, 64 percent admitted to failing to report non-significant results and 51 percent admitted to presenting unexpected findings as if they had been hypothesized from the start of the research \citep{fraser2018questionable}.
+The small number of published studies that have attempted to replicate geographic research suggest that many studies cannot be fully replicated \citep[e.g.,][]{Kedron2022dimaggio, paez2022reproducibility}, or are simply missing components needed to attempt a replication \citep{konkol2019, ostermann2017}.
+More often the literature on the replication of geographic research turns to the question of if and when it is reasonable to expect the findings and claims of a prior study to replicate \citep{kedron2021GA, kedron2022replication, goodchild2021replication, sui2021reproducibility}.
+Place to place variation in phenomena, and the processes that produce them, are one of the defining features of geographic research and a central tenant of many of its research traditions.
+With those intellectual foundations, it remains unclear how current geographic researchers view replication and its role in the knowledge accumulation process.
+There is similarly limited empirical evidence available about the factors that motivate or discourage geographic researchers from pursuing replications.
 
 To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of replicability, beliefs about what factors affects the chances or replicating a study, motivations to attempt replication studies, and experiences conducting replications.
-To support generalization, we designed a sampling frame to capture researchers from across disciplinary subfields and methodological approaches, and draw survey participants from that frame using a probability sampling scheme.
-In the remainder of this paper, we first present the design of our survey, sampling strategy, and analytical approach. 
-We then present the results of our survey before discussing the implications and limitations of our work.
+We are aware of only a handful of similar published surveys within the geographic literature \citep{balz2020reproducibility, konkol2019, ostermann2017, kedron2023survey}.
+However, these surveys typically focus on the quantitative and computational intensive forms of geographic research, primarily assess the availablity of research artifacts (e.g., data and code), and address reproducibility, whether the same results can be created using the same data and methods, rather than replicability.
+In all but one instance, these surveys also rely on convenience samples drawn from specialist conferences or non-representative subsets of the geographic research community. 
+In contrast, to support generalization, we designed a sampling frame to capture researchers from across disciplinary subfields and methodological approaches, and draw survey participants from that frame using a probability sampling scheme.
+In the remainder of this paper, we detail the design of our survey, sampling strategy, and analytical approach before presenting the results of our survey. 
+We then discuss the implications and limitations of our work.
 
@@
 \section*{Data and Methods}
-Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Researcher Perceptions of Replication in Geography Repository (OSF WEBSITE).
+Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Researcher Perceptions of Replication in Geography Repository (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/x6qrk/}).
 The repository connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
@@
 We followed a 4-step procedure to create a sampling frame for our survey that captures this diverse population of researchers.
-
 First, beginning at the publication level, we identified journals indexed as either geography or physical geography by the \href{https://access.clarivate.com/}{Web of Science's Journal Citation Reports} that also had a 5-year impact factor greater than 1.5.
@@
 
-Third, we created a list of researchers and their published articles, focusing on corresponding authors for two reasons.
+Third, moving to the researcher level, we created a list of researchers and their published articles, focusing on corresponding authors for two reasons.
 (1) Corresponding authorship is one indicator of the level of involvement an individual had in a given work. 
@@
 We then provided a definition based on the \citet{nosek2020replication}  to establish a common understanding of replicability for the remainder of the survey.
-Remaining questions assessed the epistomological purpose of a replication (5 questions), factors that impact the chances of successfully replicating a study (18 questions) or the decision to attempt a replication (13 questions), and what portion of the geographic literature has/could/should be replicated (3 questions).
-For researchers who reported attempting reproductions, we asked researcher to elaborate on their motivations and outcomes (9 questions).
+Remaining questions assessed the epistomological purpose of a replication (5 questions), what portion of the geographic literature has/could/should be replicated (3 questions), and factors that impact the chances of successfully replicating a study (18 questions) or the decision to attempt a replication (13 questions).
+For researchers who reported attempting reproductions, we asked them to elaborate on their motivations and outcomes (9 questions).
 
@@
 At the end of the data collection period, responses were checked for completeness and coded using the reporting standards of the American Association For Public Opinion Research \citep{aaporstandards}.
-Responses were downloaded from Qualtrics, anonymized, and stored in a public de-identified database in the research compendium (self-identifying reference removed).
+Responses were downloaded from Qualtrics, anonymized, and stored in a public de-identified database in the research compendium.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Analytical Approach}
+
+We conducted two analyses of the survey responses.
+First, we analyzed researcher perspectives on replicability by coding and calculating summary variables and statistics for three themes: how geographic researchers define replicability, factors researchers believe affect the chances of replicating a study, and factors researchers believe affect the decision to attempt to replicate a study.
+Second, we analyzed the experiences of researchers attempting to replicate prior studies using statistical summaries of participant motivations, research practices, and ability to recreate study results.
+For both analyses, we produced and analyzed descriptive statistical summaries of participant responses to Likert scale questions cross-tabulated by disciplinary subfield and methodological approach.
+For free-from text responses we coded responses and selected illustrative examples for inclusion.
+
+For free-form text definitions of ``replicability'' we coded participant responses using two procedures. 
+First, we measured the similarity of each provided definition to the definition adopted by the \citet{NASEM2019}. 
+The NASEM defines reproducible research as having three characteristics --- new data, same procedure, and same or similar results.
+To make this comparison, two of the authors independently coded each respondent definition for the presence/absence of each of these the three characteristics.
+Disagreements in the assignment of codes were resolved through discussion between the three authors.
+We created an aggregate measure of definition similarity for the final coded response for each participant by counting the presence of each NASEM definition characteristic, resulting in a measure with the domain [0, 3].
+
+Second, we coded each definition to identify mentions of: (i) internal validity assessment, (ii) external validity assessment, (iii) the significance of spatial or temporal context, (iv) epistemological necessity, and (v) adherence to open science practice.
+We derived this coding from common themes in the responses and our own reading of the replicability literature.
+As above, each definition was independently coded by each author before code assignments across authors were compared with disagreements resolved through discussion.
+Our first set of analyses examined the full set of survey responses, while our second set of analyses were restricted to the 84 participants that reported attempting a replication study in the past two years.
 
@@
 \subsection*{Researcher Definitions of Replication and its Epistemic Functions}
-\begin{itemize}
-    \item Respondents report thinking about replicability (73.9\%) talking with colleagues about replicability (65.0\%) and considering replicability when undertaking peer-review (59.0\%). 
-    \item Far fewer respondents report attempting replications (31.8\%). 
-\end{itemize}
+Geographic researchers are thinking about replicability and link the act of replicating a study to a number of different epistemological functions (Figure A). 
+A majority of respondents reported thinking about replicability (74\%), talking with colleagues about replicability (65\%), and considering replicability when undertaking peer-review (59\%) during the past two years.
+In particular, respondents believe that replication studies can be used to assess the construct validity (75\%) and external validity of a prior study.
+Specifically, respondents believe that replication studies can assess whether the claims of that study will hold in new locations (67\%) or new populations (63\%). 
+While respondents clearly linked replication to epistemological functions, across all functions they were more likely to agree than strongly agree that replications could serve these purposes.
+Respondents that identified as human geographers or as studying nature and society were less likely to agree that replications could be used to achieve these goals when compared to those working in other subfields.
+For example, 87 percent of respondents specializing in GIScience and methods believe replications could be used to assess whether a claim was the product of chance, compared to just 57 percent of human and nature-society researchers.
 
-\begin{itemize}
-    \item Coded analysis of Q6
-\end{itemize}
+\begin{center}
+\textbf{Insert Figure A About Here}
+\end{center}
 
-A majority of respondents believe replications can serve epistemic functions.
-\begin{itemize}
-    \item Q7 control of chance 64.5\%
-    \item Q7 identify product of flawed design 59.7\%
-    \item Q7 construct validity 75.2\%
-    \item External validity population 62.9\%
-    \item External validity location 67.8\%
-    \item Human, Nature Society, and Qualitative researchers had lower agreement on each point.
-\end{itemize}
+While respondents largely agree that replication has some epistemological role to play in the geographic research process, many respondents did not explicitly include these same concepts in their definitions of replicability.
+At total of 253 of our respondents provided an interpretable definition of replicability, but only 68 of those definitions (26\%) referenced some form of epistemological function. 
+Using replication to externally validate the claims of a study was identified by 49 respondents (19\%).
+No other epistemological function was mentioned by more than 13 respondents (5\%).  
+In contrast, 123 respondents (48\%) reported that replications could be used to o assess or improve how well a prior study conforms to the principles of open science.
+
+Rather than focusing on these larger concepts, most respondents used their definitions to present the criteria that identify a study as a replication.
+On average, respondents provided definitions that included 1.2 of the three characteristics of the replicability definitions adopted by the NASEM.
+Comparing the similarity of results between studies (65\%) and using the same method across studies (56\%) were the characteristics of replicability most frequently identified by respondents.
+Less than a quarter of respondents explicitly included use of the collection of new data (12\%) in their definitions.
+Only seven percent of respondent definitions included all three characteristics identified by the NASEM.
+The pattern of similarity to the NASEM definition and each of its components was consistent across subfields and methodological approaches, with a slightly greater emphasis placed on methodological consistency by quantitative and geographic methods and GIS researchers.
+
+Respondents specializing in different subfields and methodological approaches also emphasized different epistemological roles for replication in the research process.
+For example, on \textcolor{red}{INSERT SOME CONTRASTING QUOTED EXAMPLES HERE.}
 
@@
 However, the distribution of these responses is strongly right skewed.
-In fact, 46.9 percent of respondents estimated that less than 10 percent of recent studies have been replicated.
-It is unclear if respondents believe recent geographic research could or should be replicated.
+In fact, 47 percent of respondents estimated that less than 10 percent of recent studies have been replicated.
+It is similarly unclear if respondents believe recent geographic research could or should be replicated.
 On average, respondents estimated that approximately half of studies 'could be replicated' (55.0\%) or 'should be replicated' (55.9\%).
@@
 A majority of respondents identified the transparency and availability of the components of a study as affecting the odds of replication. 
-Poor documentation of the original study (74.9\%) and the use of restricted access data (66.1\%) were seen by the greatest number of respondents as decreasing the odds of being able to replicate a prior result.
-Some respondents identified the inclusion of multiple sites in a study as increasing the chances of an independent replication of the findings of that study, but not in great enough numbers to constitute a majority.
+Poor documentation of the original study (75\%) and the use of restricted access data (66\%) were seen by the greatest number of respondents as decreasing the odds of being able to replicate a prior result.
+Some respondents identified the inclusion of multiple sites in a study as increasing the chances of an independent replication of the findings of that study (39\%), but not in great enough numbers to constitute a majority.
 
 The characteristics of the research team that conducted the original study were generally not identified by respondents as likely to change the changes of replicating that study. 
-The majority of respondents (51.2\%) indicated that a large research team working on the prior study would have no effect on the chances of an independent researcher replicating that work. 
+The majority of respondents (51\%) indicated that a large research team working on the prior study would have no effect on the chances of an independent researcher replicating that work. 
 The remaining respondents were nearly evenly split as to whether a large team would increase of decrease the chances of replicating that study. 
 On the whole, more respondents believed that reliance on the unique expertise of the research team conducting a study, or the position adopted by that team would decrease, rather than increase, the chances of replicating the claims of a study.
-However, only 53.4 percent of respondents thought the position a research team chose to adopt when conducting study would decrease the chances of replicating that study. 
-Similarly, 48.8 percent of respondents identified reliance on the unique expertise of the original researcher team as decreasing the odds of replicating a study. 
+However, only 53 percent of respondents thought the position a research team chose to adopt when conducting study would decrease the chances of replicating that study. 
+Similarly, 48 percent of respondents identified reliance on the unique expertise of the original researcher team as decreasing the odds of replicating a study. 
 In both cases, 24 percent of respondents reported that they did not believe either factor would impact the odds of replicating a prior result.
@@
 About a quarter of respondents said that use of a mixed methods approach or the testing of multiple hypotheses had no effect on the chances of replication.
-In contrast, a large majority (80.6\%) of respondents identified the use of quantitative methods in a prior study as increasing the chances of replicating that study. 
+In contrast, a large majority (80\%) of respondents identified the use of quantitative methods in a prior study as increasing the chances of replicating that study. 
 This result matches the association observed in respondent definitions of replication, which ties replication to positivist science and quantitative approaches to knowledge creation.
@@
 Moreover, many respondents also saw these factors as occasionally affecting the decision to attempt a replication.
-Few respondents see a low chance of successfully replicating a study as a deterrent to attempting a replication, but it is unclear whether this result is driven by a belief in the value of null replication results, or the belief that replications in fact have high chances of success.
+Few respondents see a low chance of successfully replicating a study as a deterrent to attempting a replication, but it is unclear whether this result is driven by a belief in the value of null replication results, or the belief that replications have high chances of success.
 Finally, respondents did not identify ethical concerns as a factor affecting the decision to attempt a replication study. 
@@
 
-Respondents identified a number of factors that were omitted from our survey instrument as important when deciding whether to attempt a replication of a geographic study. 
+Respondents also identified a number of factors that were omitted from our survey instrument as important when deciding whether to attempt a replication of a geographic study. 
 These factors include practical issues such as the difficulty identifying and accessing new field sites where data would be collected during a replication attempt, the costs of conducting a replication, and the time needed to obtain institutional approvals.
@@
 
-Respondents from different disciplinary sub-fields and methodological approaches varied little in their identification of the factors affecting researchers' decisions to attempt replication studies. 
+Respondents from different disciplinary sub-fields and methodological approaches varied little in their identification of the factors affecting researchers' decisions to attempt replication studies (Table \ref{tab:motivations}).
 Human geographers and researchers using quantitative methods less frequently identified academic incentives as important to the replication decision when compared to other sub-groups, but were otherwise broadly similar in their views on artifact availability and study characteristics.
@@
 
-Overall, the differences we observed across sub-groups was small and should be interpreted with caution given the sub-group sample sizes.
-We also found that human geographers and qualitative researchers were disproportionately likely to provide 'I do not know' responses across questions,  
-which further decreases the amount of information available about their views and beliefs.
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Replication Attempts}
+In total, 84 of the researchers that responded to our survey (30\%) reported attempting to independently replicate at least one study in the last two years.   
+This subset of participants formed the basis for our analysis of researcher experiences when attempting to replicate of the work of others.
+Respondents specializing in physical geography made up the greatest percentage of replication attempts, but researchers from all the subfields we examined reported attempting replication studies - physical (39\%), human (24\%), GIScience and methods (19\%) and nature and society (15\%).
+Respondents attempting replications predominantly focused on quantitative (52\%) and mixed-methods (37\%) research designs.
+
+Most respondents reported that their replication studies were conducted in locations that differed from those of the original study (50\%), or that they first attempted to recreate the results of the original study in the same location before also testing them in a new location (18\%).
+Of the 47 respondents that identified why they decided to attempt their replication study, 38 reported they were attempting to externally validate the claims of the original study, while 20 percent reported that they were motivated to examine the impact a difference in geographic or temporal context might have on the results.
+For example, \textcolor{red}{PULL EXAMPLES FROM Q19}.
+A total of 16 respondents also identified replication as a fundamental part of knowledge creation and evaluation. 
+For example, \textcolor{red}{PULL ONE EXAMPLE FROM Q19}.
+
+In the majority of the attempted replications, respondents reported that they were able to recreate at least some of the results of the study they were investigating and form conclusions that matched those of the original study from those results.
+55 respondents (62\%) reported being able to exactly replicate some of the results of a prior study. 
+However, only six respondents (7\%) reported that they were able to exactly replicate all results.
+The survey results were similar when we asked respondents whether they were able to partially replicate the results of a study --- finding a different result, but ultimately coming to a similar conclusion as the prior study.
+62 respondents (73\%) reported being able to partially replicate at least some of the results of a study, while 14 respondents (16\%) reported being able to partially replicate all results.
+
+Respondents reported a limited ability to access the data, code, and procedures used in the studies they were attempting to replicate. 
+Respondents were generally able to access some (51\%) or all (31\%) of the data used in a prior study, but were slightly less successful at accessing some (42\%) or all (28\%) of the code and procedural information.
+Moreover, being able to access these materials and information did not mean that researcher could fully understand or directly replicate how a study was conducted.
+Only 16 respondents that attempted replications (19\%) reported being able to follow all of the procedures of a prior study without having to make additional assumptions about how the procedure was implemented.
+In all other cases the replicating researcher had to make additional assumptions about how the authors of the original study conducted their work.
+Respondents also reported that their replication attempts where complicated by an inability to recreate the computational environments of prior analyses and the unavailability of details about where a prior study was conducted.
+In only 31 cases (37\%) was the researcher able to find complete details about the geographic extent and location of the prior study.
+
+Ultimately 58 respondents that attempted replications (69\%) reported publishing some or all of their findings.
+23 respondents were able to publish all of the findings of their replication study, while another 36 respondents were able publish at lest some of their findings.
+48 Respondents that either did not attempt to publish their findings, or were only able to publish a portion of their findings, reported why they chose not to attempt publication. 
+27 respondents replied that replications were still ongoing or that it would simply take too much time to pursue publication. 
+Many other respondents said that they believe it would either be to difficult to publish their replication study because replications were not valued in the academic literature.
+For example researchers pointed out that, "no one seems to care", their results received "no interest from journals", and that "incentives in academia clearly point towards publishing original research."
+In one instance, "The journal that published the original paper specifically claimed to be interested in replications, but then desk rejected our replication."
+This reasoning reflects different form of non-response and selection bias at the root of the 'file drawer problem' in academic literature (CITE - Rosenthal 1979). 
+The file drawer problem exists when the outcome of a study influence the decision to publish or share that finding.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Discussion and conclusion}
+The results of our survey suggest geographic researchers are familiar with replication and believe that replication studies can serve several epistemological functions.
+However, we also found that researcher provided definitions often did not clearly articulate the epistemological role, or roles, that could be played by a replication study. 
+Researcher definitions instead focused on criteria used to identify a study as a replication. 
+This same focus on criteria can be observed in the wider R\&R literature, where authors typically broadly gesture to the epistemological function of replication then quickly turn to the accounting of data and code sharing practices.
+This tendency toward criteria suggests that replication as an epistemological tool may not be at the forefront of geographic researchers' thinking about replication.
+
+It also remains unclear if or how geographic researchers map variations between an original study and its replication to the epistemological functions that replication study is intended to serve.
+A clear understanding of this connection between variations and functions is essential because which aspects of a study are changed controls the form of validity being assessed \citep{gomez2010replications, radder2003, schmidt2009}.
+Poor documentation and articulation of these connections in replication studies of geographic research could lead to the misinterpretation of the results of an individual replication, and could misdirect the collective assessment of a claim across a set of replication studies.
+Developing a schema to map replication study variations to functions may be particularly challenging in geography due to the complexity of geographic systems and the limited control researchers have over those systems.
+Moreover, it is often unclear which aspect of a study are changing when a replication study is conducted in a new location. 
+For example, when a researcher conducting a replication collects new data from a new location it may be difficult to determine whether the study is testing the external validity of a claim in a new population, or in the same population that is subjected to different place-based processes.
+Our results suggest that a conceptual treatment of these connections attuned to the peculiarities of spatial data analysis would be an important first step toward conducting and systematically assessing interpretable replication studies of geographic research.
+
+The results of our survey suggest that collectively researchers are uncertain whether it is valuable to replicate recent geographic research. 
+Our results do indicate that it is unlikely that this uncertainty stems from a lack of belief in the potential epistemological value of replication studies.
+Instead, mirroring traditional debates within the discipline, it may be the case that researchers are uncertain whether, or to what extend, the results and claims of a study should be expected to replicate in new locations.
+Researcher uncertainty may also be a reflection of the perceived quality and importance of the available geographic literature. 
+If researchers believe many studies simply do not contain important findings, it would be rationale not to prioritize replicating those studies.
+Finally, researchers may simply perceive the external validity check offered by replication as not important to the goals of their research tradition. 
+Following \citet{sayer1992method} distinction between intensive and extensive research, many traditions in geography focus on reconstructing the causal chains that structure social and environmental relations in specfic contexts, rather than the discovery of empirical regularities across those contexts.
+While some of the qualitative responses to our survey are suggestive of these points, follow-up research could delve more deeply into which studies researcher believe are valuable to replicate and why.
+
+Disciplinary variation
+\begin{itemize}
+    \item Overall, the differences we observed across sub-groups was small, but should be interpreted with caution given the sub-group sample sizes.
+    \item We also found that human geographers and qualitative researchers were disproportionately likely to provide 'I do not know' responses across questions, which further decreases the amount of information available about their views and beliefs.
+\end{itemize}
 
 %%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Replication Attempts}
-\begin{itemize}
-    \item sub-set demographics
-    \item Q18 - same location response to characterize the attempts
-    \item Q19 - Motivations
-    \item Q20-21 - Replication outcome to component accessibility comparison. Perhaps also a comparison of success across locations by field of study (depending on the numbers).
-    \item From Q21f percent that published their findings. The into Q22 why didn't respondents pursue publication.
-\end{itemize}
+\subsection*{Limitations} 
+Survey research has several common limitations which we attempted to mitigate through the design of our study. 
+Unlike prior surveys of reproducibility and replicability, our study uses a sampling frame designed to be representative of our target population of active geographic researchers. 
+However, use of a well-constructed sampling frame and probability sampling do not ensure that a balanced and representative sample will be drawn from the target population. 
+Ideally, we would stratify our potential respondents into meaningful subgroups, randomly draw participants from these subgroups, and use a post-stratification procedure to address any imbalance in our response.
+However, we could not follow this approach because stratification require knowledge of the population characteristics that predicts differences in response and a population wide census of those key predictors.
+We did not have access to this information because we presently lack a comprehensive understanding of replicability in geography and no list of geographic researchers complete with relevant predictor information exists.
+Given these limitations, our study should be viewed as an exploratory analysis with random sampling and a transparent, reproducible methodology for sample frame construction.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Conclusion}
-A standing question is how should geographic research approaches be designed to efficiently generate reliable knowledge.
+We have similarly worked to reduce the effects of several other common forms of bias from our survey.
+We have worked to eliminate exclusion bias by including in our sampling frame all researchers publishing as corresponding authors in any wide range of geography journals over a five year period.
+However, geographic researchers publish in a range of journals that are not necessarily indexed as geography by the Web of Science. 
+Geographic researchers that have only published outside geographically indexed journals would not be captured in our sampling frame which would create exclusion errors. 
+However, we believe the number of individuals falling into this category will be small as most active geographic researchers are likely to have published at least one study in the journals meeting our inclusion criteria.
+
+Similarly, we cannot eliminate the possibility of self-selection bias from our survey. 
+It may be the case that geographic researchers more familiar with replication, or those working in subfields more involved with current R\&R debates (e.g., quantitative, computational research) were more likely to respond to our survey.
+Conversely, it may also be the case that researchers working in subfields traditionally associated with critiques of a positivist scientific approach (e.g., qualitative, human geography) were less likely to participate in our survey.
+We attempted to quantify potential self-selection by calculating and comparing survey completion rates across subfields and approaches. 
+Completion rates for all subfields were between 84 and 87 percent, except slightly higher rates for geographic methods and GIS researchers (96.8\%).
+Completion rates were 84.2 percent for mixed methods, 87.0 percent for qualitative methods, and 91.1 percent for quantitative methods. 
+These values suggest that self-selection was not a significant issue.
+
+We attempted to mitigate the potential for questionnaire bias, which could be caused by partially basing our survey instrument on prior studies that over-represent perspectives from the computational and experimental sciences.
+If this were the case, our survey may not gather data on researcher practices and beliefs relevant to replicating types of research not well represented in the existing literature. 
+To address this concern, we incorporated into our survey instrument questions informed by a parallel review of the R\&R literature available within geography and a review of critiques of positivist science made by social scientists and human geographers.
+We also provided the option for an open ended text response to questions to identify issues we did not anticipate during instrument construction.
+
+Finally, our survey provides a description of the perspectives of geographic researchers at one point in time and one depth of understanding.
+As the first survey of its kind, our work provides an initial measurement of geographers definitions of replicability, beliefs about what factors affects the chances
+or replicating a study, motivations to attempt replication studies, and experiences
+conducting replications. 
+However, in many cases we were not able to probe more deeply into the nuances of these measurements and the conceptualization that underlie them.
+For example, as highlighted in the discussion, we were able to gain only limited insight into the epistemological roles researchers believe replications can serve and how they map those roles onto what is changes in a replication study.
+Future research using in-depth interviews or multi-analyst study designs could probe these question more deeply. 
+It would also be useful to track the information collected in this survey over time and to link that tracking to specific topics. 
+For example, understanding how researcher perspectives on the epistemological function of replication shift in climate change impacts research may be a useful indicator of how well researchers in that field are developing theories and methodologies capable of dealing with increasing variation and shifting baselines induced by climate change.
+More broadly, regular monitoring of perceptions of replication would help identify areas in need of engagement, as well as the success or failure of past investments designed to enhance R\&R.
 

### 2023-09-27 procedure/code/04-figures.R
Updated figures with and without labeling.

@@ -2,322 +2,251 @@ library(here)
 library(tidyverse)
 library(table1)
 library(officer)
-
-
+library(ggthemes)
+library(ggridges)
+library("ggtext")
+library(extrafont)
+download.file("http://simonsoftware.se/other/xkcd.ttf",
+              dest="xkcd.ttf", mode="wb")
+system("mkdir ~/.fonts")
+system("cp xkcd.ttf  ~/.fonts")
+font_import(paths = "~/.fonts", pattern="[X/x]kcd")
+fonts()
+loadfonts()
+library(stats)
 #--------------------------------#
-#-                              -#
-#- PERFORM DESCRIPTIVE ANALYSIS -#
-#-                              -#
+#- Figures -#
 #--------------------------------#
 analysis_hegs_rpl <- readRDS(here("data","derived","public","analysis_hegs_rpl.rds"))
 
-#Recode Q8 and Q10 
+
+#-------------------------------------------------------------------------------#
+#Fig A - Diverging bar graph from Q7
+#      - Larger font for the percentage values embedded in the bars
+#      - Confirm that percentages are being generated correctly
+#-------------------------------------------------------------------------------#
+
+#Subset data to Q7 and apply descriptive variable names
+Fig_A <-analysis_hegs_rpl[,substr(names(analysis_hegs_rpl), 1,2) == "Q7"]
+names(Fig_A) <- c("Chance",
+                  "Flawed Design",
+                  "Accurately Reflect Concepts",
+                  "Holds Across Populations",
+                  "Holds Across Location")
+
+Fig_A <- as.data.frame(Fig_A[,c(1,2,3,4,5)])
+
+jpeg(here("results","figures","Fig_A_labeled.jpeg"), units="in", width=11, height=7, res=300)
+pivot_longer(Fig_A, everything()) %>%
+  group_by(name) %>%
+  dplyr::count(value) %>%
+  mutate(percentage = (n/283),
+         percentage_diverging = ifelse(value %in% c("Strongly disagree","Disagree"),
+                                       -1*percentage,
+                                       percentage),
+         name = factor(name, levels=c("Chance",
+                                      "Flawed Design",
+                                      "Accurately Reflect Concepts",
+                                      "Holds Across Populations",
+                                      "Holds Across Location"
+         )),
+         label = paste0(round(percentage*100,0),""),
[…]

### 2023-09-28 docs/manuscript/manuscript.tex

@@
 We developed the survey questions following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility and replicability literature.
-We pilot tested the survey instrument with \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
+We pilot tested the survey instrument with \textit{n}=15 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
 After pilot testing, we removed these individuals from our sampling frame to ensure they would not be included in our final sample.
@@
 \subsection*{Data Collection}
-We used a digital form of the Tailored Design Method \citep{dillman2014internet} to survey geographic researchers between May 17 and June 10, 2022.
+We used a digital form of the Tailored Design Method \citep{dillman2014internet} to survey geographic researchers between Oct 3 and Oct 27, 2022.
 A simple random sample of 2,000 researchers was drawn without replacement from our sampling frame, and those researchers were invited via email to participate in the online survey. 
-Researchers received their initial invitation on May 17, 2022. 
-Two reminder emails were sent to researchers that had not yet completed the survey on May 26 and May 31, 2022.
+Researchers received their initial invitation on Oct 3, 2022. 
+Two reminder emails were sent to researchers that had not yet completed the survey on Oct 13 and Oct 20, 2022.
 
@@
 \subsection*{Researcher Definitions of Replication and its Epistemic Functions}
-Geographic researchers are thinking about replicability and link the act of replicating a study to a number of different epistemological functions (Figure A). 
+Geographic researchers are thinking about replicability and link the act of replicating a study to a number of different epistemological functions (Figure \ref{fig:Q7-Epistemology}). 
 A majority of respondents reported thinking about replicability (74\%), talking with colleagues about replicability (65\%), and considering replicability when undertaking peer-review (59\%) during the past two years.
@@
 \begin{center}
-\textbf{Insert Figure A About Here}
+\textbf{Insert Figure \ref{fig:Q7-Epistemology} About Here}
 \end{center}
@@
     \centering
-    \includegraphics[scale=0.5]{results/figures/Fig-Q12-HCS.png}
+    \includegraphics[scale=1]{results/figures/Fig1-Q7-Epistemology.png}
+    \caption{Perceptions of the epistemological function of replication studies.
+Respondents identified the extent to which they agree replication studies can be used to assess the claims or features of past research; `don't know' (DK), and missing (M) responses.}
+    \label{fig:Q7-Epistemology}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%
+\newpage
+
+\begin{figure}[hbt!]
+    \centering
+    \includegraphics[scale=0.5]{results/figures/Fig2-Q12-HCS.png}
     \caption{Estimates of the percentage of geographic studies that (a) have been replicated, (b) could be replicated, or (c) should be replicated}
@@
     \centering
-    \includegraphics[scale=0.8]{results/figures/Fig-Q8-10-Chances.png}
+    \includegraphics[scale=0.8]{results/figures/Fig3-Q8-10-Chances.png}
     \caption{Factors affecting the chances of replicating a study.
@@
     \centering
-    \includegraphics[scale=0.80]{results/figures/Fig-Q15-Decisions.png}
+    \includegraphics[scale=0.80]{results/figures/Fig4-Q15-Decisions.png}
     \caption{Factors Affecting Researcher Decisions to Undertake Replication Studies.

### 2023-09-28 docs/manuscript/manuscript.tex
Update author info

@@
 \newpage
-\noindent PETER KEDRON is an Associate Professor in the School of Geographical Science and Urban Planning and core faculty member in the Spatial Analysis Research Center (SPARC) at Arizona State University, Tempe, AZ, 85283, US.
-Email: Peter.Kedron@asu.edu.
-His research interests include spatial analysis, geographic information science, economic geography, and the accumulation of knowledge about geographic phenomena.
+\noindent PETER KEDRON is an Associate Professor in Department of Geography at University of California Santa Barbara, Santa Barbara CA, 93106, US.
+Email: peterkedron@ucsb.edu.
+His research program develops and uses spatial analytical methods to understanding persistently uneven patterns of spatial development.
+His recent work focuses on improving the production and accumulation of knowledge used to benefit society through policy.
 \\
 
-\noindent JOSEPH HOLLER is an Assistant Professor of Geography at Middlebury College, Middlebury, VT, 05753, US. Email: \\
+\noindent JOSEPH HOLLER is an Assistant Professor of Geography at Middlebury College.
+He is human geographer and geographic information scientist with research interests in social vulnerability and adaptation in the context of climate change and environmental degradation.
+His research intersects with work in political ecology, development geography, human dimensions of global change, and geographic information science.
+\\
 
-\noindent SARAH BARDIN is a PhD candidate ...
+\noindent SARAH BARDIN is a doctoral student in Geography at the School of Geographical Sciences and Urban Planning at Arizona State University.
+Her research focuses on leveraging spatial modeling and GIS to generate policy-relevant, actionable insights from data.
 

### 2023-09-28 procedure/code/04-figures.R
Updated fig 3

@@ -13,12 +13,11 @@ system("cp xkcd.ttf  ~/.fonts")
 font_import(paths = "~/.fonts", pattern="[X/x]kcd")
 fonts()
 loadfonts()
-library(stats)
+
 #--------------------------------#
 #- Figures -#
 #--------------------------------#
 analysis_hegs_rpl <- readRDS(here("data","derived","public","analysis_hegs_rpl.rds"))
-
 
 #-------------------------------------------------------------------------------#
 #Fig A - Diverging bar graph from Q7
@@ -100,6 +99,7 @@ analysis_hegs_rpl <- analysis_hegs_rpl %>%
                                                                                                                                           `Occasionally` = 2,
                                                                                                                                           `Frequently` = 1,
                                                                                                                                           `Always` = 0,
+                                                                                                                                          `Don't know` = 5,
                                                                                                                                           .default = NaN)))
 
 
@@ -226,11 +226,10 @@ pivot_longer(Fig_3, everything()) %>%
                                       "Lack of Funding",
                                       "Original Research"
          ))) %>%
-  filter(!is.na(value) & value!="Don't know") %>%
   ggplot(aes(x = name, y = percentage, fill = value)) +
   geom_bar(position = position_fill(reverse = TRUE), stat = "identity", width = 0.8) +
   coord_flip() + 
-  scale_fill_manual(values = c("#CD2311","#EF5645","#BFBFBF","#D9D9D9","#F2F2F2")) +
+  scale_fill_manual(values = c("#CD2311","#EF5645","#BFBFBF","#D9D9D9","#F2F2F2"), na.value="white") +
   ylab("") + 
   xlab("") +
   scale_x_discrete(expand = c(0, 0))  +
@@ -248,5 +247,24 @@ pivot_longer(Fig_3, everything()) %>%
         legend.title =element_blank()) 
 dev.off()
 
+#--------------------------------#
+#- Tables -#
+#--------------------------------#
+
+#-------------------------------------------------------------------------------#
+#Table 1 - Demographics of individuals who attempted a reproduction
+#-------------------------------------------------------------------------------#
+table(analysis_hegs_rpl$Q17_rep_behavior_5) ## 90 individuals reported attempting replications
+nonreplications <- c("R_3J8E376HYtxj70C","R_26hSbKV3v7G37sN","R_1dBrF30sz0LEXbx",
+                     "R_ANzRI4FyY6OkG0p","R_2arhrt5roJt2dUu","")
 
 
+
+
+
+
+
[…]

### 2023-09-29 procedure/code/03-analysis.R
Created new demographic and summary tables for replication sample

@@ -224,3 +224,57 @@ t1flex(Q4_table7) %>%
                pr_section = sect_properties)
 
 
+
+#--------------------------------#
+#- New Tables -#
+#--------------------------------#
+
+#Identify set of respodents who reported attempting a replication
+completed_rep <- read_xlsx(here("data","derived","public","Q17_coding.xlsx"))
+completed_rep <- completed_rep %>% 
+  filter(rep_flag == 1) %>%
+  transmute(ResponseId, rep_flag)
+
+replication_sample <- left_join(completed_rep,analysis_hegs_rpl,by="ResponseId")
+
+#-------------------------------------------------------------------------------#
+#Table 1 - Demographics of individuals who attempted a replication
+#-------------------------------------------------------------------------------#
+table1::label(replication_sample$Q3_recoded)   <- "Subdiscipline"
+table1::label(replication_sample$Q4_quantqual) <- "Methods"
+table1::label(replication_sample$Q24_lab_size) <- "Size of lab"
+table1::label(replication_sample$Q25_title)    <- "Title"
+table1::label(replication_sample$Q1_age)       <- "Age"
+
+rep_sample_demo <- table1::table1(~Q4_quantqual + Q24_lab_size + Q25_title + Q1_age +  Q3_recoded + Q4_quantqual, data = replication_sample)
+
+# Output tables using write table and flextable
+write.table(rep_sample_demo , here("results","tables","rep_sample_demo.csv"), col.names = T, row.names=F, append= T, sep=',')
+
+#-------------------------------------------------------------------------------#
+#Table 2 - Summary stats for individuals who attempted a replication
+#-------------------------------------------------------------------------------#
+table1::label(replication_sample$Q18_same_loc)      <- "Same location"
+table1::label(replication_sample$Q20_rep_results_1) <- "Exactly replicated"
+table1::label(replication_sample$Q20_rep_results_2) <- "Partially replicated"
+table1::label(replication_sample$Q20_rep_results_3) <- "Not replicated"
+table1::label(replication_sample$Q21_rep_process_1) <- "Access to data"
+table1::label(replication_sample$Q21_rep_process_2) <- "Access to code"
+table1::label(replication_sample$Q21_rep_process_3) <- "Follow procedures exactly"
+table1::label(replication_sample$Q21_rep_process_4) <- "Recreate computational environment"
+table1::label(replication_sample$Q21_rep_process_5) <- "Find details about geographic location and extent"
[…]

### 2023-09-29 procedure/code/04-figures.R

@@ -13,6 +13,7 @@ system("cp xkcd.ttf  ~/.fonts")
 font_import(paths = "~/.fonts", pattern="[X/x]kcd")
 fonts()
 loadfonts()
+library(readxl)
 
 #--------------------------------#
 #- Figures -#
@@ -247,24 +248,22 @@ pivot_longer(Fig_3, everything()) %>%
         legend.title =element_blank()) 
 dev.off()
 
-#--------------------------------#
-#- Tables -#
-#--------------------------------#
+fig3_values <- pivot_longer(Fig_3, everything()) %>%
+  group_by(name) %>%
+  dplyr::count(value) %>%
+  mutate(percentage = (n/283),
+         name = factor(name, levels=c("Ethical Concerns",
+                                      "Low Chance of Success",
+                                      "Geographic Variation",
+                                      "Inexperience",
+                                      "Recreating Methods",
+                                      "Method Access",
+                                      "Data Access",
+                                      "Fraud",
+                                      "Difficulty Publishing",
+                                      "Perceived Value",
+                                      "Lack of Funding",
+                                      "Original Research"
+         )))
+write_csv(fig3_values, "fig3_labels.csv")
 
-#-------------------------------------------------------------------------------#
-#Table 1 - Demographics of individuals who attempted a reproduction
-#-------------------------------------------------------------------------------#
-table(analysis_hegs_rpl$Q17_rep_behavior_5) ## 90 individuals reported attempting replications
-nonreplications <- c("R_3J8E376HYtxj70C","R_26hSbKV3v7G37sN","R_1dBrF30sz0LEXbx",
-                     "R_ANzRI4FyY6OkG0p","R_2arhrt5roJt2dUu","")
-
-
-
-
-
-
-
-Please also create summary statistics tables showing counts and percentages of respondents for the subsequent 
-questions through Q23 (ignoring the text responses).
-
-ln 401; please calculate these same completion rates for this survey. The current number are from the reproduction sruvey.

### 2023-12-15 docs/manuscript/manuscript.tex

@@
 \newtheorem{notation}{Notation}
+\usepackage{csquotes}
 
@@
 \section*{Introduction}
-Since the 1600s, replication has been a defining characteristic of the scientific method and an essential tool of researchers working to understanding and explain phenomena. 
-Broadly defined, a replication study is any study that has at least one outcome that would be considered diagnostic evidence of a claim from prior research \citep{nosek2020}.
-More frequently, replication studies are differentiated along axes that distinguish the epistemological function they are intended to serve. 
-Replications can be used to assess (1) conclusion, (2) internal, (3) construct, and (4) external validity, or (5) may act as confirmatory tests of an underlying hypothesis \citep[see][]{schmidt2009, gomez2010replications, radder2003, radder2012}.
-While the result of a replication study does not provide conclusive evidence for or against a finding, a well-executed, high-quality replication that recreates the results of an prior study typically increases confidence in that finding \citep{earp2015, nichols2021}.
-When prior results cannot be recreated through replication the claims of the prior study, the data and methods used, and the current understanding of the phenomena may be brought into question \citep{christensen2019, NASEM2019}.
+Attempting to replicate a study is a means of critically assessing whether the evidence provided by the researchers that conducted the study support the claims they make and their explanation of a phenomenon.
+Replications confront existing explanations with new evidence by retesting prior claims using new data, while typically controlling for procedural differences by conducting similar analyses.
+Replications can be designed to serve epistemic functions and to test several forms of validity.
+Attempts to reproduce prior research also retest claims, but do so using the same data and the same, or very similar, analyses. 
+The central focus a reproduction attempt is the verification of claims through the examination of how a study was conducted and whether the design and execution of that study support the results presented.
+While the results of a reproduction or replication do not provide conclusive evidence for or against a claim, those that produce outcomes consistent with prior studies typically increase confidence in a claim and the theories underlying it \citep{earp2015, nichols2021}.
+When prior results cannot be recreated, the claims of the prior study, the data and methods used, and the current understanding of the phenomena may be brought into question \citep{christensen2019, NASEM2019}.
 
@@
 A series of reproduction studies led by Kedron and Holler \citep{Kedron2023Beyond, Kedron_Holler_Bardin_Hilgendorf_2022} advance this stream of work by introducing selected variations into the reproduction process to test the sensitivity of results to conceptual and methodological perturbations.
-However, those studies also largely focuses on testing the conclusion and internal validity of past studies through computational reproduction.
+However, those studies also largely focus on testing the conclusion and internal validity of past studies through computational reproduction.
 
@@
 Place to place variation in phenomena, and the processes that produce them, are one of the defining features of geographic research and a central tenant of many of its research traditions.
-With those intellectual foundations, it remains unclear how current geographic researchers view replication and its role in the knowledge accumulation process.
+With those intellectual foundations, it remains unclear how current geographic researchers view replication and the role of the practice in the knowledge accumulation process.
 There is similarly limited empirical evidence available about the factors that motivate or discourage geographic researchers from pursuing replications.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Replication and the Evaluation of Prior Claims}
+Broadly defined, a replication study is any study that has at least one outcome that would be considered diagnostic evidence of a claim from prior research, and can be used to assess the validity of prior claims \citep{nosek2020}.
+More narrowly, replication studies are differentiated by the alterations they make to a study, which is linked to the epistemological function they are intended to serve.
+By altering different aspects of a study a researcher attempting a replication can use their finding to potentially assess (1) conclusion, (2) internal, (3) construct, and (4) external validity \citep[see][]{schmidt2009, gomez2010replications, radder2003, radder2012}.
+
+OLD: Replications provide evidence of the credibility of claims across conditions that either naturally or are purposefully manipulated to differ from the original study.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Data and Methods}
-Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Researcher Perceptions of Replication in Geography Repository (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/x6qrk/}).
-The repository connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
+Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Researcher Perceptions of Replication in Geography project (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/x6qrk/}).
+That OSF project connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
 All of the results presented in this paper can be independently reproduced using the materials in that repository.
@@
 From those journals, we created a database of all articles published between 2017 and 2021.  
-
 Second, we used Arizona State University's institutional subscription to the \href{https://www.scopus.com/home.uri}{Scopus Database} to extract journal information (e.g., subject area, ranking), article information (e.g., abstract, citation counts), and author information (e.g., corresponding status, email) for each publication.
@@
 We asked each participant to assess their familiarity with the term ``replicability'' and to provide their own definition. 
-We then provided a definition based on the \citet{nosek2020replication}  to establish a common understanding of replicability for the remainder of the survey.
-Remaining questions assessed the epistomological purpose of a replication (5 questions), what portion of the geographic literature has/could/should be replicated (3 questions), and factors that impact the chances of successfully replicating a study (18 questions) or the decision to attempt a replication (13 questions).
+We then provided a definition based on \citet{nosek2020} to establish a common understanding of replicability for the remainder of the survey.
+Specifically, replication was defined as,
+
+\begin{displayquote}
+    ``A \textbf{Replication} is any study that seeks to evaluate a claim of a prior study using similar procedures and new data.
+A claim made in a prior study have been replicated when the replication produces outcomes that are consistent with the prior claim and increase confidence in that claim."
+\end{displayquote}
+
+\noindent Remaining questions assessed the epistomological purpose of a replication (5 questions), what portion of the geographic literature has/could/should be replicated (3 questions), and factors that impact the chances of successfully replicating a study (18 questions) or the decision to attempt a replication (13 questions).
 For researchers who reported attempting reproductions, we asked them to elaborate on their motivations and outcomes (9 questions).
@@
 Researchers received their initial invitation on Oct 3, 2022. 
-Two reminder emails were sent to researchers that had not yet completed the survey on Oct 13 and Oct 20, 2022.
+Two reminder emails were sent on Oct 13 and Oct 20, 2022 to researchers that had not yet completed the survey.
 
@@
 We conducted two analyses of the survey responses.
-First, we analyzed researcher perspectives on replicability by coding and calculating summary variables and statistics for three themes: how geographic researchers define replicability, factors researchers believe affect the chances of replicating a study, and factors researchers believe affect the decision to attempt to replicate a study.
-Second, we analyzed the experiences of researchers attempting to replicate prior studies using statistical summaries of participant motivations, research practices, and ability to recreate study results.
+First, we analyzed researcher perspectives on replicability by coding and calculating summary variables and statistics for three themes: how geographic researchers define replicability, factors researchers believe affect the decision to attempt to replicate a study, and factors researchers believe affect the chances of sucessfully replicating a study.
+Second, we analyzed the experiences of researchers attempting to replicate prior studies using statistical summaries of participant motivations, research practices, and ability to produce results consistent with prior studies.
 For both analyses, we produced and analyzed descriptive statistical summaries of participant responses to Likert scale questions cross-tabulated by disciplinary subfield and methodological approach.
@@
 Specifically, respondents believe that replication studies can assess whether the claims of that study will hold in new locations (67\%) or new populations (63\%). 
-While respondents clearly linked replication to epistemological functions, across all functions they were more likely to agree than strongly agree that replications could serve these purposes.
+While respondents clearly linked replication to epistemological functions, across all functions they were more likely to agree than to strongly agree that replications could serve these purposes.
 Respondents that identified as human geographers or as studying nature and society were less likely to agree that replications could be used to achieve these goals when compared to those working in other subfields.
@@
 No other epistemological function was mentioned by more than 13 respondents (5\%).  
-In contrast, 123 respondents (48\%) reported that replications could be used to o assess or improve how well a prior study conforms to the principles of open science.
+In contrast, 123 respondents (48\%) reported that replications could be used to assess or improve how well a prior study conforms to the principles of open science (e.g., sharing procedures).
+
+Within the limited subset of respondents that explicitly discussed epistemology in their definitions, a small number of researchers carefully articulated connections between the assessment of external validity and the investigation and influence of geographic and temporal context.
+For example, one participant defined replicability as,
+
+\begin{displayquote}
+``the degree to which a study could be conducted in the same way again, at a different point in time and by other people.
+Good replicability necessitates that study sites, methods and materials are described in adequate detail.
+But then there's the question of what replicability means in observational studies where the whole setting of the study changes in time (e.g.
+forest succession in study sites) so that the study cannot be repeated in the same way in the same area again.
+Also, there's a difference between replicability of a study and replicability of results.
+A replicable study does not automatically yield replicable results."
+\end{displayquote}
+
+\noindent More often respondents simply labelled validity checks as the purpose of a replication, as when one researcher defined replicability as, ``The ability to reproduce a study using the same or similar research design to test both its internal and external valdity."
+A number of respondents specializing in qualitative research provided definitions that questioned, or even rejected, the role of replication in their subfield. 
+One representative articulates this position by defining replicability as,
+
+\begin{displayquote}
+    ``The claim that empirical research of a study can be repeated in the same way as it was done in the study.
+However, this is not exactly possible in qualitative research, as data collection is always a co-construction between all persons involved in the data collection.
+Transferred to qualitative research, this means for me rather that one would use the same questions, analyse the data with the same methods, etc.
+The fact that the results are not necessarily the same is not a weakness, but rather to be expected, since our knowledge is always embedded and co-constructed."
+\end{displayquote}
 
@@
 Only seven percent of respondent definitions included all three characteristics identified by the NASEM.
+A representative definition provided by one respondent identified replicability as, ``That another researcher can get the same results as you by using the same methodological approach."
 The pattern of similarity to the NASEM definition and each of its components was consistent across subfields and methodological approaches, with a slightly greater emphasis placed on methodological consistency by quantitative and geographic methods and GIS researchers.
-
-Respondents specializing in different subfields and methodological approaches also emphasized different epistemological roles for replication in the research process.
-For example, on \textcolor{red}{INSERT SOME CONTRASTING QUOTED EXAMPLES HERE.}
 
@@
 It is similarly unclear if respondents believe recent geographic research could or should be replicated.
-On average, respondents estimated that approximately half of studies 'could be replicated' (55.0\%) or 'should be replicated' (55.9\%).
+On average, respondents estimated that approximately half of studies `could be replicated' (55.0\%) or `should be replicated' (55.9\%). 
 However, the distribution of responses to both questions are relatively flat across the range of possible values and highly variable (\textit{$sd_{could}=24.3\%$}, \textit{$sd_{should}=27.7\%$}), which suggests
 respondents were uncertain whether it was possible or valuable to replicate recent research.  
+This pattern of response was consistent across respondents that self-identified as working in different subfields and methodological approaches.
 
@@
 
-Respondents identified a range of factors that might impact the chances of an independent researcher replicating the claims of a prior study (Figure \ref{fig:Q8-10-Chances}a).
+Respondents identified a range of study characteristics that might impact the chances of an independent researcher replicating the claims of a prior study (Figure \ref{fig:Q8-10-Chances}a).
 A majority of respondents identified the transparency and availability of the components of a study as affecting the odds of replication. 
@@
 The remaining respondents were nearly evenly split as to whether a large team would increase of decrease the chances of replicating that study. 
-On the whole, more respondents believed that reliance on the unique expertise of the research team conducting a study, or the position adopted by that team would decrease, rather than increase, the chances of replicating the claims of a study.
-However, only 53 percent of respondents thought the position a research team chose to adopt when conducting study would decrease the chances of replicating that study. 
+On the whole, more respondents believed that reliance on the unique expertise of the research team conducting a study, or the unique position of a researcher would decrease, rather than increase, the chances of replicating the claims of a study.
+However, only 53 percent of respondents thought the unique position of a researcher would decrease the chances of replicating that study. 
 Similarly, 48 percent of respondents identified reliance on the unique expertise of the original researcher team as decreasing the odds of replicating a study. 
@@
 
-Respondents were similarly divided about the extend to which the approach adopted in the prior study would affect the chances of replicating that study. 
-Respondents were nearly evenly split as to whether the number of hypotheses tested by a study, and whether that study used qualitative or mixed methods would increase or decrease an independent researcher's chances of finding results that supported the claims of the prior study.
+Respondents were similarly divided about the extent to which the approach adopted in the prior study would affect the chances of replicating that study. 
+Respondents were nearly evenly split as to whether the number of hypotheses tested by a study, and whether that study used qualitative or mixed methods, would increase or decrease an independent researcher's chances of finding results that supported the claims of the prior study.
 About a quarter of respondents said that use of a mixed methods approach or the testing of multiple hypotheses had no effect on the chances of replication.
@@
 For all six of the characteristics we examined, at least 12 percent of respondents replied that those factors would have no effect on the chances of replicating a prior study.
-Numerous respondents also replied that they the simply did not know whether a characteristic would impact the chances of replicating a study. 
+Numerous respondents also replied that they simply did not know whether a characteristic would impact the chances of replicating a study. 
 For example, 20 percent of respondents said they did not know whether a phenomenon being spatially dependent with itself would affect the chances of replicating a prior study, and an additional 15 percent of respondents said spatial dependence would have no effect on replication.
@@
 Respondents were roughly evenly divided on whether other factors would increase or decrease the chances of replicating a study.
-Respondents also favored 'somewhat likely' responses over stronger 'very likely' responses across all characteristics, which further suggests that absence of a clear consensus understanding of how these factors relate to and impact replication.
+Respondents also favored `somewhat likely' responses over stronger `very likely' responses across all characteristics, which further suggests that absence of a clear consensus understanding of how these factors relate to and impact replication.
 
@@
 Finally, respondents did not identify ethical concerns as a factor affecting the decision to attempt a replication study. 
-However, several of these results should also be interpreted with caution. 
+However, these results should also be interpreted in the context of the different levels of uncertainty respondents expressed for each question. 
 More that 15 percent of respondents replied that they did not know whether geographic variation, inexperience with replication, or ethical concerns would affect a researcher's decision to attempt a replication.
 
-Respondents also identified a number of factors that were omitted from our survey instrument as important when deciding whether to attempt a replication of a geographic study. 
-These factors include practical issues such as the difficulty identifying and accessing new field sites where data would be collected during a replication attempt, the costs of conducting a replication, and the time needed to obtain institutional approvals.
+Respondents also qualitatively identified a number of factors that were omitted from our survey instrument as important when deciding whether to attempt a replication of a geographic study. 
+These factors include practical issues such as the difficulty identifying and accessing new field sites where data would be collected during a replication attempt, the costs of conducting a replication, and the time needed to obtain institutional ethics approvals.
 Respondents also identified uncertainty about how to compare the results of a replication attempt to the original as important when deciding to undertake a replication attempt. 
+For example, one respondent noted that.
+``Given expected spatial variation, it can be difficult to arrive at a valid metric that would affirm replication while properly acknowledging the inherent variability."
 Finally, a small number of respondents believe that geographic researchers do not undertake replication studies because they either believe that replication is not possible or not necessary in geography.
 These respondents argued that the main value of geographic studies is that each study provide a unique lens on the portion of the world under investigation, which makes replication a unnecessary endeavour.
+As one respondent stated,
+
+\begin{displayquote}
+    ``It [replication] just doesn't seem necessary.
+The pertinent outcomes aren't simply the empirical findings, but the ways in which they are interpreted and the lenses on the world that are generated.
+These won't be replicated - they've already been produced from the initial research.
+Just producing similar data from another study doesn't seem very valuable."
+\end{displayquote}
 
@@
 Most respondents reported that their replication studies were conducted in locations that differed from those of the original study (50\%), or that they first attempted to recreate the results of the original study in the same location before also testing them in a new location (18\%).
-Of the 47 respondents that identified why they decided to attempt their replication study, 38 reported they were attempting to externally validate the claims of the original study, while 20 percent reported that they were motivated to examine the impact a difference in geographic or temporal context might have on the results.
-For example, \textcolor{red}{PULL EXAMPLES FROM Q19}.
+Of the 47 respondents that identified why they decided to attempt their replication study, 38 reported they were attempting to externally validate the claims of the original study, while 10 reported that they were motivated to examine the impact that a difference in geographic or temporal context might have on the results.
+Respondents emphasizing external validation provided motivations statements like,``Testing of conceptual claims on a specific governance context (post-conflict areas) that motivated me to examine other post-conflict areas to examine replicability of results." or ``I didn't think the claim was likely to replicate, and already had relevant data that could be used to test the hypothesis in question."
+Those motivated by differences in context discussed motivations such as, ``We needed compare between Mexico, Honduras and the U.S." and ``To capture seasonal nuance from samples only collected during summer in other studies."
 A total of 16 respondents also identified replication as a fundamental part of knowledge creation and evaluation. 
-For example, \textcolor{red}{PULL ONE EXAMPLE FROM Q19}.
+For example, one respondent directly linked the motivation to replicate to the desire to construct theory, ``To build theory.
+To add strength to criticisms of other theory based on so-called case studies".
 
-In the majority of the attempted replications, respondents reported that they were able to recreate at least some of the results of the study they were investigating and form conclusions that matched those of the original study from those results.
-55 respondents (62\%) reported being able to exactly replicate some of the results of a prior study. 
+While few respondents were able to replicate all results, the majority respondents reported that they were able to recreate at least some of the results of the study they were investigating. 
+55 respondents (65\%) reported being able to exactly replicate some of the results of a prior study. 
 However, only six respondents (7\%) reported that they were able to exactly replicate all results.
 The survey results were similar when we asked respondents whether they were able to partially replicate the results of a study --- finding a different result, but ultimately coming to a similar conclusion as the prior study.
-62 respondents (73\%) reported being able to partially replicate at least some of the results of a study, while 14 respondents (16\%) reported being able to partially replicate all results.
+62 respondents (74\%) reported being able to partially replicate at least some of the results of a study, while 14 respondents (17\%) reported being able to partially replicate all results.
 
 Respondents reported a limited ability to access the data, code, and procedures used in the studies they were attempting to replicate. 
-Respondents were generally able to access some (51\%) or all (31\%) of the data used in a prior study, but were slightly less successful at accessing some (42\%) or all (28\%) of the code and procedural information.
+Respondents were generally able to access some (51\%) or all (31\%) of the data used in a prior study, but were slightly less successful at accessing some (43\%) or all (29\%) of the code and procedural information.
 Moreover, being able to access these materials and information did not mean that researcher could fully understand or directly replicate how a study was conducted.
@@
 Ultimately 58 respondents that attempted replications (69\%) reported publishing some or all of their findings.
-23 respondents were able to publish all of the findings of their replication study, while another 36 respondents were able publish at lest some of their findings.
-48 Respondents that either did not attempt to publish their findings, or were only able to publish a portion of their findings, reported why they chose not to attempt publication. 
+23 respondents were able to publish all of the findings of their replication study, while another 35 respondents were able publish at lest some of their findings.
+48 respondents that either did not attempt to publish their findings, or were only able to publish a portion of their findings, reported why they chose not to attempt publication. 
 27 respondents replied that replications were still ongoing or that it would simply take too much time to pursue publication. 
 Many other respondents said that they believe it would either be to difficult to publish their replication study because replications were not valued in the academic literature.
-For example researchers pointed out that, "no one seems to care", their results received "no interest from journals", and that "incentives in academia clearly point towards publishing original research."
-In one instance, "The journal that published the original paper specifically claimed to be interested in replications, but then desk rejected our replication."
-This reasoning reflects different form of non-response and selection bias at the root of the 'file drawer problem' in academic literature (CITE - Rosenthal 1979). 
+For example researchers pointed out that,``no one seems to care", their results received ``no interest from journals", and that ``incentives in academia clearly point towards publishing original research."
+In one instance,``The journal that published the original paper specifically claimed to be interested in replications, but then desk rejected our replication."
+This reasoning reflects different form of non-response and selection bias at the root of the `file drawer problem' in academic literature \citep{rosenthal1979}. 
 The file drawer problem exists when the outcome of a study influence the decision to publish or share that finding.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Discussion and conclusion}
+\section*{Discussion and Conclusion}
 The results of our survey suggest geographic researchers are familiar with replication and believe that replication studies can serve several epistemological functions.
@@
 Researcher definitions instead focused on criteria used to identify a study as a replication. 
-This same focus on criteria can be observed in the wider R\&R literature, where authors typically broadly gesture to the epistemological function of replication then quickly turn to the accounting of data and code sharing practices.
-This tendency toward criteria suggests that replication as an epistemological tool may not be at the forefront of geographic researchers' thinking about replication.
+This same focus on criteria can be observed in the wider R\&R literature, where authors typically gesture to the epistemological function of replication then quickly turn to the accounting of data and code sharing practices.
+This tendency toward criteria may suggest that replication as an epistemological tool is not be at the forefront of geographic researchers' thinking about replication.
+While this finding aligns with the observable focus on computational forms of reproducibility in the geographic literature, further data is needed to support this conclusion because it may simply be the case that respondents could not provide sufficient definitional nuance in a survey text response.
 
@@
 
-The results of our survey suggest that collectively researchers are uncertain whether it is valuable to replicate recent geographic research. 
+The results of our survey also suggest that collectively researchers are uncertain whether it is valuable to replicate recent geographic research. 
 Our results do indicate that it is unlikely that this uncertainty stems from a lack of belief in the potential epistemological value of replication studies.
@@
 
-Disciplinary variation
-\begin{itemize}
-    \item Overall, the differences we observed across sub-groups was small, but should be interpreted with caution given the sub-group sample sizes.
-    \item We also found that human geographers and qualitative researchers were disproportionately likely to provide 'I do not know' responses across questions, which further decreases the amount of information available about their views and beliefs.
-\end{itemize}
+Building on the differences that exist between research traditions in geography, it may be fruitful to further examine how researcher working in different subfield precieve and use replication in the work.
+Overall, the differences in responses we observed across subfields and methodological approaches was small, but this finding should be interpreted with caution given sizes of our subfield samples.
+However, it is sensible that responses to questions about barriers to replicability and motivations to attempt replications would be similar between groups because researchers across the discipline work in similar academic incentive systems.
+One notable exception to this consistency was our finding that human geographers and qualitative researchers were disproportionately likely to provide 'I do not know' responses across survey questions and to question the epistemological role of replication in their subfield.
 
 %%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Limitations} 
+\subsection*{Limitations and Future Research} 
 Survey research has several common limitations which we attempted to mitigate through the design of our study. 
@@
 We attempted to quantify potential self-selection by calculating and comparing survey completion rates across subfields and approaches. 
-Completion rates for all subfields were between 84 and 87 percent, except slightly higher rates for geographic methods and GIS researchers (96.8\%).
-Completion rates were 84.2 percent for mixed methods, 87.0 percent for qualitative methods, and 91.1 percent for quantitative methods. 
+Completion rates for all subfields were between 69 and 78 percent with slightly lower rates for geographic methods and GIS researchers (69.0\%) and physical geographers (70.6\%).
+Completion rates were 76.6 percent for mixed methods, 70.8 percent for qualitative methods, and 71.7 percent for quantitative methods. 
 These values suggest that self-selection was not a significant issue.
@@
 Finally, our survey provides a description of the perspectives of geographic researchers at one point in time and one depth of understanding.
-As the first survey of its kind, our work provides an initial measurement of geographers definitions of replicability, beliefs about what factors affects the chances
-or replicating a study, motivations to attempt replication studies, and experiences
-conducting replications. 
+Our work provides an initial measurement of geographers definitions of replicability, beliefs about what factors affects the chances of replicating a study, motivations to attempt replication studies, and experiences conducting replications.
 However, in many cases we were not able to probe more deeply into the nuances of these measurements and the conceptualization that underlie them.
@@
     \centering
-    \includegraphics[scale=0.80]{results/figures/Fig4-Q15-Decisions.png}
+    \includegraphics[scale=0.8]{results/figures/Fig4-Q15-Decisions.png}
     \caption{Factors Affecting Researcher Decisions to Undertake Replication Studies.
-Factors grouped by: Academic Incentives (AA), Artifact Accessibility (AA), Study Characteristics (SC); and the percentage `don't know' (DK) and missing (M) responses.}
+Factors grouped by: Academic Incentives (AI), Artifact Accessibility (AA), Study Characteristics (SC); and the percentage `don't know' (DK) and missing (M) responses.}
     \label{fig:Q15-DecisionFactors}

### 2024-01-19 docs/manuscript/manuscript.tex
Updates from Overleaf

@@
 \section*{Introduction}
-Attempting to replicate a study is a means of critically assessing whether the evidence provided by the researchers that conducted the study support the claims they make and their explanation of a phenomenon.
-Replications confront existing explanations with new evidence by retesting prior claims using new data, while typically controlling for procedural differences by conducting similar analyses.
-Replications can be designed to serve epistemic functions and to test several forms of validity.
-Attempts to reproduce prior research also retest claims, but do so using the same data and the same, or very similar, analyses. 
-The central focus a reproduction attempt is the verification of claims through the examination of how a study was conducted and whether the design and execution of that study support the results presented.
-While the results of a reproduction or replication do not provide conclusive evidence for or against a claim, those that produce outcomes consistent with prior studies typically increase confidence in a claim and the theories underlying it \citep{earp2015, nichols2021}.
-When prior results cannot be recreated, the claims of the prior study, the data and methods used, and the current understanding of the phenomena may be brought into question \citep{christensen2019, NASEM2019}.
+Replications confront existing explanations with new evidence by retesting prior claims using new data, while controlling for procedural differences by conducting similar analyses.
+Replications can be designed to serve different epistemic functions and to test several forms of validity.
+Attempts to reproduce prior research may also test the validity of a study, but do so using the same data and the same, or very similar, analyses. 
+Contrasted with a replication attempt, the central focus of a reproduction attempt is the verification of claims through the examination of how a study was conducted and whether the design and execution of that study support the results presented.
+While the results of a reproduction or replication do not provide conclusive evidence for or against a claim, those that produce outcomes consistent with prior studies typically increase confidence in a claim and the theories it is based on \citep{earp2015, nichols2021}.
+When prior results cannot be recreated, there is reason to question the data and methods used by the prior study, the claims made by the prior study, and perhaps even the current theoretical understanding of the geographic phenomena \citep{christensen2019, NASEM2019}.
 
@@
 The majority of recent research in the geographic literature on the subject has focused on reproduction over replication, and has emphasized the computational reproducibility of geographic research ahead of other dimensions.
-For example, an ongoing reproducibility initiative supported by the Association of Geographic Information Laboratories in Europe annually attempts to reproduce the computational results of submissions to their annual meeting and reports on the accessibility of related data, code, and computational environment \citep{nust2018, ostermann2021}.
+For example, an ongoing reproducibility initiative supported by the Association of Geographic Information Laboratories in Europe attempts to reproduce the computational results of submissions to their annual meeting and reports on the accessibility of related data, code, and computational environment \citep{nust2018, ostermann2021}.
 A series of reproduction studies led by Kedron and Holler \citep{Kedron2023Beyond, Kedron_Holler_Bardin_Hilgendorf_2022} advance this stream of work by introducing selected variations into the reproduction process to test the sensitivity of results to conceptual and methodological perturbations.
-However, those studies also largely focus on testing the conclusion and internal validity of past studies through computational reproduction.
+However, those studies also largely focus on testing the conclusion validity of past studies through computational reproduction.
 
@@
 Place to place variation in phenomena, and the processes that produce them, are one of the defining features of geographic research and a central tenant of many of its research traditions.
-With those intellectual foundations, it remains unclear how current geographic researchers view replication and the role of the practice in the knowledge accumulation process.
+With these intellectual foundations, it remains unclear how current geographic researchers view replication and the role of the practice in the knowledge accumulation process.
 There is similarly limited empirical evidence available about the factors that motivate or discourage geographic researchers from pursuing replications.
@@
 We are aware of only a handful of similar published surveys within the geographic literature \citep{balz2020reproducibility, konkol2019, ostermann2017, kedron2023survey}.
-However, these surveys typically focus on the quantitative and computational intensive forms of geographic research, primarily assess the availablity of research artifacts (e.g., data and code), and address reproducibility, whether the same results can be created using the same data and methods, rather than replicability.
+However, these surveys typically focus on the quantitative and computational intensive forms of geographic research, primarily assess the availablity of research artifacts (e.g., data and code), and address reproducibility rather than replicability.
 In all but one instance, these surveys also rely on convenience samples drawn from specialist conferences or non-representative subsets of the geographic research community. 
 In contrast, to support generalization, we designed a sampling frame to capture researchers from across disciplinary subfields and methodological approaches, and draw survey participants from that frame using a probability sampling scheme.
-In the remainder of this paper, we detail the design of our survey, sampling strategy, and analytical approach before presenting the results of our survey. 
-We then discuss the implications and limitations of our work.
+
+In the remainder of this paper, we first briefly present the epistemic roles of replication in the context of geographic research.
+We then detail the design of our survey, sampling strategy, and analytical approach before presenting our results. 
+We conclude with a discussion of the implications and limitations of our work.
 
@@
 \section*{Replication and the Evaluation of Prior Claims}
-Broadly defined, a replication study is any study that has at least one outcome that would be considered diagnostic evidence of a claim from prior research, and can be used to assess the validity of prior claims \citep{nosek2020}.
-More narrowly, replication studies are differentiated by the alterations they make to a study, which is linked to the epistemological function they are intended to serve.
-By altering different aspects of a study a researcher attempting a replication can use their finding to potentially assess (1) conclusion, (2) internal, (3) construct, and (4) external validity \citep[see][]{schmidt2009, gomez2010replications, radder2003, radder2012}.
+Replications structure the iterative development of theory by confronting claims with new evidence.
+Broadly defined, a replication is any study that has at least one outcome that would be considered diagnostic evidence of the validity of a claim made in prior research \citep{nosek2020}.
+No single study provides evidence about all of the conditions that could affect a claim because individual studies are performed by particular researchers using particular methods to draw and analyze data from particular settings.
+Until tested, whether a claim is expected to hold under new conditions is either a product of the theory used to structure the original investigation, or a speculative assumption of generalizability.
+Replications empirically test the validity and reliability of the claims made in a study by selectively altering different aspects of the initial work and repeating the study \citep{schmidt2009, gomez2010replications, radder2003, radder2012}.
+By altering different aspects of a study across a series of replications, researchers can collectively and progressively test claims across a widening set of conditions and use that information to revise theory.
 
-OLD: Replications provide evidence of the credibility of claims across conditions that either naturally or are purposefully manipulated to differ from the original study.
+The type of check a replication provides depends on which aspects of a study are changed and in what combination. 
+Researchers pursuing a replication will collect new data, but will also change the materials and procedures used in the replication, the measurement of variables, the location of the replication, and/or the population being studied \citep{hendrick1990, schmidt2009, gomez2010replications}.
+Replication studies are often classified either direct or conceptual based on which of these aspects a research is changing and the epistemological objective they are pursuing \citep[see][]{sargent1981repeatability, schmidt2009, plesser2018reproducibility}.
+
+Direct replications make limited changes to an initial study in order to verify the claims of the study by testing for conclusion, construct, and internal validity. 
+If a researcher attempting a replication keeps all aspects of a study the same, but collects new data, the replication is designed to assess conclusion validity.
+As long as the population being studied remains stable between the two studies, the replication will control for sampling error and will provide evidence as to whether the prior results were the product of chance variation.
+Alternatively, a researcher can use a replication to test construct validity, if they change how a key construct is measured and also hold all other aspects of a study constant. 
+Consistently observing a relationship across well-established measures of a concept or phenomenon may raise researcher confidence that the operationalization used in the original study did not bias the result, or affect the claims made.
+Finally, when the materials and procedures (e.g., data collection device, analyses) used in a replication differ from an initial study, the replication assesses the whether these factors affected the original results testing the internal validity of the prior work.
+
+In conceptual replications changes are made to the population or location being studied to test external validity and whether the claims made in a study generalize to new populations and contexts. 
+In geographic research, a conceptual replication could for example involve changing the location of a study from one city to another, or one ecosystem to another. 
+Alternatively, a researcher could could conduct a conceptual replication of a study by examining the same location after a migration event is through to have changed the population of that area. 
+Conceptual replications provide evidence that can be used to assess the hypotheses and theories that underlie a prior study in new situations \citep{schmidt2009}.
+However, conceptual replications do not necessarily provide evidence that can be used to adjust confidence in a claim made in an initial study \citep{nosek2020}.
+For example, it is not necessarily the case that observing evidence in a one location that contradicts a claim made in study of another location would cause a researcher to reduce their confidence in that initial claim.
+
+As tests of generalizability and external validity, conceptual replications play an important role in the development of theory \citep{earp2015}.
+When a theory is early in its development, it is often unclear whether a researcher should expect the predictions of that theory to hold in new populations, spaces, and times.
+This is the case because new theories commonly lack a well developed set of conditional statements identifying for whom, where, and/or when their explanations and predictions should hold. 
+Without these statements, it remains possible that the predictions of the theory will generalize across a large set of contexts. 
+In other words, a lack of evidence causes uncertainty about the explanatory range of the theory.
+In this situation, conceptual replications act as empirical tests of the generalizability of a theory to new contexts. 
+Conceptual replications provide evidence to inform the addition and revision of conditional statements that identify for whom, where, and /or when the theory is expected to provide meaningful predictions.
+As the conditions required for a claim to replicate are incorporated into the theory, the theory matures and the situations in which the prediction of the theory are expected to hold becomes clear.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{The Replicability of Geographic Research}
+Geographers have arguably never formally and explicitly held an extended discussion of the role of replication in the discipline.
+However, replication is implicitly at the center of the discipline's nomothetic-ideographic debate \citep{kedron2022replication, sui2021reproducibility} and ongoing discussions about how to construct explanations of the physical and human processes that shape the world \citep[see][]{inkpen2013science, harvey1969, miller2015data, sayer1992method, yeung2019rethinking, yeung2023theory}.
+Within this literature, discussions of replication typically pivot on the expected variability of processes across locations, whether replications can inform theory development and, as a practical matter, the ability to control factors that may affect the outcome of a study.
+
+The first point raised in most discussions of replication in geography is that places are unavoidably different from one another \citep[see][]{goodchild2021Annals, goodchild2022reproducibility, Wainwright2021}.
+Researchers involved in these discussions often invoke \cite{anselin1989special} second law of geography which notes that geographic features exhibit uncontrolled variability over space implying that observable differences between places, and perhaps an inability to replicate prior findings, should be expected across locations.
+Geographic variation essentially poses an identification problem for those interpreting the results of a replication because it is not clear whether the same research outcome (e.g., parameter estimates) observed in different location is or is not determined by the same processes.
+In some instances, commentary about differences between locations are extended to point out the uniqueness of places and mixed with discussions of role of researcher position and perspective in the research process \citep{Peet1999, simandan2019revisiting}.
+Discussions of replication developed from this perspective often suggest that the role replication can play in geography is limited because research is an interpretive process dependent on the unique perspective of a researcher who is analyzing data drawn from different or unique places \citep{Wainwright2021}.
+
+Arguments about geographic variation can be pushed further and linked the principle of flux \citep{marcovich1967} which, applied to locations, alternatively argues that phenomena studied in space cannot be encountered twice, or that places are defined not by the stability of their features but by their continual renewal through processes that create change in those same features.
+The two alternative readings of this principle have very different implications for the prospect of replicating geographic research.
+Under the first simpler reading, change is constant and a researcher should not expect to find the same arrangement of features in different locations, or even to encounter the same arrangement of features at different times in the same location.
+In this situation, an inability replicate a finding would not be surprising and explanations would be localized. 
+Under the second reading, geographic features are continually changing but structured by processes that may, or may not, be consistent across time and space. 
+In this situation, findings may be expected to replicate and attempting replications can give insight into the stability of processes across locations.
+
+Understanding places as defined by process that potentially differ across locations aligns with the argument that geography is well-suited to the development of empirically grounded middle-range theory \citep{miller2015data}.
+The aim of middle-range theory is not to develop overarching explanations or essential features of processes, but rather to offer provisional explanations of identifiable phenomena which can be tested and used to slowly develop more general but bounded explanations \citep{merton1968social}.
+As \cite{harvey1969} notes, geographers often elaborate the theories of other disciplines by linking them with spatial explanations of form and process.
+\cite{turner1989, turner2002} argues this synthesis approach gives geography the capability to generate and refine the text of theories and establish their spatial domain by examining phenomena empirically within a web of complex processes that interact within and between locations.
+In this way, replications can give insight into when, where, and why a explanation does not hold \citep{zhang_wolf_2023}.
+Similarly, \cite{sayer1992method} distinguishes between intensive research in which synthesis is used to identify how processes work in a particular case of location, and extensive research in which synthesis extends across cases or locations to identify how widely a process holds.
+In intensive research, replication attempts that change the data collected from a location can be used to corroborate the explanation of a process.
+In extensive research, replication data is gathered from new context to establish the coverage of an explanation. 
+In either case, that accumulation of empirical evidence through replication can be used to refine and adjust theory.
+
+Finally, discussions of replication in the literature also frequently point out that many of the phenomena geographers study not only vary across locations, but are difficult or impossible to control \citep[see][]{sayer1992method, kedron2021GA, waters2021motivations}.
+In practice, geographers often lack the ability to control where data is collected, which populations are included or excluded in a study, how variables are measured, and the materials and procedures used when attempting a replication.
+This lack of control makes it difficult to execute replications that isolate the influence of any particular factor, which makes it unclear what lessons should be learned from a replication attempt and what epistemological function that attempt may be serving.
+Moreover, it is also often unclear which factors should be accounted for when studying a particular location.
+As \cite{goodchild2021replication} suggest, even when some level of control can be exerted on a process, it will remain difficult to exclude the variable effects of context from studies that are incompletely identified in the presence of spatially heterogeneity.
+While these factors make replication practically challenging in some forms of geographic research, they do not themselves eliminate the potential usefulness of the practice in selected cases.
+
+Geography as a discipline is presently defined by its topical, epistemological, and methodological diversity. 
+While replication has been an implicit part of many discussions of the development of knowledge in the discipline, how exactly the practice is understood and applied by researchers within those different traditions remains unclear.
+Moreover, to date there has been no empirical measure of how often researchers across the discipline attempt to replicate research, what motivates them to pursue or not pursue replications, and how they would interpret the findings of such studies.
+In fact, we expect that many geographic researcher would disagree with the conception and presentation of replication presented above. 
+However, until researcher conceptions and practices of replication are measured conversations about the role of replication in the discipline can only progress so far.
 
@@
 Researcher definitions instead focused on criteria used to identify a study as a replication. 
+Indeed, many of these definitions closely aligned with the definition of reproducibility, which mirrors  \cite{kedron2023survey} findings that researchers appear to often conflate these two terms. 
 This same focus on criteria can be observed in the wider R\&R literature, where authors typically gesture to the epistemological function of replication then quickly turn to the accounting of data and code sharing practices.
-This tendency toward criteria may suggest that replication as an epistemological tool is not be at the forefront of geographic researchers' thinking about replication.
+This tendency toward criteria may suggest that replication as an epistemological tool is not at the forefront of geographic researchers' thinking about replication.
 While this finding aligns with the observable focus on computational forms of reproducibility in the geographic literature, further data is needed to support this conclusion because it may simply be the case that respondents could not provide sufficient definitional nuance in a survey text response.
@@
 It also remains unclear if or how geographic researchers map variations between an original study and its replication to the epistemological functions that replication study is intended to serve.
-A clear understanding of this connection between variations and functions is essential because which aspects of a study are changed controls the form of validity being assessed \citep{gomez2010replications, radder2003, schmidt2009}.
+A clear understanding of the connection between variations and functions is essential because which aspects of a study are changed controls the form of validity being assessed \citep{gomez2010replications, radder2003, schmidt2009}.
 Poor documentation and articulation of these connections in replication studies of geographic research could lead to the misinterpretation of the results of an individual replication, and could misdirect the collective assessment of a claim across a set of replication studies.
@@
 
-Building on the differences that exist between research traditions in geography, it may be fruitful to further examine how researcher working in different subfield precieve and use replication in the work.
-Overall, the differences in responses we observed across subfields and methodological approaches was small, but this finding should be interpreted with caution given sizes of our subfield samples.
-However, it is sensible that responses to questions about barriers to replicability and motivations to attempt replications would be similar between groups because researchers across the discipline work in similar academic incentive systems.
-One notable exception to this consistency was our finding that human geographers and qualitative researchers were disproportionately likely to provide 'I do not know' responses across survey questions and to question the epistemological role of replication in their subfield.
+Finally, building on the differences that exist between research traditions in geography, it may be fruitful to further examine how researchers working in different subfields perceive and use replication in their work.
+Overall, the differences in responses we observed across subfields and methodological approaches was small, but this finding should be interpreted with caution given the sizes of our subfield samples.
+It is sensible that responses to questions about barriers to replicability and motivations to attempt replications would be similar across subfields because researchers across the discipline work in similar academic incentive systems.
+Alternatively, there are substantial differences in the concepts and methods used in different subfields, in the types of questions researchers ask, and the phenomena and systems they study. 
+It seems natural that this variation in practice would translate into the use and implementation of replications. 
+However, the limited size of the sample of researchers that reported actually attempting replications did not allow for an extensive analysis of this questions by subfield. 
+Perhaps an initial indicator of these differences is our finding that human geographers and qualitative researchers were disproportionately likely to provide 'I do not know' responses across survey questions and to question the epistemological role of replication in their subfield.
 
@@
 Ideally, we would stratify our potential respondents into meaningful subgroups, randomly draw participants from these subgroups, and use a post-stratification procedure to address any imbalance in our response.
-However, we could not follow this approach because stratification require knowledge of the population characteristics that predicts differences in response and a population wide census of those key predictors.
+However, we could not follow this approach because stratification requires knowledge of the population characteristics that predicts differences in response and a population wide census of those key predictors.
 We did not have access to this information because we presently lack a comprehensive understanding of replicability in geography and no list of geographic researchers complete with relevant predictor information exists.
@@
 Geographic researchers that have only published outside geographically indexed journals would not be captured in our sampling frame which would create exclusion errors. 
-However, we believe the number of individuals falling into this category will be small as most active geographic researchers are likely to have published at least one study in the journals meeting our inclusion criteria.
+We believe the number of individuals falling into this category will be small as most active geographic researchers are likely to have published at least one study in the journals meeting our inclusion criteria.
 
@@
 Finally, our survey provides a description of the perspectives of geographic researchers at one point in time and one depth of understanding.
-Our work provides an initial measurement of geographers definitions of replicability, beliefs about what factors affects the chances of replicating a study, motivations to attempt replication studies, and experiences conducting replications.
+This work offers an initial measurement of geographers definitions of replicability, beliefs about what factors affects the chances of replicating a study, motivations to attempt replication studies, and experiences conducting replications.
 However, in many cases we were not able to probe more deeply into the nuances of these measurements and the conceptualization that underlie them.
@@
 Future research using in-depth interviews or multi-analyst study designs could probe these question more deeply. 
-It would also be useful to track the information collected in this survey over time and to link that tracking to specific topics. 
+It would also be useful to track the information collected in this survey over time and to link that tracking to specific research topics. 
 For example, understanding how researcher perspectives on the epistemological function of replication shift in climate change impacts research may be a useful indicator of how well researchers in that field are developing theories and methodologies capable of dealing with increasing variation and shifting baselines induced by climate change.

### 2024-02-01 docs/manuscript/manuscript.tex
Updates from Overleaf

@@
 \section*{Introduction}
-Replications confront existing explanations with new evidence by retesting prior claims using new data, while controlling for procedural differences by conducting similar analyses.
+Replications confront existing explanations with new evidence by retesting prior claims using new data and similar research procedures.
 Replications can be designed to serve different epistemic functions and to test several forms of validity.
@@
 More often the literature on the replication of geographic research turns to the question of if and when it is reasonable to expect the findings and claims of a prior study to replicate \citep{kedron2021GA, kedron2022replication, goodchild2021replication, sui2021reproducibility}.
-Place to place variation in phenomena, and the processes that produce them, are one of the defining features of geographic research and a central tenant of many of its research traditions.
-With these intellectual foundations, it remains unclear how current geographic researchers view replication and the role of the practice in the knowledge accumulation process.
+Place-to-place variations in phenomena, and the processes that produce those variations, are one of the defining features of geographic research and a central tenet of many of its research traditions.
+With these intellectual foundations, it remains unclear how current geographic researchers view replication and its role of in the knowledge accumulation process.
 There is similarly limited empirical evidence available about the factors that motivate or discourage geographic researchers from pursuing replications.
@@
 We are aware of only a handful of similar published surveys within the geographic literature \citep{balz2020reproducibility, konkol2019, ostermann2017, kedron2023survey}.
-However, these surveys typically focus on the quantitative and computational intensive forms of geographic research, primarily assess the availablity of research artifacts (e.g., data and code), and address reproducibility rather than replicability.
+However, these surveys typically focus on the quantitative and computational intensive forms of geographic research, primarily assess the availability of research artifacts (e.g., data and code), and address reproducibility rather than replicability.
 In all but one instance, these surveys also rely on convenience samples drawn from specialist conferences or non-representative subsets of the geographic research community. 
@@
 No single study provides evidence about all of the conditions that could affect a claim because individual studies are performed by particular researchers using particular methods to draw and analyze data from particular settings.
-Until tested, whether a claim is expected to hold under new conditions is either a product of the theory used to structure the original investigation, or a speculative assumption of generalizability.
+Until a claim is tested through replication, our expectation of whether it will hold under new conditions relies on the theory used to structure the original investigation, or on a speculative assumption of generalizability.
 Replications empirically test the validity and reliability of the claims made in a study by selectively altering different aspects of the initial work and repeating the study \citep{schmidt2009, gomez2010replications, radder2003, radder2012}.
@@
 Researchers pursuing a replication will collect new data, but will also change the materials and procedures used in the replication, the measurement of variables, the location of the replication, and/or the population being studied \citep{hendrick1990, schmidt2009, gomez2010replications}.
-Replication studies are often classified either direct or conceptual based on which of these aspects a research is changing and the epistemological objective they are pursuing \citep[see][]{sargent1981repeatability, schmidt2009, plesser2018reproducibility}.
+Replication studies are often classified as either direct or conceptual based on which of these aspects a research is changing and the epistemological objective they are pursuing \citep[see][]{sargent1981repeatability, schmidt2009, plesser2018reproducibility}.
 
 Direct replications make limited changes to an initial study in order to verify the claims of the study by testing for conclusion, construct, and internal validity. 
-If a researcher attempting a replication keeps all aspects of a study the same, but collects new data, the replication is designed to assess conclusion validity.
+If a researcher attempting a replication keeps all aspects of a study the same, but collects new data, then the replication is designed to assess conclusion validity.
 As long as the population being studied remains stable between the two studies, the replication will control for sampling error and will provide evidence as to whether the prior results were the product of chance variation.
-Alternatively, a researcher can use a replication to test construct validity, if they change how a key construct is measured and also hold all other aspects of a study constant. 
+Alternatively, if a researcher changes how a key construct is measured and also holds all other aspects of a study constant, then the replication can test construct validity.
 Consistently observing a relationship across well-established measures of a concept or phenomenon may raise researcher confidence that the operationalization used in the original study did not bias the result, or affect the claims made.
-Finally, when the materials and procedures (e.g., data collection device, analyses) used in a replication differ from an initial study, the replication assesses the whether these factors affected the original results testing the internal validity of the prior work.
+Finally, if the materials and procedures (e.g., data collection device, analyses) used in a replication differ from a prior study, then the replication assesses whether these factors affected the original results, thereby testing the internal validity of the prior work.
 
-In conceptual replications changes are made to the population or location being studied to test external validity and whether the claims made in a study generalize to new populations and contexts. 
-In geographic research, a conceptual replication could for example involve changing the location of a study from one city to another, or one ecosystem to another. 
-Alternatively, a researcher could could conduct a conceptual replication of a study by examining the same location after a migration event is through to have changed the population of that area. 
+In conceptual replications, changes are made to the population or location being studied in order to test external validity and whether the claims made in a study generalize to new populations and contexts.
+In geographic research, a conceptual replication could involve changing the location of a study from one city to another, or from one ecosystem to another. 
+Alternatively, a researcher could could conduct a conceptual replication of a study by examining the same location after migration is thought to have changed the population of that area. 
 Conceptual replications provide evidence that can be used to assess the hypotheses and theories that underlie a prior study in new situations \citep{schmidt2009}.
 However, conceptual replications do not necessarily provide evidence that can be used to adjust confidence in a claim made in an initial study \citep{nosek2020}.
-For example, it is not necessarily the case that observing evidence in a one location that contradicts a claim made in study of another location would cause a researcher to reduce their confidence in that initial claim.
+For example, it is not necessarily the case that observing evidence in one location that contradicts a claim made in a prior study of another location would cause a researcher to reduce their confidence in the prior claim.
 
-As tests of generalizability and external validity, conceptual replications play an important role in the development of theory \citep{earp2015}.
+As tests of generalizability and external validity, conceptual replications play an important role in the development of theory \citep{earp2015, haig2022, irvine2021}.
 When a theory is early in its development, it is often unclear whether a researcher should expect the predictions of that theory to hold in new populations, spaces, and times.
@@
 Geographers have arguably never formally and explicitly held an extended discussion of the role of replication in the discipline.
-However, replication is implicitly at the center of the discipline's nomothetic-ideographic debate \citep{kedron2022replication, sui2021reproducibility} and ongoing discussions about how to construct explanations of the physical and human processes that shape the world \citep[see][]{inkpen2013science, harvey1969, miller2015data, sayer1992method, yeung2019rethinking, yeung2023theory}.
+However, replication is implicitly at the center of the discipline's nomothetic-ideographic debate \citep{kedron2022replication, sui2021reproducibility} and ongoing discussions about how to construct explanations of the physical and human processes that shape the world \citep[see][]{harvey1969, inkpen2013science, miller2015data, sayer1992method, yeung2019rethinking, yeung2023theory}.
 Within this literature, discussions of replication typically pivot on the expected variability of processes across locations, whether replications can inform theory development and, as a practical matter, the ability to control factors that may affect the outcome of a study.
@@
 The first point raised in most discussions of replication in geography is that places are unavoidably different from one another \citep[see][]{goodchild2021Annals, goodchild2022reproducibility, Wainwright2021}.
-Researchers involved in these discussions often invoke \cite{anselin1989special} second law of geography which notes that geographic features exhibit uncontrolled variability over space implying that observable differences between places, and perhaps an inability to replicate prior findings, should be expected across locations.
-Geographic variation essentially poses an identification problem for those interpreting the results of a replication because it is not clear whether the same research outcome (e.g., parameter estimates) observed in different location is or is not determined by the same processes.
-In some instances, commentary about differences between locations are extended to point out the uniqueness of places and mixed with discussions of role of researcher position and perspective in the research process \citep{Peet1999, simandan2019revisiting}.
+Researchers involved in these discussions often invoke \cite{anselin1989special} second law of geography which notes that geographic features exhibit uncontrolled variability over space. 
+This principle implies that researchers can expect to observe differences between places, and that perhaps they should expect an inability to replicate prior findings from one place in another.
+Geographic variation essentially poses an identification problem for those interpreting the results of a replication because it is not clear whether the same research outcome (e.g., parameter estimates) observed in different locations is or is not determined by the same processes.
+In some instances, commentary about differences between places are combined  with discussions of role of researcher position and perspective in the research process \citep{Peet1999, simandan2019revisiting}.
 Discussions of replication developed from this perspective often suggest that the role replication can play in geography is limited because research is an interpretive process dependent on the unique perspective of a researcher who is analyzing data drawn from different or unique places \citep{Wainwright2021}.
 
-Arguments about geographic variation can be pushed further and linked the principle of flux \citep{marcovich1967} which, applied to locations, alternatively argues that phenomena studied in space cannot be encountered twice, or that places are defined not by the stability of their features but by their continual renewal through processes that create change in those same features.
+Arguments about geographic variation can be pushed further and linked the principle of flux \citep{marcovich1967}, which, alternatively argues on one hand that phenomena studied in a place cannot be encountered twice, or on the other hand that places are defined not by the stability of their features but by their continual renewal through processes that create change in those same features.
 The two alternative readings of this principle have very different implications for the prospect of replicating geographic research.
-Under the first simpler reading, change is constant and a researcher should not expect to find the same arrangement of features in different locations, or even to encounter the same arrangement of features at different times in the same location.
+Under the first simpler reading, change is constant and a researcher should not expect to find the same arrangement of features at different times in the same location.
 In this situation, an inability replicate a finding would not be surprising and explanations would be localized. 
 Under the second reading, geographic features are continually changing but structured by processes that may, or may not, be consistent across time and space. 
-In this situation, findings may be expected to replicate and attempting replications can give insight into the stability of processes across locations.
+In this situation, findings may be expected to replicate within a range of uncertainty, and attempting replications can give insight into the stability of processes across locations.
 
-Understanding places as defined by process that potentially differ across locations aligns with the argument that geography is well-suited to the development of empirically grounded middle-range theory \citep{miller2015data}.
+Understanding places as defined by processes that potentially differ across locations aligns with the argument that geography is well-suited to the development of empirically grounded middle-range theory \citep{miller2015data}.
 The aim of middle-range theory is not to develop overarching explanations or essential features of processes, but rather to offer provisional explanations of identifiable phenomena which can be tested and used to slowly develop more general but bounded explanations \citep{merton1968social}.
@@
 Geography as a discipline is presently defined by its topical, epistemological, and methodological diversity. 
-While replication has been an implicit part of many discussions of the development of knowledge in the discipline, how exactly the practice is understood and applied by researchers within those different traditions remains unclear.
+While replication has been an implicit part of many discussions of the development of knowledge in the discipline, it remains unclear exactly how the practice is understood and applied by researchers within those different traditions.
 Moreover, to date there has been no empirical measure of how often researchers across the discipline attempt to replicate research, what motivates them to pursue or not pursue replications, and how they would interpret the findings of such studies.
-In fact, we expect that many geographic researcher would disagree with the conception and presentation of replication presented above. 
-However, until researcher conceptions and practices of replication are measured conversations about the role of replication in the discipline can only progress so far.
+In fact, we expect that many geographic researchers would disagree with the conception and presentation of replication presented above. 
+However, until researcher conceptions and practices of replication are systematically assessed, conversations about the role of replication in the discipline can only progress so far.
 
@@
 All of the results presented in this paper can be independently reproduced using the materials in that repository.
-Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_RPl_Survey_PAP} - \url{https://osf.io/a4nwg}). 
+Before the start of data collection, we preregistered an analysis plan for the survey with OSF Registries (\citet{Kedron_RPl_Survey_PAP} - \url{https://osf.io/a4nwg}). 
 The survey was conducted under the approval and supervision of the Arizona State Institutional Review Board - \textit{STUDY00014232}.
@@
 \subsection*{Researcher Definitions of Replication and its Epistemic Functions}
-Geographic researchers are thinking about replicability and link the act of replicating a study to a number of different epistemological functions (Figure \ref{fig:Q7-Epistemology}). 
+Geographic researchers are thinking about replicability and link the act of replicating a study to a number of different epistemological functions. 
 A majority of respondents reported thinking about replicability (74\%), talking with colleagues about replicability (65\%), and considering replicability when undertaking peer-review (59\%) during the past two years.
-In particular, respondents believe that replication studies can be used to assess the construct validity (75\%) and external validity of a prior study.
-Specifically, respondents believe that replication studies can assess whether the claims of that study will hold in new locations (67\%) or new populations (63\%). 
+Specifically, respondents believe that replication studies can assess whether the claims of that study will hold in new locations (67\%) or new populations (63\%) (Figure \ref{fig:Q7-Epistemology}).
+Respondents also believe that replication studies can be used to investigate and assess whether the variables used in prior studies reflect the concepts that intended to represent (76\%) and whether prior findings resulted from chance variation (66\%).
 While respondents clearly linked replication to epistemological functions, across all functions they were more likely to agree than to strongly agree that replications could serve these purposes.
@@
 While respondents largely agree that replication has some epistemological role to play in the geographic research process, many respondents did not explicitly include these same concepts in their definitions of replicability.
-At total of 253 of our respondents provided an interpretable definition of replicability, but only 68 of those definitions (26\%) referenced some form of epistemological function. 
+A total of 253 of our respondents provided an interpretable definition of replicability, but only 68 of those definitions (26\%) referenced some form of epistemological function. 
 Using replication to externally validate the claims of a study was identified by 49 respondents (19\%).
 No other epistemological function was mentioned by more than 13 respondents (5\%).  
-In contrast, 123 respondents (48\%) reported that replications could be used to assess or improve how well a prior study conforms to the principles of open science (e.g., sharing procedures).
+In contrast, 123 respondents (48\%) reported that replications could be used to assess or improve how well a prior study conforms to the principles of open science (e.g., sharing data and procedures).
 
@@
 
-\noindent More often respondents simply labelled validity checks as the purpose of a replication, as when one researcher defined replicability as, ``The ability to reproduce a study using the same or similar research design to test both its internal and external valdity."
+\noindent More often, respondents simply labelled validity checks as the purpose of a replication.
+One such researcher defined replicability as, ``The ability to reproduce a study using the same or similar research design to test both its internal and external validity."
+
 A number of respondents specializing in qualitative research provided definitions that questioned, or even rejected, the role of replication in their subfield. 
-One representative articulates this position by defining replicability as,
+One qualitative researcher articulates this position by defining replicability as,
 
 \begin{displayquote}
-    ``The claim that empirical research of a study can be repeated in the same way as it was done in the study.
+    ``the claim that empirical research of a study can be repeated in the same way as it was done in the study.
 However, this is not exactly possible in qualitative research, as data collection is always a co-construction between all persons involved in the data collection.
@@
 \subsection*{Factors Affecting the Chances of Replicating a Prior Study}
-Overall respondents believe that the majority of research in the discipline has not been independently replicated and appear to be uncertain about what proportion of the literature could or should be replicated (Figure \ref{fig:Q12-HCS}).
+Overall, respondents believe that the majority of research in the discipline has not been independently replicated and appear to be uncertain about what proportion of the literature could or should be replicated (Figure \ref{fig:Q12-HCS}).
 On average, respondents estimated that 25 percent of recent studies in their sub-field have be replicated. 
@@
 
-The characteristics of the research team that conducted the original study were generally not identified by respondents as likely to change the changes of replicating that study. 
-The majority of respondents (51\%) indicated that a large research team working on the prior study would have no effect on the chances of an independent researcher replicating that work. 
+Respondents were generally uncertain or pessimistic about how the characteristics of the researchers and teams of prior studies would change the chances of replicating the studies. 
+A majority of respondents (51\%) indicated that a large research team working on the prior study would have no effect on the chances of an independent researcher replicating that work. 
 The remaining respondents were nearly evenly split as to whether a large team would increase of decrease the chances of replicating that study. 
-On the whole, more respondents believed that reliance on the unique expertise of the research team conducting a study, or the unique position of a researcher would decrease, rather than increase, the chances of replicating the claims of a study.
-However, only 53 percent of respondents thought the unique position of a researcher would decrease the chances of replicating that study. 
-Similarly, 48 percent of respondents identified reliance on the unique expertise of the original researcher team as decreasing the odds of replicating a study. 
+More respondents believed that reliance on the unique expertise (48\%) or unique position(s) (53\%) of the researcher(s)  conducting a study would decrease, rather than increase, the chances of replicating the claims of a study.
 In both cases, 24 percent of respondents reported that they did not believe either factor would impact the odds of replicating a prior result.
 
-Respondents were similarly divided about the extent to which the approach adopted in the prior study would affect the chances of replicating that study. 
+Respondents were also divided about the extent to which the approach adopted in the prior study would affect the chances of replicating that study. 
 Respondents were nearly evenly split as to whether the number of hypotheses tested by a study, and whether that study used qualitative or mixed methods, would increase or decrease an independent researcher's chances of finding results that supported the claims of the prior study.
@@
 For all six of the characteristics we examined, at least 12 percent of respondents replied that those factors would have no effect on the chances of replicating a prior study.
-Numerous respondents also replied that they simply did not know whether a characteristic would impact the chances of replicating a study. 
+Numerous respondents also replied that they simply did not know whether a characteristic would impact the chances of replicating a study, resulting in a total of 18 to 42 percent of respondents reporting neutral or uncertain opinions about the characteristics of a phenomena and the replicability of research about it.
 For example, 20 percent of respondents said they did not know whether a phenomenon being spatially dependent with itself would affect the chances of replicating a prior study, and an additional 15 percent of respondents said spatial dependence would have no effect on replication.
-Even with this uncertainty, 41 percent of respondents said the presence of spatial dependence was likely to decrease the chances of replicating a prior study.
+Respondents also favored `somewhat likely' responses over stronger `very likely' responses across all characteristics, which further suggests that absence of a clear consensus understanding of how these factors relate to and impact replication.
 
-A majority of respondents did identify the inability to directly measure a phenomenon (61.5\%) and a strong relationship between a phenomenon and local conditions (59.7\%) as reducing the chances of replicating a prior study.
-Respondents were roughly evenly divided on whether other factors would increase or decrease the chances of replicating a study.
-Respondents also favored `somewhat likely' responses over stronger `very likely' responses across all characteristics, which further suggests that absence of a clear consensus understanding of how these factors relate to and impact replication.
+Even with this uncertainty, respondents were clearly more concerned about the impact of spatial dependence and place than about spatial heterogeneity.
+41 percent of respondents reported that the presence of spatial dependence in a phenomena was likely to decrease the chances of replicating a prior study.
+A stronger majority of 59 percent reported that phenomena linked to place-based local conditions would decrease the chances of replication.
+Meanwhile, respondents were split about whether spatially variable phenomena would increase or decrease the chances of replication.
+
+Respondents were more decisive about replication issues with inability to measure or manipulate phenomena than about the presence of multiple possible explanations.
+A majority of respondents identified the inability to directly measure a phenomenon (61.5\%) as reducing the chances of replicating a prior study.
+A large number of respondents (42\%) were either neutral or undecided on whether the inability to experimentally manipulate a phenomena impacts the replicability of studies about it, with a majority of the remaining respondents agreeing that this inability would decrease the chances of replication.
+An equally large number of respondents were neutral or undecided on whether the presence of a large number of plausible explanations for a phenomena would impact the chances of replicating studies about it, with no clear trend.
 
@@
 \subsection*{Factors that Affect the Decision to Attempt Replications}
-Several factors appear to affect whether researchers decide to attempt to replicate recent geographic research (Figure \ref{fig:Q15-DecisionFactors}).
+Several factors related to academic incentives and the availability of prior study research artifacts appear to affect whether researchers decide to attempt to replicate recent geographic research, with relative less concern about the characteristics of prior studies (Figure \ref{fig:Q15-DecisionFactors}).
+
 Geographic researchers identified current academic incentives as the factor most frequently impacting the decision to attempt a replication study. 
@@
 For example, one respondent noted that.
-``Given expected spatial variation, it can be difficult to arrive at a valid metric that would affirm replication while properly acknowledging the inherent variability."
+``Given expected spatial variation, it can be difficult to arrive at a valid metric that would affirm replication while properly acknowledging the inherent variability.''
+
 Finally, a small number of respondents believe that geographic researchers do not undertake replication studies because they either believe that replication is not possible or not necessary in geography.
@@
 These won't be replicated - they've already been produced from the initial research.
-Just producing similar data from another study doesn't seem very valuable."
+Just producing similar data from another study doesn't seem very valuable.''
 \end{displayquote}
@@
 Of the 47 respondents that identified why they decided to attempt their replication study, 38 reported they were attempting to externally validate the claims of the original study, while 10 reported that they were motivated to examine the impact that a difference in geographic or temporal context might have on the results.
-Respondents emphasizing external validation provided motivations statements like,``Testing of conceptual claims on a specific governance context (post-conflict areas) that motivated me to examine other post-conflict areas to examine replicability of results." or ``I didn't think the claim was likely to replicate, and already had relevant data that could be used to test the hypothesis in question."
-Those motivated by differences in context discussed motivations such as, ``We needed compare between Mexico, Honduras and the U.S." and ``To capture seasonal nuance from samples only collected during summer in other studies."
+Respondents emphasizing external validation provided motivation statements like,``Testing of conceptual claims on a specific governance context (post-conflict areas) that motivated me to examine other post-conflict areas to examine replicability of results.'' or ``I didn't think the claim was likely to replicate, and already had relevant data that could be used to test the hypothesis in question.''
+Those motivated by differences in context discussed motivations such as, ``We needed compare between Mexico, Honduras and the U.S." and ``To capture seasonal nuance from samples only collected during summer in other studies.''
 A total of 16 respondents also identified replication as a fundamental part of knowledge creation and evaluation. 
 For example, one respondent directly linked the motivation to replicate to the desire to construct theory, ``To build theory.
-To add strength to criticisms of other theory based on so-called case studies".
+To add strength to criticisms of other theory based on so-called case studies.''
 
@@
 Respondents were generally able to access some (51\%) or all (31\%) of the data used in a prior study, but were slightly less successful at accessing some (43\%) or all (29\%) of the code and procedural information.
-Moreover, being able to access these materials and information did not mean that researcher could fully understand or directly replicate how a study was conducted.
+Moreover, being able to access these materials and information did not mean that researchers could fully understand or directly replicate how a study was conducted.
 Only 16 respondents that attempted replications (19\%) reported being able to follow all of the procedures of a prior study without having to make additional assumptions about how the procedure was implemented.
-In all other cases the replicating researcher had to make additional assumptions about how the authors of the original study conducted their work.
-Respondents also reported that their replication attempts where complicated by an inability to recreate the computational environments of prior analyses and the unavailability of details about where a prior study was conducted.
-In only 31 cases (37\%) was the researcher able to find complete details about the geographic extent and location of the prior study.
+In all other cases, the replicating researcher had to make additional assumptions about how the authors of the original study conducted their work.
+Respondents also reported that their replication attempts where complicated by an inability to recreate the computational environments of prior analyses and by the unavailability of details about where a prior study was conducted.
+The researcher was able to find complete details about the geographic extent and location of the prior study in only 31 cases (37\%).
 
-Ultimately 58 respondents that attempted replications (69\%) reported publishing some or all of their findings.
-23 respondents were able to publish all of the findings of their replication study, while another 35 respondents were able publish at lest some of their findings.
+Ultimately, 58 respondents that attempted replications (69\%) reported publishing some or all of their findings.
+23 respondents were able to publish all of the findings of their replication study, while another 35 respondents were able publish at least some of their findings.
 48 respondents that either did not attempt to publish their findings, or were only able to publish a portion of their findings, reported why they chose not to attempt publication. 
 27 respondents replied that replications were still ongoing or that it would simply take too much time to pursue publication. 
-Many other respondents said that they believe it would either be to difficult to publish their replication study because replications were not valued in the academic literature.
-For example researchers pointed out that,``no one seems to care", their results received ``no interest from journals", and that ``incentives in academia clearly point towards publishing original research."
-In one instance,``The journal that published the original paper specifically claimed to be interested in replications, but then desk rejected our replication."
-This reasoning reflects different form of non-response and selection bias at the root of the `file drawer problem' in academic literature \citep{rosenthal1979}. 
+Many other respondents believed it would be too difficult to publish their replication study because replications were not valued in the academic literature.
+For example, researchers pointed out that,``no one seems to care'', that their results received ``no interest from journals", and that ``incentives in academia clearly point towards publishing original research."
+In one instance,``The journal that published the original paper specifically claimed to be interested in replications, but then desk rejected our replication.''
+This reasoning reflects different forms of non-response and selection bias at the root of the `file drawer problem' in academic literature \citep{rosenthal1979}. 
 The file drawer problem exists when the outcome of a study influence the decision to publish or share that finding.
@@
 \section*{Discussion and Conclusion}
-The results of our survey suggest geographic researchers are familiar with replication and believe that replication studies can serve several epistemological functions.
-However, we also found that researcher provided definitions often did not clearly articulate the epistemological role, or roles, that could be played by a replication study. 
-Researcher definitions instead focused on criteria used to identify a study as a replication. 
+The results of our survey suggest that geographic researchers are familiar with replication and believe that replication studies can serve several epistemological functions.
+However, we also found that researcher-provided definitions often did not clearly articulate the epistemological role, or roles, that could be played by a replication study. 
+Researchers' definitions instead focused on criteria used to identify a study as a replication. 
 Indeed, many of these definitions closely aligned with the definition of reproducibility, which mirrors  \cite{kedron2023survey} findings that researchers appear to often conflate these two terms. 
@@
 Developing a schema to map replication study variations to functions may be particularly challenging in geography due to the complexity of geographic systems and the limited control researchers have over those systems.
-Moreover, it is often unclear which aspect of a study are changing when a replication study is conducted in a new location. 
+Moreover, it is often unclear which aspects of a study are changing when a replication study is conducted in a new location. 
 For example, when a researcher conducting a replication collects new data from a new location it may be difficult to determine whether the study is testing the external validity of a claim in a new population, or in the same population that is subjected to different place-based processes.
 Our results suggest that a conceptual treatment of these connections attuned to the peculiarities of spatial data analysis would be an important first step toward conducting and systematically assessing interpretable replication studies of geographic research.
+Moreover, this attention to variations between prior studies and replications will be pragmatically impossible without improved attention to the availability of reproducible data and procedures for prior studies.
 
@@
 Our results do indicate that it is unlikely that this uncertainty stems from a lack of belief in the potential epistemological value of replication studies.
-Instead, mirroring traditional debates within the discipline, it may be the case that researchers are uncertain whether, or to what extend, the results and claims of a study should be expected to replicate in new locations.
+Instead, mirroring traditional debates within the discipline, it may be the case that researchers are uncertain whether, or to what extent, the results and claims of a study should be expected to replicate in new locations.
 Researcher uncertainty may also be a reflection of the perceived quality and importance of the available geographic literature. 
-If researchers believe many studies simply do not contain important findings, it would be rationale not to prioritize replicating those studies.
+If researchers believe many studies simply do not contain important findings, it would be rational not to prioritize replicating those studies.
 Finally, researchers may simply perceive the external validity check offered by replication as not important to the goals of their research tradition. 
-Following \citet{sayer1992method} distinction between intensive and extensive research, many traditions in geography focus on reconstructing the causal chains that structure social and environmental relations in specfic contexts, rather than the discovery of empirical regularities across those contexts.
+Following \citet{sayer1992method} distinction between intensive and extensive research, many traditions in geography focus on reconstructing the causal chains that structure social and environmental relations in specific contexts, rather than the discovery of empirical regularities across those contexts.
 While some of the qualitative responses to our survey are suggestive of these points, follow-up research could delve more deeply into which studies researcher believe are valuable to replicate and why.
+For example, the definition of replication by a qualitative researcher in our survey states that producing different results is not a weakness, leading to questions about how to approach replications and their different results in qualitative research.
 
@@
 However, the limited size of the sample of researchers that reported actually attempting replications did not allow for an extensive analysis of this questions by subfield. 
-Perhaps an initial indicator of these differences is our finding that human geographers and qualitative researchers were disproportionately likely to provide 'I do not know' responses across survey questions and to question the epistemological role of replication in their subfield.
+Perhaps an initial indicator of these differences is our finding that human geographers and qualitative researchers were disproportionately likely to provide `I do not know' responses across survey questions and to question the epistemological role of replication in their subfield.
 
@@
 For example, as highlighted in the discussion, we were able to gain only limited insight into the epistemological roles researchers believe replications can serve and how they map those roles onto what is changes in a replication study.
+Similarly, it would be useful to understand why respondent believe studies should or should not be replicated. 
+Are those responses a reflection of beliefs that replications are 1) not meaningful for geographic research, 2) impractical to attempt due to the unavailability of procedural details, or 3) unimportant because many geographic studies do not have interesting or important results and implications?
 Future research using in-depth interviews or multi-analyst study designs could probe these question more deeply. 

### 2024-02-06 docs/manuscript/manuscript.tex
Updates from Overleaf

@@
 \author{
-\name{Peter Kedron\textsuperscript{a,b}\thanks{CONTACT Peter Kedron. Email: peterkedron@ucsb.edu}, Joseph Holler\textsuperscript{d}, and Sarah Bardin\textsuperscript{a,c}}
-\affil{\textsuperscript{a} Department of Geography, University of California Santa Barbara, Santa Barbara, California, USA; \textsuperscript{b}School of Geographical Sciences and Urban Planning, Arizona State University, Tempe, Arizona, USA; \textsuperscript{c}Spatial Analysis Research Center (SPARC), Arizona State University, Tempe, Arizona, USA; \textsuperscript{d}Department of Geography, Middlebury College, Middlebury, Vermont, USA}
+\name{Peter Kedron\textsuperscript{a,b}\thanks{CONTACT Peter Kedron. Email: peterkedron@ucsb.edu}, Joseph Holler\textsuperscript{c}, and Sarah Bardin\textsuperscript{b,d}}
+\affil{\textsuperscript{a} Department of Geography, University of California Santa Barbara, Santa Barbara, California, USA; \textsuperscript{b}School of Geographical Sciences and Urban Planning, Arizona State University, Tempe, Arizona, USA; \textsuperscript{c}Department of Geography, Middlebury College, Middlebury, Vermont, USA
+\textsuperscript{d}Spatial Analysis Research Center (SPARC), Arizona State University, Tempe, Arizona, USA; }
 }
@@
 Attempts to reproduce prior research may also test the validity of a study, but do so using the same data and the same, or very similar, analyses. 
-Contrasted with a replication attempt, the central focus of a reproduction attempt is the verification of claims through the examination of how a study was conducted and whether the design and execution of that study support the results presented.
-While the results of a reproduction or replication do not provide conclusive evidence for or against a claim, those that produce outcomes consistent with prior studies typically increase confidence in a claim and the theories it is based on \citep{earp2015, nichols2021}.
+Contrasted with a replication attempt, the central focus of a reproduction attempt is the verification of claims through the examination of how a study was conducted and whether the design and execution of that study supports the results presented.
+While the results of a reproduction or replication do not provide conclusive evidence for or against a claim, those that produce outcomes consistent with prior studies typically increase confidence in a claim and the theories upon which it is based \citep{earp2015, nichols2021}.
 When prior results cannot be recreated, there is reason to question the data and methods used by the prior study, the claims made by the prior study, and perhaps even the current theoretical understanding of the geographic phenomena \citep{christensen2019, NASEM2019}.
@@
 The small number of published studies that have attempted to replicate geographic research suggest that many studies cannot be fully replicated \citep[e.g.,][]{Kedron2022dimaggio, paez2022reproducibility}, or are simply missing components needed to attempt a replication \citep{konkol2019, ostermann2017}.
-More often the literature on the replication of geographic research turns to the question of if and when it is reasonable to expect the findings and claims of a prior study to replicate \citep{kedron2021GA, kedron2022replication, goodchild2021replication, sui2021reproducibility}.
+More often the literature on the replication of geographic research turns to the question of if and when it is reasonable to expect the findings and claims of a prior study to be replicable \citep{kedron2021GA, kedron2022replication, goodchild2021replication, sui2021reproducibility}.
 Place-to-place variations in phenomena, and the processes that produce those variations, are one of the defining features of geographic research and a central tenet of many of its research traditions.
-With these intellectual foundations, it remains unclear how current geographic researchers view replication and its role of in the knowledge accumulation process.
+With these intellectual foundations, it remains unclear how current geographic researchers view replication and its role in the knowledge accumulation process.
 There is similarly limited empirical evidence available about the factors that motivate or discourage geographic researchers from pursuing replications.
 
-To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of replicability, beliefs about what factors affects the chances or replicating a study, motivations to attempt replication studies, and experiences conducting replications.
+To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of replicability, beliefs about what factors affect the chances of replicating a study, motivations to attempt replication studies, and experiences conducting replications.
 We are aware of only a handful of similar published surveys within the geographic literature \citep{balz2020reproducibility, konkol2019, ostermann2017, kedron2023survey}.
@@
 Broadly defined, a replication is any study that has at least one outcome that would be considered diagnostic evidence of the validity of a claim made in prior research \citep{nosek2020}.
-No single study provides evidence about all of the conditions that could affect a claim because individual studies are performed by particular researchers using particular methods to draw and analyze data from particular settings.
-Until a claim is tested through replication, our expectation of whether it will hold under new conditions relies on the theory used to structure the original investigation, or on a speculative assumption of generalizability.
+No single study provides evidence about all conditions that could affect a claim, because individual studies are performed by particular researchers using particular methods to draw and analyze data from particular settings.
+Until a claim is tested through replication, our expectation of whether it will hold under new conditions relies on the theory used to structure the original investigation or on a speculative assumption of generalizability.
 Replications empirically test the validity and reliability of the claims made in a study by selectively altering different aspects of the initial work and repeating the study \citep{schmidt2009, gomez2010replications, radder2003, radder2012}.
@@
 Researchers pursuing a replication will collect new data, but will also change the materials and procedures used in the replication, the measurement of variables, the location of the replication, and/or the population being studied \citep{hendrick1990, schmidt2009, gomez2010replications}.
-Replication studies are often classified as either direct or conceptual based on which of these aspects a research is changing and the epistemological objective they are pursuing \citep[see][]{sargent1981repeatability, schmidt2009, plesser2018reproducibility}.
+Replication studies are often classified as either direct or conceptual depending on which of these aspects a researcher is changing and the epistemological objective they are pursuing \citep[see][]{sargent1981repeatability, schmidt2009, plesser2018reproducibility}.
 
@@
 Alternatively, if a researcher changes how a key construct is measured and also holds all other aspects of a study constant, then the replication can test construct validity.
-Consistently observing a relationship across well-established measures of a concept or phenomenon may raise researcher confidence that the operationalization used in the original study did not bias the result, or affect the claims made.
+Consistently observing a relationship across well-established measures of a concept or phenomenon may raise researcher confidence that the operationalization used in the original study did not bias the result or affect the claims made.
 Finally, if the materials and procedures (e.g., data collection device, analyses) used in a replication differ from a prior study, then the replication assesses whether these factors affected the original results, thereby testing the internal validity of the prior work.
@@
 In conceptual replications, changes are made to the population or location being studied in order to test external validity and whether the claims made in a study generalize to new populations and contexts.
-In geographic research, a conceptual replication could involve changing the location of a study from one city to another, or from one ecosystem to another. 
-Alternatively, a researcher could could conduct a conceptual replication of a study by examining the same location after migration is thought to have changed the population of that area. 
+In geographic research, a conceptual replication could involve changing the location of a study from one city to another or from one ecosystem to another. 
+Alternatively, a researcher could conduct a conceptual replication of a study by examining the same location across different time periods, for instance, before and after migration is thought to have changed the population within that area.
 Conceptual replications provide evidence that can be used to assess the hypotheses and theories that underlie a prior study in new situations \citep{schmidt2009}.
 However, conceptual replications do not necessarily provide evidence that can be used to adjust confidence in a claim made in an initial study \citep{nosek2020}.
-For example, it is not necessarily the case that observing evidence in one location that contradicts a claim made in a prior study of another location would cause a researcher to reduce their confidence in the prior claim.
+For example, it is not necessarily the case that observing evidence in one location that contradicts a prior study's claim based on a different location should reduce a researcher's confidence in the prior claim.
 
 As tests of generalizability and external validity, conceptual replications play an important role in the development of theory \citep{earp2015, haig2022, irvine2021}.
-When a theory is early in its development, it is often unclear whether a researcher should expect the predictions of that theory to hold in new populations, spaces, and times.
+When a theory is early in its development, it is often unclear whether a researcher should expect the predictions of that theory to hold in new populations, locations, and times.
 This is the case because new theories commonly lack a well developed set of conditional statements identifying for whom, where, and/or when their explanations and predictions should hold. 
@@
 In other words, a lack of evidence causes uncertainty about the explanatory range of the theory.
-In this situation, conceptual replications act as empirical tests of the generalizability of a theory to new contexts. 
-Conceptual replications provide evidence to inform the addition and revision of conditional statements that identify for whom, where, and /or when the theory is expected to provide meaningful predictions.
-As the conditions required for a claim to replicate are incorporated into the theory, the theory matures and the situations in which the prediction of the theory are expected to hold becomes clear.
+In this situation, conceptual replications act as empirical tests of the external validity of a theory. 
+Conceptual replications provide evidence to inform the addition and revision of conditional statements that identify for whom, where, and/or when the theory is expected to provide meaningful predictions.
+As the conditions required for a claim to replicate are incorporated into the theory, the theory matures and the situations in which the prediction of the theory are expected to hold becomes clearer.
 
@@
 Researchers involved in these discussions often invoke \cite{anselin1989special} second law of geography which notes that geographic features exhibit uncontrolled variability over space. 
-This principle implies that researchers can expect to observe differences between places, and that perhaps they should expect an inability to replicate prior findings from one place in another.
-Geographic variation essentially poses an identification problem for those interpreting the results of a replication because it is not clear whether the same research outcome (e.g., parameter estimates) observed in different locations is or is not determined by the same processes.
+This principle implies that researchers can expect to observe differences between places, which may contribute to an inability to replicate prior findings from one place in another.
+Geographic variation essentially poses an identification problem for those interpreting the results of a replication, because it is not clear whether the same research outcome (e.g., parameter estimates) observed in different locations is or is not determined by the same processes.
 In some instances, commentary about differences between places are combined  with discussions of role of researcher position and perspective in the research process \citep{Peet1999, simandan2019revisiting}.
-Discussions of replication developed from this perspective often suggest that the role replication can play in geography is limited because research is an interpretive process dependent on the unique perspective of a researcher who is analyzing data drawn from different or unique places \citep{Wainwright2021}.
+Discussions of replication developed from this perspective often suggest that the role replication can play in geography is limited, because research is an interpretive process dependent on the unique perspective of a researcher who is analyzing data drawn from different or unique places \citep{Wainwright2021}.
 
-Arguments about geographic variation can be pushed further and linked the principle of flux \citep{marcovich1967}, which, alternatively argues on one hand that phenomena studied in a place cannot be encountered twice, or on the other hand that places are defined not by the stability of their features but by their continual renewal through processes that create change in those same features.
+Arguments about geographic variation can be pushed further and linked to the principle of flux \citep{marcovich1967}. 
+This alternative argument suggests that, on the one hand, phenomena studied in a place cannot be encountered twice, and, on the other hand, that places are defined not by the stability of their features but by their continual renewal through processes that create change in those same features.
 The two alternative readings of this principle have very different implications for the prospect of replicating geographic research.
 Under the first simpler reading, change is constant and a researcher should not expect to find the same arrangement of features at different times in the same location.
-In this situation, an inability replicate a finding would not be surprising and explanations would be localized. 
-Under the second reading, geographic features are continually changing but structured by processes that may, or may not, be consistent across time and space. 
-In this situation, findings may be expected to replicate within a range of uncertainty, and attempting replications can give insight into the stability of processes across locations.
+In this situation, an inability to replicate a finding would not be surprising and explanations would be localized. 
+Under the second reading, geographic features are continually changing but are structured by processes that may, or may not, be consistent across time and space. 
+In this situation, findings may be expected to replicate within a range of uncertainty, and attempting replications can give insights into the stability of processes across locations.
 
 Understanding places as defined by processes that potentially differ across locations aligns with the argument that geography is well-suited to the development of empirically grounded middle-range theory \citep{miller2015data}.
-The aim of middle-range theory is not to develop overarching explanations or essential features of processes, but rather to offer provisional explanations of identifiable phenomena which can be tested and used to slowly develop more general but bounded explanations \citep{merton1968social}.
+The aim of middle-range theory is not to develop overarching explanations or essential features of processes, but rather to offer provisional explanations of identifiable phenomena, which can be tested and used to slowly develop more general but bounded explanations \citep{merton1968social}.
 As \cite{harvey1969} notes, geographers often elaborate the theories of other disciplines by linking them with spatial explanations of form and process.
 \cite{turner1989, turner2002} argues this synthesis approach gives geography the capability to generate and refine the text of theories and establish their spatial domain by examining phenomena empirically within a web of complex processes that interact within and between locations.
-In this way, replications can give insight into when, where, and why a explanation does not hold \citep{zhang_wolf_2023}.
+In this way, replications can give insight into when, where, and why an explanation does not hold \citep{zhang_wolf_2023}.
 Similarly, \cite{sayer1992method} distinguishes between intensive research in which synthesis is used to identify how processes work in a particular case of location, and extensive research in which synthesis extends across cases or locations to identify how widely a process holds.
 In intensive research, replication attempts that change the data collected from a location can be used to corroborate the explanation of a process.
-In extensive research, replication data is gathered from new context to establish the coverage of an explanation. 
+In extensive research, replication data is gathered from new contexts to establish the coverage of an explanation. 
 In either case, that accumulation of empirical evidence through replication can be used to refine and adjust theory.
 
-Finally, discussions of replication in the literature also frequently point out that many of the phenomena geographers study not only vary across locations, but are difficult or impossible to control \citep[see][]{sayer1992method, kedron2021GA, waters2021motivations}.
+Finally, discussions of replication in the literature also frequently point out that many of the phenomena geographers study not only vary across locations but are difficult or impossible to control \citep[see][]{sayer1992method, kedron2021GA, waters2021motivations}.
 In practice, geographers often lack the ability to control where data is collected, which populations are included or excluded in a study, how variables are measured, and the materials and procedures used when attempting a replication.
@@
 Moreover, it is also often unclear which factors should be accounted for when studying a particular location.
-As \cite{goodchild2021replication} suggest, even when some level of control can be exerted on a process, it will remain difficult to exclude the variable effects of context from studies that are incompletely identified in the presence of spatially heterogeneity.
+As \cite{goodchild2021replication} suggest, even when some level of control can be exerted on a process, it will remain difficult to exclude the variable effects of context from studies that are incompletely identified in the presence of spatial heterogeneity.
 While these factors make replication practically challenging in some forms of geographic research, they do not themselves eliminate the potential usefulness of the practice in selected cases.
@@
 Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Researcher Perceptions of Replication in Geography project (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/x6qrk/}).
-That OSF project connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
+This OSF project connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
 All of the results presented in this paper can be independently reproduced using the materials in that repository.
@@
 We determined uniqueness by grouping researchers by their author-id, and we determined the most recent contact information by selecting records associated with the most recent year of publication. 
-For 383 researchers who had two or more distinct emails in the latest year of publication, we removed non-institutional personal email addresses and then selected one of the remaining institutional email address.
+For 383 researchers who had two or more distinct emails in the latest year of publication, we removed non-institutional personal email addresses and then selected one of the remaining institutional email addresses.
 
@@
 
-\noindent Remaining questions assessed the epistomological purpose of a replication (5 questions), what portion of the geographic literature has/could/should be replicated (3 questions), and factors that impact the chances of successfully replicating a study (18 questions) or the decision to attempt a replication (13 questions).
+\noindent Remaining questions assessed the epistemological purpose of a replication (5 questions), what portion of the geographic literature has/could/should be replicated (3 questions), and factors that impact the chances of successfully replicating a study (18 questions) or the decision to attempt a replication (13 questions).
 For researchers who reported attempting reproductions, we asked them to elaborate on their motivations and outcomes (9 questions).
@@
 We developed the survey questions following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility and replicability literature.
-We pilot tested the survey instrument with \textit{n}=15 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
+We pre-tested the survey instrument with \textit{n}=15 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
 After pilot testing, we removed these individuals from our sampling frame to ensure they would not be included in our final sample.
@@
 Participation in the survey was entirely voluntary. 
-Each researcher that opted to participate in the survey was provided with IRB approved consent documentation and linked to the internet survey instrument. 
+Each researcher that opted to participate in the survey was provided with IRB-approved consent documentation and linked to the internet survey instrument. 
 Participants were also given the option to provide an email address for eligibility for one of three  prizes of 90 US\$, selected randomly after the data collection period.
@@
 We conducted two analyses of the survey responses.
-First, we analyzed researcher perspectives on replicability by coding and calculating summary variables and statistics for three themes: how geographic researchers define replicability, factors researchers believe affect the decision to attempt to replicate a study, and factors researchers believe affect the chances of sucessfully replicating a study.
+First, we analyzed researcher perspectives on replicability by coding and calculating summary variables and statistics for three themes: how geographic researchers define replicability, factors researchers believe affect the decision to attempt to replicate a study, and factors researchers believe affect the chances of successfully replicating a study.
 Second, we analyzed the experiences of researchers attempting to replicate prior studies using statistical summaries of participant motivations, research practices, and ability to produce results consistent with prior studies.
 For both analyses, we produced and analyzed descriptive statistical summaries of participant responses to Likert scale questions cross-tabulated by disciplinary subfield and methodological approach.
-For free-from text responses we coded responses and selected illustrative examples for inclusion.
+For free-form text responses we coded responses and selected illustrative examples for inclusion.
 
@@
 First, we measured the similarity of each provided definition to the definition adopted by the \citet{NASEM2019}. 
-The NASEM defines reproducible research as having three characteristics --- new data, same procedure, and same or similar results.
-To make this comparison, two of the authors independently coded each respondent definition for the presence/absence of each of these the three characteristics.
+The NASEM defines replicable research as having three characteristics --- new data, same procedure, and same or similar results.
+To make this comparison, two of the authors independently coded each respondent definition for the presence/absence of each of these three characteristics.
 Disagreements in the assignment of codes were resolved through discussion between the three authors.
@@
 Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
-The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
-Respondents were similarly balanced across disciplinary subfields, but did contain a greater number of physical geographers  - human geography (26.8\%), physical geography (39.9\%), nature and society (14.8\%), geographic methods and GIScience (17.3\%).
-Different methodological approaches were well represented by respondents in the sample with qualitative researchers making up the smallest sub-group  - quantitative (47.3\%), qualitative (16.3\%), and mixed-methods (36.0\%).
+The majority of respondents were also academics, but were well-balanced across career levels as no one category made up more that 30 percent of the sample.
+Respondents were similarly balanced across disciplinary subfields but did contain a greater number of physical geographers  - human geography (26.8\%), physical geography (39.9\%), nature and society (14.8\%), geographic methods and GIScience (17.3\%).
+Different methodological approaches were well-represented by respondents in the sample with qualitative researchers making up the smallest sub-group  - quantitative (47.3\%), qualitative (16.3\%), and mixed-methods (36.0\%).
 
@@
 Specifically, respondents believe that replication studies can assess whether the claims of that study will hold in new locations (67\%) or new populations (63\%) (Figure \ref{fig:Q7-Epistemology}).
-Respondents also believe that replication studies can be used to investigate and assess whether the variables used in prior studies reflect the concepts that intended to represent (76\%) and whether prior findings resulted from chance variation (66\%).
+Respondents also believe that replication studies can be used to investigate and assess whether the variables used in prior studies reflect the concepts that they were intended to represent (76\%) and whether prior findings resulted from chance variation (66\%).
 While respondents clearly linked replication to epistemological functions, across all functions they were more likely to agree than to strongly agree that replications could serve these purposes.
@@
 A majority of respondents (51\%) indicated that a large research team working on the prior study would have no effect on the chances of an independent researcher replicating that work. 
-The remaining respondents were nearly evenly split as to whether a large team would increase of decrease the chances of replicating that study. 
+The remaining respondents were nearly evenly split as to whether a large team would increase or decrease the chances of replicating that study. 
 More respondents believed that reliance on the unique expertise (48\%) or unique position(s) (53\%) of the researcher(s)  conducting a study would decrease, rather than increase, the chances of replicating the claims of a study.
@@
 For example, 20 percent of respondents said they did not know whether a phenomenon being spatially dependent with itself would affect the chances of replicating a prior study, and an additional 15 percent of respondents said spatial dependence would have no effect on replication.
-Respondents also favored `somewhat likely' responses over stronger `very likely' responses across all characteristics, which further suggests that absence of a clear consensus understanding of how these factors relate to and impact replication.
+Respondents also favored `somewhat likely' responses over stronger `very likely' responses across all characteristics, which further suggests that absence of a clear consensus or understanding of how these factors relate to and impact replication.
 
-Even with this uncertainty, respondents were clearly more concerned about the impact of spatial dependence and place than about spatial heterogeneity.
+Even with this uncertainty, respondents were clearly more concerned about the impact of spatial dependence and place than about spatial variability.
 41 percent of respondents reported that the presence of spatial dependence in a phenomena was likely to decrease the chances of replicating a prior study.
@@
 
-Respondents were more decisive about replication issues with inability to measure or manipulate phenomena than about the presence of multiple possible explanations.
+Respondents were more decisive about replication issues due to an inability to measure or manipulate phenomena than about the presence of multiple possible explanations.
 A majority of respondents identified the inability to directly measure a phenomenon (61.5\%) as reducing the chances of replicating a prior study.
@@
 \subsection*{Factors that Affect the Decision to Attempt Replications}
-Several factors related to academic incentives and the availability of prior study research artifacts appear to affect whether researchers decide to attempt to replicate recent geographic research, with relative less concern about the characteristics of prior studies (Figure \ref{fig:Q15-DecisionFactors}).
+Several factors related to academic incentives and the availability of prior study research artifacts appear to affect whether researchers decide to attempt to replicate recent geographic research, with relatively less concern about the characteristics of prior studies (Figure \ref{fig:Q15-DecisionFactors}).
 
@@
 Moreover, many respondents also saw these factors as occasionally affecting the decision to attempt a replication.
-Few respondents see a low chance of successfully replicating a study as a deterrent to attempting a replication, but it is unclear whether this result is driven by a belief in the value of null replication results, or the belief that replications have high chances of success.
+Few respondents see a low chance of successfully replicating a study as a deterrent to attempting a replication, but it is unclear whether this result is driven by a belief in the value of null replication results or the belief that replications have high chances of success.
 Finally, respondents did not identify ethical concerns as a factor affecting the decision to attempt a replication study. 
 However, these results should also be interpreted in the context of the different levels of uncertainty respondents expressed for each question. 
-More that 15 percent of respondents replied that they did not know whether geographic variation, inexperience with replication, or ethical concerns would affect a researcher's decision to attempt a replication.
+More than 15 percent of respondents replied that they did not know whether geographic variation, inexperience with replication, or ethical concerns would affect a researcher's decision to attempt a replication.
 
 Respondents also qualitatively identified a number of factors that were omitted from our survey instrument as important when deciding whether to attempt a replication of a geographic study. 
-These factors include practical issues such as the difficulty identifying and accessing new field sites where data would be collected during a replication attempt, the costs of conducting a replication, and the time needed to obtain institutional ethics approvals.
+These factors include practical issues, such as the difficulty identifying and accessing new field sites where data would be collected during a replication attempt, the costs of conducting a replication, and the time needed to obtain institutional ethics approvals.
 Respondents also identified uncertainty about how to compare the results of a replication attempt to the original as important when deciding to undertake a replication attempt. 
@@
 Finally, a small number of respondents believe that geographic researchers do not undertake replication studies because they either believe that replication is not possible or not necessary in geography.
-These respondents argued that the main value of geographic studies is that each study provide a unique lens on the portion of the world under investigation, which makes replication a unnecessary endeavour.
+These respondents argued that the main value of geographic studies is that each study provides a unique lens on the portion of the world under investigation, which makes replication an unnecessary endeavour.
 As one respondent stated,
@@
 Human geographers and researchers using quantitative methods less frequently identified academic incentives as important to the replication decision when compared to other sub-groups, but were otherwise broadly similar in their views on artifact availability and study characteristics.
-A greater percentage of quantitative researchers and those working in the areas of GIScience and Methods identified the accessibility of data and methodological information as more often impacting the decision to replicate, but not at a level that was substantially higher than other sub-groups.
+A greater percentage of quantitative researchers and those working in the areas of GIScience and methods identified the accessibility of data and methodological information as more often impacting the decision to replicate but not at a level that was substantially higher than other sub-groups.
 In fact, a greater percentage of researchers studying nature and society identified data accessibility as important than did methods researchers.
@@
 In total, 84 of the researchers that responded to our survey (30\%) reported attempting to independently replicate at least one study in the last two years.   
-This subset of participants formed the basis for our analysis of researcher experiences when attempting to replicate of the work of others.
+This subset of participants formed the basis for our analysis of researcher experiences when attempting to replicate the work of others.
 Respondents specializing in physical geography made up the greatest percentage of replication attempts, but researchers from all the subfields we examined reported attempting replication studies - physical (39\%), human (24\%), GIScience and methods (19\%) and nature and society (15\%).
@@
 Of the 47 respondents that identified why they decided to attempt their replication study, 38 reported they were attempting to externally validate the claims of the original study, while 10 reported that they were motivated to examine the impact that a difference in geographic or temporal context might have on the results.
-Respondents emphasizing external validation provided motivation statements like,``Testing of conceptual claims on a specific governance context (post-conflict areas) that motivated me to examine other post-conflict areas to examine replicability of results.'' or ``I didn't think the claim was likely to replicate, and already had relevant data that could be used to test the hypothesis in question.''
+Respondents emphasizing external validation provided motivation statements such as,``Testing of conceptual claims on a specific governance context (post-conflict areas) that motivated me to examine other post-conflict areas to examine replicability of results.'' or ``I didn't think the claim was likely to replicate, and already had relevant data that could be used to test the hypothesis in question.''
 Those motivated by differences in context discussed motivations such as, ``We needed compare between Mexico, Honduras and the U.S." and ``To capture seasonal nuance from samples only collected during summer in other studies.''
@@
 
-While few respondents were able to replicate all results, the majority respondents reported that they were able to recreate at least some of the results of the study they were investigating. 
+While few respondents were able to replicate all results, the majority of respondents reported that they were able to recreate at least some of the results of the study they were investigating. 
 55 respondents (65\%) reported being able to exactly replicate some of the results of a prior study. 
@@
 Ultimately, 58 respondents that attempted replications (69\%) reported publishing some or all of their findings.
-23 respondents were able to publish all of the findings of their replication study, while another 35 respondents were able publish at least some of their findings.
+23 respondents were able to publish all of the findings of their replication study, while another 35 respondents were able to publish at least some of their findings.
 48 respondents that either did not attempt to publish their findings, or were only able to publish a portion of their findings, reported why they chose not to attempt publication. 
 27 respondents replied that replications were still ongoing or that it would simply take too much time to pursue publication. 
-Many other respondents believed it would be too difficult to publish their replication study because replications were not valued in the academic literature.
+Many other respondents believed it would be too difficult to publish their replication study, because replications were not valued in the academic literature.
 For example, researchers pointed out that,``no one seems to care'', that their results received ``no interest from journals", and that ``incentives in academia clearly point towards publishing original research."
@@
 This reasoning reflects different forms of non-response and selection bias at the root of the `file drawer problem' in academic literature \citep{rosenthal1979}. 
-The file drawer problem exists when the outcome of a study influence the decision to publish or share that finding.
+The file drawer problem exists when the outcome of a study influences the decision to publish or share that finding.
 
@@
 Finally, researchers may simply perceive the external validity check offered by replication as not important to the goals of their research tradition. 
-Following \citet{sayer1992method} distinction between intensive and extensive research, many traditions in geography focus on reconstructing the causal chains that structure social and environmental relations in specific contexts, rather than the discovery of empirical regularities across those contexts.
+Following \citet{sayer1992method} distinction between intensive and extensive research, many traditions in geography focus on reconstructing the causal chains that structure social and environmental relations in specific contexts rather than the discovery of empirical regularities across those contexts.
 While some of the qualitative responses to our survey are suggestive of these points, follow-up research could delve more deeply into which studies researcher believe are valuable to replicate and why.
@@
 Alternatively, there are substantial differences in the concepts and methods used in different subfields, in the types of questions researchers ask, and the phenomena and systems they study. 
-It seems natural that this variation in practice would translate into the use and implementation of replications. 
+It seems natural that this variation in practice would translate into differences in the use and implementation of replications. 
 However, the limited size of the sample of researchers that reported actually attempting replications did not allow for an extensive analysis of this questions by subfield. 
@@
 However, we could not follow this approach because stratification requires knowledge of the population characteristics that predicts differences in response and a population wide census of those key predictors.
-We did not have access to this information because we presently lack a comprehensive understanding of replicability in geography and no list of geographic researchers complete with relevant predictor information exists.
+We did not have access to this information, because we presently lack a comprehensive understanding of replicability in geography, and no list of geographic researchers complete with relevant predictor information exists.
 Given these limitations, our study should be viewed as an exploratory analysis with random sampling and a transparent, reproducible methodology for sample frame construction.
@@
 We have similarly worked to reduce the effects of several other common forms of bias from our survey.
-We have worked to eliminate exclusion bias by including in our sampling frame all researchers publishing as corresponding authors in any wide range of geography journals over a five year period.
+We have sought to eliminate exclusion bias by including in our sampling frame all researchers publishing as corresponding authors in any wide range of geography journals over a five-year period.
 However, geographic researchers publish in a range of journals that are not necessarily indexed as geography by the Web of Science. 
@@
 We attempted to mitigate the potential for questionnaire bias, which could be caused by partially basing our survey instrument on prior studies that over-represent perspectives from the computational and experimental sciences.
-If this were the case, our survey may not gather data on researcher practices and beliefs relevant to replicating types of research not well represented in the existing literature. 
+If this were the case, our survey may not gather data on researcher practices and beliefs relevant to replicating types of research not well-represented in the existing literature. 
 To address this concern, we incorporated into our survey instrument questions informed by a parallel review of the R\&R literature available within geography and a review of critiques of positivist science made by social scientists and human geographers.
@@
 Finally, our survey provides a description of the perspectives of geographic researchers at one point in time and one depth of understanding.
-This work offers an initial measurement of geographers definitions of replicability, beliefs about what factors affects the chances of replicating a study, motivations to attempt replication studies, and experiences conducting replications.
-However, in many cases we were not able to probe more deeply into the nuances of these measurements and the conceptualization that underlie them.
-For example, as highlighted in the discussion, we were able to gain only limited insight into the epistemological roles researchers believe replications can serve and how they map those roles onto what is changes in a replication study.
-Similarly, it would be useful to understand why respondent believe studies should or should not be replicated. 
+This work offers an initial measurement of geographers definitions of replicability, beliefs about what factors affect the chances of replicating a study, motivations to attempt replication studies, and experiences conducting replications.
+However, in many cases we were not able to probe more deeply into the nuances of these measurements and the conceptualizations that underlie them.
+For example, as highlighted in the discussion, we were able to gain only limited insight into the epistemological roles researchers believe replications can serve and how they map those roles onto what is changed in a replication study.
+Similarly, it would be useful to understand why respondents believe studies should or should not be replicated. 
 Are those responses a reflection of beliefs that replications are 1) not meaningful for geographic research, 2) impractical to attempt due to the unavailability of procedural details, or 3) unimportant because many geographic studies do not have interesting or important results and implications?

### 2024-02-06 docs/manuscript/manuscript.tex
Updates from Overleaf

@@
 \begin{abstract}
-Write Abstract
-
+Replications confront existing explanations with new evidence by retesting prior claims using new data and similar research procedures. 
+Publishing replication studies remains uncommon in the geographic literature. 
+Place-to-place variations make it unclear whether the results and claims of a study should be expected to replicate across locations, while a lack of experimental control makes it challenging to implement replications that can provide clear evidence about those same results and claims.
+The small number of studies that have attempted to replicate geographic research suggest that many studies cannot be fully replicated, or are simply missing information needed to attempt a replication.
+Accordingly, it remains unclear how geographic researchers view replication and its role in the knowledge accumulation process.
+To address this question, we surveyed geographic researchers about their understanding of replicability, beliefs about what factors affect the chances of replicating a study, motivations to attempt replication studies, and experiences conducting replications.
+The results of our survey suggest that researchers are familiar with replication and believe that replication studies can serve a range of epistemological functions. 
+Nonetheless, only a small percentage of geographic researchers attempt or publish replications due to a lack of incentives. 
+Researchers are similarly uncertain whether it is currently valuable to replicate geographic research.
+These findings may in part be due to differences between research traditions, and it may be fruitful to further examine how researchers working in different subfields perceive and use replication in their work.
 \end{abstract}
